---
title: "pca"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#PCA code adapted from Kevin Wong

```{r}
#load required libraries
library(tidyr)
library("reshape")
library(plyr)
library(dplyr)
library(ggplot2)
library("arsenal")
library("Rmisc")
library(gridExtra)
library(ggpubr)
library(factoextra)
library(ggplot2)
library(RColorBrewer)
library(lme4)
library(lmerTest)
library(car)
library(effects)
library(ggfortify)
library(cowplot)
library(vegan)
library(corrr)
library(ggcorrplot)
library(GGally)
library(broom)
library(cowplot)
library(RVAideMemoire)
library(arsenal)
library(patchwork)
library(tidyr)
library(ggrepel)
library(randomForest)
library("janitor")
library(varImp)
```

```{r}
#packages not available for R version 4.0.1
install.packages("ropls")
library(ropls)
install.packages("mixOmics")
library("mixOmics")
install.packages("MetaboAnalystR")
library(MetaboAnalystR)
```

```{r}
#create new dataset that has samples as rows and peak areas grouped by class
agg_class <- aggregate(peak_stand ~ coralID + class, data = all_long2, FUN = sum, na.rm = TRUE)

#put in wide form so compound classes are column titles
agg_class_wide <- spread(agg_class, class, peak_stand)

#merge with metadata
agg_class_meta <- merge(agg_class_wide, meta2, by="coralID")

#remove unnecessary columns (dates etc)
agg_class_meta <- agg_class_meta[ -c(32:36)]

#make sure acclimation treatment and genotype columns are being read as factor
agg_class_meta$ATTRIBUTE_acclimation <- as.factor(agg_class_meta$ATTRIBUTE_acclimation)
agg_class_meta$ATTRIBUTE_genotype <- as.factor(agg_class_meta$ATTRIBUTE_genotype)
```

```{r}
#standardize by sample weight
agg_class_norm_all <- agg_class_meta

agg_class_norm_all <- agg_class_norm_all[ ,2:27]/agg_class_norm_all[ ,31]
```

```{r}
#add 1000 to all variables to account for 0 values and log normalization
agg_class_norm_all <- log((agg_class_norm_all + 1000), 2)

#recombine with metadata
agg_class_norm_all <- cbind(agg_class_meta[ ,28:31],agg_class_norm_all)
```

```{r}
#create dataframe including only classified compounds
agg_class_norm_known <- agg_class_norm_all[ -c(30)]

#save as csv
write.csv(agg_class_norm_known,"agg_class_norm_known.csv")
```

```{r}
#PCA of all known compounds (normalized)
pca1 <- prcomp(agg_class_norm_known[c(5:29)], scale. = TRUE, center = TRUE)
summary(pca1)

#calculate eigenvalues 
fviz_eig(pca1)
```

```{r}
#prepare for plotting 
coral_info <- agg_class_norm_known[c(2,3)]

pca_data <- pca1 %>%
  augment(coral_info) %>%
  group_by(ATTRIBUTE_acclimation, ATTRIBUTE_genotype) %>%
  mutate(PC1.mean = mean(.fittedPC1),
         PC2.mean = mean(.fittedPC2))

pca.centroids <- pca_data %>%
  dplyr::select(ATTRIBUTE_acclimation, ATTRIBUTE_genotype, PC1.mean, PC2.mean) %>%
  dplyr::group_by(ATTRIBUTE_acclimation, ATTRIBUTE_genotype) %>%
  dplyr::summarise(PC1.mean = mean(PC1.mean), PC2.mean = mean(PC2.mean))
```

```{r}
#Examine PERMANOVA results

# scale data
vegan_known <- scale(agg_class_norm_known[c(5:29)])

# PerMANOVA 
permanova_known <- adonis(vegan_known ~ ATTRIBUTE_acclimation*ATTRIBUTE_genotype, data = agg_class_norm_known, method='eu')

z_pca_known <- permanova_known$aov.tab
z_pca_known
```

#Assemble plots

#1. Make plots with dots

```{r}
#adding percentages on axis
names(pca_data)[4] <- "PCA1"
names(pca_data)[5] <- "PCA2"
percentage_known <- round((pca1$sdev^2) / sum((pca1$sdev^2)) * 100, 2)
percentage_known <- paste( colnames(pca_data[4:30]), "(", paste(as.character(percentage_known), "%", ")", sep="") )
```

```{r}
#setting up data to add polygons
pca_data$Acclimation.Genotype <- paste(pca_data$ATTRIBUTE_acclimation, pca_data$ATTRIBUTE_genotype)
find_hull_known <- function(pca_data) pca_data[chull(pca_data$PCA1, pca_data$PCA2), ]
hulls_known <- ddply(pca_data, "Acclimation.Genotype", find_hull_known)
```

```{r}
#plot points 
PCA_known <- ggplot(pca_data, aes(PCA1, PCA2, color=ATTRIBUTE_genotype)) + 
  geom_point(size = 4, alpha=0.5, aes(shape = ATTRIBUTE_acclimation)) +
  theme_bw() +
  guides(color=guide_legend(ncol=2)) +
  ylab(percentage_known[2])+
  xlab(percentage_known[1])
PCA_known
```

#2. Add centroids
```{r}
#add centroids 
PCAcen_known <- PCA_known + 
  geom_polygon(data = hulls_known, alpha = 0.2, aes(color = ATTRIBUTE_acclimation, fill = ATTRIBUTE_acclimation, lty = ATTRIBUTE_acclimation)) +
  geom_point(aes(x=PC1.mean, y=PC2.mean,color=ATTRIBUTE_acclimation, shape = ATTRIBUTE_acclimation), data=pca.centroids, size=4, show.legend=TRUE)
PCAcen_known
```

#What if I grouped them by the survivorship data? Specifically the post-hoc. 
```{r}
#group acclimation treatments into group 1 (1 and 2) and group 2 (3, 4, and 5)
agg_class_norm_all2 <- agg_class_norm_all

#df["group_b"][df["group_b"] == 11] <- 77
agg_class_norm_all2[ ,c(2)][agg_class_norm_all2[ ,c(2)] == "2"] <- "1"
agg_class_norm_all2[ ,c(2)][agg_class_norm_all2[ ,c(2)] == "3"] <- "2"
agg_class_norm_all2[ ,c(2)][agg_class_norm_all2[ ,c(2)] == "4"] <- "2"
agg_class_norm_all2[ ,c(2)][agg_class_norm_all2[ ,c(2)] == "5"] <- "2"
```

```{r}
#do the same for known data
agg_class_norm_known2 <- agg_class_norm_known

agg_class_norm_known2[ ,c(2)][agg_class_norm_known2[ ,c(2)] == "2"] <- "1"
agg_class_norm_known2[ ,c(2)][agg_class_norm_known2[ ,c(2)] == "3"] <- "2"
agg_class_norm_known2[ ,c(2)][agg_class_norm_known2[ ,c(2)] == "4"] <- "2"
agg_class_norm_known2[ ,c(2)][agg_class_norm_known2[ ,c(2)] == "5"] <- "2"
```

```{r}
#group genotypes by survival rates 
agg_class_norm_known3 <- agg_class_norm_known
```

```{r}
agg_class_norm_known3[ ,c(3)][agg_class_norm_known3[ ,c(3)] == "CX"] <- "CX"
agg_class_norm_known3[ ,c(3)][agg_class_norm_known3[ ,c(3)] == "BY"] <- "CX"
agg_class_norm_known3[ ,c(3)][agg_class_norm_known3[ ,c(3)] == "DW"] <- "CX"
agg_class_norm_known3[ ,c(3)][agg_class_norm_known3[ ,c(3)] == "EV"] <- "EV"
agg_class_norm_known3[ ,c(3)][agg_class_norm_known3[ ,c(3)] == "HS"] <- "EV"
agg_class_norm_known3[ ,c(3)][agg_class_norm_known3[ ,c(3)] == "FU"] <- "FU"
agg_class_norm_known3[ ,c(3)][agg_class_norm_known3[ ,c(3)] == "GT"] <- "FU"
agg_class_norm_known3[ ,c(3)][agg_class_norm_known3[ ,c(3)] == "IR"] <- "FU"
agg_class_norm_known3[ ,c(3)][agg_class_norm_known3[ ,c(3)] == "JQ"] <- "FU"
```

#PCA with acclimation treatments divided into two groups
```{r}
#PCA of all known compounds (normalized)
pca2 <- prcomp(agg_class_norm_known2[c(5:29)], scale. = TRUE, center = TRUE)
summary(pca2)

#calculate eigenvalues 
fviz_eig(pca2)

coral_info2 <- agg_class_norm_known2[c(2,3)]

pca_data2 <- pca2 %>%
  augment(coral_info2) %>%
  group_by(ATTRIBUTE_acclimation, ATTRIBUTE_genotype) %>%
  mutate(PC1.mean = mean(.fittedPC1),
         PC2.mean = mean(.fittedPC2))

pca.centroids2 <- pca_data2 %>%
  dplyr::select(ATTRIBUTE_acclimation, ATTRIBUTE_genotype, PC1.mean, PC2.mean) %>%
  dplyr::group_by(ATTRIBUTE_acclimation, ATTRIBUTE_genotype) %>%
  dplyr::summarise(PC1.mean = mean(PC1.mean), PC2.mean = mean(PC2.mean))
```

```{r}
#Examine PERMANOVA results

# scale data
vegan_known2 <- scale(agg_class_norm_known2[c(5:29)])

# PerMANOVA 
permanova_known2 <- adonis(vegan_known2 ~ ATTRIBUTE_acclimation*ATTRIBUTE_genotype, data = agg_class_norm_known2, method='eu')

z_pca_known2 <- permanova_known2$aov.tab
z_pca_known2
```

#1. Make plots with dots

```{r}
#adding percentages on axis
names(pca_data2)[4] <- "PCA1"
names(pca_data2)[5] <- "PCA2"
percentage_known2 <- round((pca2$sdev^2) / sum((pca2$sdev^2)) * 100, 2)
percentage_known2 <- paste( colnames(pca_data2[4:30]), "(", paste(as.character(percentage_known2), "%", ")", sep="") )
```

```{r}
#setting up data to add polygons
pca_data2$Acclimation.Genotype <- paste(pca_data2$ATTRIBUTE_acclimation, pca_data2$ATTRIBUTE_genotype)
find_hull_known2 <- function(pca_data2) pca_data2[chull(pca_data2$PCA1, pca_data2$PCA2), ]
hulls_known2 <- ddply(pca_data2, "Acclimation.Genotype", find_hull_known2)
```

```{r}
#plot points 
PCA_known2 <- ggplot(pca_data2, aes(PCA1, PCA2, color=ATTRIBUTE_acclimation)) + 
  geom_point(size = 4, alpha=0.5, aes(shape = ATTRIBUTE_acclimation)) +
  theme_bw() +
  guides(color=guide_legend(ncol=2)) +
  ylab(percentage_known2[2])+
  xlab(percentage_known2[1])
PCA_known2
```

#2. Add centroids
```{r}
#add centroids 
PCAcen_known2 <- PCA_known2 + 
  geom_polygon(data = hulls_known2, alpha = 0.2, aes(color = ATTRIBUTE_acclimation, fill = ATTRIBUTE_acclimation, lty = ATTRIBUTE_acclimation)) +
  geom_point(aes(x=PC1.mean, y=PC2.mean,color=ATTRIBUTE_acclimation, shape = ATTRIBUTE_acclimation), data=pca.centroids2, size=4, show.legend=TRUE)
PCAcen_known2
```

#PCA with genotypes divided into four groups
```{r}
#PCA of all known compounds (normalized)
pca3 <- prcomp(agg_class_norm_known3[c(5:29)], scale. = TRUE, center = TRUE)
summary(pca3)

#calculate eigenvalues 
fviz_eig(pca3)

coral_info3 <- agg_class_norm_known3[c(2,3)]

pca_data3 <- pca3 %>%
  augment(coral_info3) %>%
  group_by(ATTRIBUTE_acclimation, ATTRIBUTE_genotype) %>%
  mutate(PC1.mean = mean(.fittedPC1),
         PC2.mean = mean(.fittedPC2))

pca.centroids3 <- pca_data3 %>%
  dplyr::select(ATTRIBUTE_acclimation, ATTRIBUTE_genotype, PC1.mean, PC2.mean) %>%
  dplyr::group_by(ATTRIBUTE_acclimation, ATTRIBUTE_genotype) %>%
  dplyr::summarise(PC1.mean = mean(PC1.mean), PC2.mean = mean(PC2.mean))
```

```{r}
#Examine PERMANOVA results

# scale data
vegan_known3 <- scale(agg_class_norm_known3[c(5:29)])

# PerMANOVA 
permanova_known3 <- adonis(vegan_known3 ~ ATTRIBUTE_acclimation*ATTRIBUTE_genotype, data = agg_class_norm_known3, method='eu')

z_pca_known3 <- permanova_known3$aov.tab
z_pca_known3
```

#1. Make plots with dots

```{r}
#adding percentages on axis
names(pca_data3)[4] <- "PCA1"
names(pca_data3)[5] <- "PCA2"
percentage_known3 <- round((pca3$sdev^2) / sum((pca3$sdev^2)) * 100, 2)
percentage_known3 <- paste( colnames(pca_data3[4:30]), "(", paste(as.character(percentage_known2), "%", ")", sep="") )
```

```{r}
#setting up data to add polygons
pca_data3$Acclimation.Genotype <- paste(pca_data3$ATTRIBUTE_acclimation, pca_data3$ATTRIBUTE_genotype)
find_hull_known3 <- function(pca_data3) pca_data3[chull(pca_data3$PCA1, pca_data3$PCA2), ]
hulls_known3 <- ddply(pca_data3, "Acclimation.Genotype", find_hull_known3)
```

```{r}
#plot points 
PCA_known3 <- ggplot(pca_data3, aes(PCA1, PCA2, color=ATTRIBUTE_genotype)) + 
  geom_point(size = 4, alpha=0.5, aes(shape = ATTRIBUTE_genotype)) +
  theme_bw() +
  guides(color=guide_legend(ncol=2))
PCA_known3
```

#2. Add centroids
```{r}
#add centroids 
PCAcen_known3 <- PCA_known3 + 
  geom_polygon(data = hulls_known3, alpha = 0.2, aes(color = ATTRIBUTE_genot›ype, fill = ATTRIBUTE_genotype, lty = ATTRIBUTE_genotype)) +
  geom_point(aes(x=PC1.mean, y=PC2.mean,color=ATTRIBUTE_genotype, shape = ATTRIBUTE_genotype), data=pca.centroids3, size=4, show.legend=TRUE)
PCAcen_known3
```

#PCAs with all compounds
```{r}
#PCA of all known compounds (normalized)
pca_all <- prcomp(heat_clean2[ ,c(6:349)], scale. = TRUE, center = TRUE)
summary(pca_all)

#calculate eigenvalues 
fviz_eig(pca_all)

coral_info_all <- heat_clean2[ ,c(3:4)]

pca_data_all <- pca_all %>%
  augment(coral_info_all) %>%
  group_by(ATTRIBUTE_acclimation, ATTRIBUTE_genotype) %>%
  mutate(PC1.mean = mean(.fittedPC1),
         PC2.mean = mean(.fittedPC2))

pca.centroids_all <- pca_data_all %>%
  dplyr::select(ATTRIBUTE_acclimation, ATTRIBUTE_genotype, PC1.mean, PC2.mean) %>%
  dplyr::group_by(ATTRIBUTE_acclimation, ATTRIBUTE_genotype) %>%
  dplyr::summarise(PC1.mean = mean(PC1.mean), PC2.mean = mean(PC2.mean))
```

```{r}
#Examine PERMANOVA results

# scale data
vegan_known_all <- scale(heat_clean2[ ,c(6:349)])

# PerMANOVA 
permanova_known_all <- adonis(vegan_known_all ~ ATTRIBUTE_acclimation*ATTRIBUTE_genotype, data = heat_clean2, method='eu')

z_pca_known_all <- permanova_known_all$aov.tab
z_pca_known_all
```

#1. Make plots with dots

```{r}
#adding percentages on axis
names(pca_data_all)[4] <- "PCA1"
names(pca_data_all)[5] <- "PCA2"
percentage_known_all <- round((pca_all$sdev^2) / sum((pca_all$sdev^2)) * 100, 2)
percentage_known_all <- paste( colnames(pca_data_all[4:211]), "(", paste(as.character(percentage_known_all), "%", ")", sep="") )
```

```{r}
#setting up data to add polygons
pca_data_all$Acclimation.Genotype <- paste(pca_data_all$ATTRIBUTE_acclimation, pca_data_all$ATTRIBUTE_genotype)
find_hull_known_all <- function(pca_data_all) pca_data_all[chull(pca_data_all$PCA1, pca_data_all$PCA2), ]
hulls_known_all <- ddply(pca_data_all, "Acclimation.Genotype", find_hull_known_all)
```

```{r}
#plot points 
PCAplot_all <- ggplot(pca_data_all, aes(PCA1, PCA2, color=ATTRIBUTE_genotype)) + 
  geom_point(size = 4, alpha=0.6, aes(shape = ATTRIBUTE_acclimation)) +
  theme_classic() +
  guides(color=guide_legend(ncol=2))+
  ylab(percentage_known_all[2])+
  xlab(percentage_known_all[1])
PCAplot_all
```

#2. Add centroids
```{r}
#add centroids 
PCAcen_all <- PCAplot_all + 
  geom_polygon(data = hulls_known_all, alpha = 0.2, aes(color = ATTRIBUTE_genotype, fill = ATTRIBUTE_genotype, lty = ATTRIBUTE_acclimation)) +
  geom_point(aes(x=PC1.mean, y=PC2.mean,color=ATTRIBUTE_genotype, shape = ATTRIBUTE_acclimation), data=pca.centroids_all, size=4, show.legend=TRUE)
PCAcen_all
```

#Known direct parents
```{r}
#PCA of all known compounds (normalized)
pca_parent <- prcomp(agg_parent_norm_known[c(5:57)], scale. = TRUE, center = TRUE)
summary(pca_parent)

#calculate eigenvalues 
fviz_eig(pca_parent)
```

```{r}
#prepare for plotting 
coral_info <- agg_class_norm_known[c(2,3)]

pca_p_data <- pca_parent %>%
  augment(coral_info) %>%
  group_by(ATTRIBUTE_acclimation, ATTRIBUTE_genotype) %>%
  mutate(PC1.mean = mean(.fittedPC1),
         PC2.mean = mean(.fittedPC2))

pca.p.centroids <- pca_p_data %>%
  dplyr::select(ATTRIBUTE_acclimation, ATTRIBUTE_genotype, PC1.mean, PC2.mean) %>%
  dplyr::group_by(ATTRIBUTE_acclimation, ATTRIBUTE_genotype) %>%
  dplyr::summarise(PC1.mean = mean(PC1.mean), PC2.mean = mean(PC2.mean))
```

```{r}
#Examine PERMANOVA results

# scale data
vegan_parent <- scale(agg_parent_norm_known[c(5:57)])

# PerMANOVA 
permanova_parent <- adonis(vegan_parent ~ ATTRIBUTE_acclimation*ATTRIBUTE_genotype, data = agg_parent_norm_known, method='eu')

z_pca_known <- permanova_parent$aov.tab
z_pca_known
```

#Assemble plots

#1. Make plots with dots
```{r}
#adding percentages on axis
names(pca_p_data)[4] <- "PCA1"
names(pca_p_data)[5] <- "PCA2"
percentage_parent <- round((pca_parent$sdev^2) / sum((pca_parent$sdev^2)) * 100, 2)
percentage_parent <- paste( colnames(pca_p_data[4:58]), "(", paste(as.character(percentage_parent), "%", ")", sep="") )
```

```{r}
#setting up data to add polygons
pca_p_data$Acclimation.Genotype <- paste(pca_p_data$ATTRIBUTE_acclimation, pca_p_data$ATTRIBUTE_genotype)
find_hull_parent <- function(pca_p_data) pca_p_data[chull(pca_p_data$PCA1, pca_p_data$PCA2), ]
hulls_parent <- ddply(pca_p_data, "Acclimation.Genotype", find_hull_parent)
```

```{r}
#plot points 
PCA_par <- ggplot(pca_p_data, aes(PCA1, PCA2, color=ATTRIBUTE_genotype)) + 
  geom_point(size = 4, alpha=0.5, aes(shape = ATTRIBUTE_acclimation)) +
  theme_bw() +
  guides(color=guide_legend(ncol=2)) +
  ylab(percentage_parent[2])+
  xlab(percentage_parent[1])
PCA_par
```

#2. Add centroids
```{r}
#add centroids 
PCAcen_parent <- PCA_par + 
  geom_polygon(data = hulls_parent, alpha = 0.2, aes(color = ATTRIBUTE_acclimation, fill = ATTRIBUTE_acclimation, lty = ATTRIBUTE_acclimation)) +
  geom_point(aes(x=PC1.mean, y=PC2.mean,color=ATTRIBUTE_acclimation, shape = ATTRIBUTE_acclimation), data=pca.p.centroids, size=4, show.legend=TRUE)
PCAcen_parent
```

#Further PCA results 
```{r}
#get results of PCA 
g1 <- fviz_pca_biplot(pca1, repel = TRUE)
g1
```

#Biplot
```{r}
fviz_pca_var(pca1,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )
```

#PCA results
```{r}
# Eigenvalues
eig.val <- get_eigenvalue(pca1)
eig.val
  
# Results for Variables
res.var <- get_pca_var(pca1)
res.var$coord          # Coordinates
res.var$contrib        # Contributions to the PCs
res.var$cos2           # Quality of representation 

# Results for individuals
res.ind <- get_pca_ind(pca1)
res.ind$coord          # Coordinates
res.ind$contrib        # Contributions to the PCs
res.ind$cos2           # Quality of representation 
```

```{r}
# Helper function 
#::::::::::::::::::::::::::::::::::::::::
var_coord_func <- function(loadings, comp.sdev){
  loadings*comp.sdev
}
# Compute Coordinates
#::::::::::::::::::::::::::::::::::::::::
loadings <- pca1$rotation
sdev <- pca1$sdev
var.coord <- t(apply(loadings, 1, var_coord_func, sdev)) 
head(var.coord[, 1:4])
```

```{r}
# Compute Cos2
#::::::::::::::::::::::::::::::::::::::::
var.cos2 <- var.coord^2
head(var.cos2[, 1:4])
```

```{r}
# Compute contributions
#::::::::::::::::::::::::::::::::::::::::
comp.cos2 <- apply(var.cos2, 2, sum)
contrib <- function(var.cos2, comp.cos2){var.cos2*100/comp.cos2}
var.contrib <- t(apply(var.cos2,1, contrib, comp.cos2))
head(var.contrib[, 1:4])
```

#Other formatting code from Kevin
```{r}
#for just point PCA 
  scale_colour_manual(values=c("#46008B", "#8B0046", "#468B00")) +
  scale_fill_manual(values=c("#46008B", "#8B0046", "#468B00")) + 
  scale_shape_manual(values=c(15, 17, 19)) +
  theme_classic()+
  ylim(-15,15)+
  xlim(-15,15)+
  ylab(percentage_known[2])+
  xlab(percentage_known[1])+
  geom_text(x=9, y=-12, label=paste("p(Day)=", z_pca_known$`Pr(>F)`[1]), size=7, color=ifelse(z_pca_known$`Pr(>F)`[1] < 0.05, "black", "darkgray")) + 
  geom_text(x=9, y=-13.25, label=paste("p(Group)=", z_pca_known$`Pr(>F)`[2]), size=7, color=ifelse(z_pca_known$`Pr(>F)`[2] < 0.05, "black", "darkgray")) + 
  geom_text(x=9, y=-14.5, label=paste("p(Day x Group)=", z_pca_known$`Pr(>F)`[3]), size=7, color=ifelse(z_pca_known$`Pr(>F)`[3] < 0.05, "black", "darkgray")) +
  theme(legend.text = element_text(size=18), 
        legend.position=c(0.90,0.95),
        plot.background = element_blank(),
        legend.title = element_text(size=20), 
        plot.margin = margin(1, 1, 1, 1, "cm"),
        axis.text = element_text(size=18), 
        title = element_text(size=25, face="bold"), 
        axis.title = element_text(size=18))
```

#From Ariana
```{r}
scaled.pca <- prcomp(agg_all[c(2:345)], scale=TRUE, center=TRUE) 

fviz_eig(scaled.pca)

pcaPlot_full<-ggplot2::autoplot(scaled.pca, data=agg_all, frame.colour="ATTRIBUTE_acclimation", loadings=FALSE,  colour="ATTRIBUTE_acclimation", loadings.label.colour="black") +
  theme_bw()
pcaPlot_full
#okay this looks the same and is a LOT faster 
```
























.