---
title: "plsda.rmd"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
#load required libraries
library(rlang)
library(forcats)
library(tidyr)
library("reshape")
library(plyr)
library(dplyr)
library(ggplot2)
library("arsenal")
library("Rmisc")
library(gridExtra)
library(ggpubr)
library(factoextra)
library(ggplot2)
library(RColorBrewer)
library(lme4)
library(lmerTest)
library(car)
library(effects)
library(ggfortify)
library(cowplot)
library(vegan)
library(corrr)
library(ggcorrplot)
library(GGally)
library(broom)
library(cowplot)
library(RVAideMemoire)
library(arsenal)
library(patchwork)
library(tidyr)
library(ggrepel)
library(randomForest)
library("janitor")
library(varImp)
library(mdatools)
```

```{r}
#install latest version of mixOmics using Bioconducter 
library("BiocManager")
#BiocManager::install('mixOmics')
library("mixOmics")
```

#use agg_parent_norm_all dataframe (generated in data_help.Rmd) using ACCLIMATION TREATMENT
```{r load data}
agg_parent_norm_all <- read.csv("agg_parent_norm_all.csv", check.names = FALSE)
```

```{r add new column}
agg_parent_norm_all$acclimation2 <- case_when(agg_parent_norm_all$ATTRIBUTE_acclimation == 1 ~ "126 Days",
                               agg_parent_norm_all$ATTRIBUTE_acclimation == 2 ~ "112 Days",
                               agg_parent_norm_all$ATTRIBUTE_acclimation == 3 ~ "38 Days",
                               agg_parent_norm_all$ATTRIBUTE_acclimation == 4 ~ "24 Days",
                               agg_parent_norm_all$ATTRIBUTE_acclimation == 5 ~ "0 Days",)
```

```{r}
#select treatment names
Y <- agg_parent_norm_all$ATTRIBUTE_acclimation
```

```{r}
#select only data columns
X <- agg_parent_norm_all[5:58]
```

```{r}
#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)  
```

```{r}
dp_acc <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE, ellipse = TRUE, title="Direct Parent PLS-DA: Acclimation",col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))$graph
dp_acc <- dp_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))
dp_acc
```

#use agg_parent_norm_all dataframe (generated in data_help.Rmd) using GENOTYPE

```{r}
#select treatment names
Y <- agg_parent_norm_all$ATTRIBUTE_genotype
```

```{r}
#select only data columns
X <- agg_parent_norm_all[5:58]
```

```{r}
#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)  
```

```{r}
plotIndiv(MyResult.plsda, comp = 1:2, group = agg_parent_norm_all$ATTRIBUTE_genotype, ind.names = FALSE, legend=TRUE, ellipse = TRUE, title="Direct Parent PLS-DA: Source Colony")
```

```{r}
dp_gen <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE, ellipse = TRUE, title="Direct Parent PLS-DA: Source Colony")$graph

dp_gen <- dp_gen + scale_color_manual(name = "Source \nColony", labels=c("AZ", "BY", "CX", "DW", "EV", "FU", "GT", "HS", "IR", "JQ"), values=c("#000e94", "#0024ff", "#116bff", "#34deff", "#63fba5", "#c3fb00", "#fdd000", "#fa6200", "#e92800", "#7c1000"))
dp_gen
```


#PLS-DA within acclimation treatments and genotypes

```{r}
agg_all <- read.csv("agg_all.csv", check.names = FALSE)
```

#Acclimation 1
```{r prepare dataset: agg_all_1}
#subset only rows in the Acclimation 1 from agg_all
agg_all_acc1 <- agg_all[agg_all$ATTRIBUTE_acclimation == '1',]
#View(agg_all_acc1)
```

```{r acc1 PLSDA: genotype}
#select treatment names
Yacc1 <- agg_all_acc1$ATTRIBUTE_genotype

#select only data columns
Xacc1 <- agg_all_acc1[7:350]

#PLSDA without variable selection
acc1.plsda <- mixOmics::plsda(Xacc1,Yacc1) # 1 Run the method
plotIndiv(acc1.plsda)    # 2 Plot the samples
plotVar(acc1.plsda, cutoff = 0.5)

plsda_acc1 <- plotIndiv(acc1.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Acclimation 1 PLS-DA: Genotype",pch = c(2,3,4,5,6,7,8,9,10),col=c("#0024ff", "#116bff", "#34deff", "#63fba5", "#c3fb00", "#fdd000", "#fa6200", "#e92800", "#7c1000"))$graph
plsda_acc1 <- plsda_acc1 + scale_color_manual(name = "Source \nColony", labels=c("BY", "CX", "DW", "EV", "FU", "GT", "HS", "IR", "JQ"), values=c("#0024ff", "#116bff", "#34deff", "#63fba5", "#c3fb00", "#fdd000", "#fa6200", "#e92800", "#7c1000"))
plsda_acc1
```

#Acclimation 2
```{r prepare dataset: agg_all_2}
#subset only rows in the Acclimation 2 from agg_all
agg_all_acc2 <- agg_all[agg_all$ATTRIBUTE_acclimation == '2',]
```

```{r acc2 PLSDA: genotype}
#select treatment names
Yacc2 <- agg_all_acc2$ATTRIBUTE_genotype

#select only data columns
Xacc2 <- agg_all_acc2[7:350]

#PLSDA without variable selection
acc2.plsda <- mixOmics::plsda(Xacc2,Yacc2) # 1 Run the method
plotIndiv(acc2.plsda)    # 2 Plot the samples
plotVar(acc2.plsda, cutoff = 0.5)

plsda_acc2 <- plotIndiv(acc2.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Acclimation 2 PLS-DA: Genotype",pch = c(2,3,4,5,6,7,8,9,10),col=c("#0024ff", "#116bff", "#34deff", "#63fba5", "#c3fb00", "#fdd000", "#fa6200", "#e92800", "#7c1000"))$graph
plsda_acc2 <- plsda_acc2 + scale_color_manual(name = "Source \nColony", labels=c("BY", "CX", "DW", "EV", "FU", "GT", "HS", "IR", "JQ"), values=c("#0024ff", "#116bff", "#34deff", "#63fba5", "#c3fb00", "#fdd000", "#fa6200", "#e92800", "#7c1000"))
plsda_acc2
```

#Acclimation 3
```{r prepare dataset: agg_all_3}
#subset only rows in the Acclimation 3 from agg_all
agg_all_acc3 <- agg_all[agg_all$ATTRIBUTE_acclimation == '3',]
```

```{r acc3 PLSDA: genotype}
#select treatment names
Yacc3 <- agg_all_acc3$ATTRIBUTE_genotype

#select only data columns
Xacc3 <- agg_all_acc3[7:350]

#PLSDA without variable selection
acc3.plsda <- mixOmics::plsda(Xacc3,Yacc3) # 1 Run the method
plotIndiv(acc3.plsda)    # 2 Plot the samples
plotVar(acc3.plsda, cutoff = 0.5)

plsda_acc3 <- plotIndiv(acc3.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Acclimation 3 PLS-DA: Genotype")$graph

plsda_acc3
```

#Acclimation 4
```{r prepare dataset: agg_all_4}
#subset only rows in the Acclimation 4 from agg_all
agg_all_acc4 <- agg_all[agg_all$ATTRIBUTE_acclimation == '4',]
```

```{r acc4 PLSDA: genotype}
#select treatment names
Yacc4 <- agg_all_acc4$ATTRIBUTE_genotype

#select only data columns
Xacc4 <- agg_all_acc4[7:350]

#PLSDA without variable selection
acc4.plsda <- mixOmics::plsda(Xacc4,Yacc4) # 1 Run the method
plotIndiv(acc4.plsda)    # 2 Plot the samples
plotVar(acc4.plsda, cutoff = 0.5)

plsda_acc4 <- plotIndiv(acc4.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Acclimation 4 PLS-DA: Genotype")$graph

plsda_acc4

plsda_acc4_leg <- plotIndiv(acc4.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Acclimation 4 PLS-DA: Genotype")$graph
```

#Acclimation 5
```{r prepare dataset: agg_all_5}
#subset only rows in the Acclimation 5 from agg_all
agg_all_acc5 <- agg_all[agg_all$ATTRIBUTE_acclimation == '5',]
```

```{r acc5 PLSDA: genotype}
#select treatment names
Yacc5 <- agg_all_acc5$ATTRIBUTE_genotype

#select only data columns
Xacc5 <- agg_all_acc5[7:350]

#PLSDA without variable selection
acc5.plsda <- mixOmics::plsda(Xacc5,Yacc5) # 1 Run the method
plotIndiv(acc5.plsda)    # 2 Plot the samples
plotVar(acc5.plsda, cutoff = 0.5)

plsda_acc5 <- plotIndiv(acc5.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Acclimation 5 PLS-DA: Genotype",col = c("#000e94", "#0024ff", "#116bff", "#34deff", "#c3fb00", "#fdd000", "#fa6200", "#e92800", "#7c1000"),pch = c(1,2,3,4,6,7,8,9,10))$graph

plsda_acc5
```

#Arrange PLSDA: Acclimation figures
```{r supplemental fig 4}
#extract legend
legend1 <- get_legend(plsda_acc4_leg)
grid.newpage()
grid.draw(legend1)

#combine plots
plsda_accall <- grid.arrange(plsda_acc1, plsda_acc2, plsda_acc3, plsda_acc4, plsda_acc5, legend1,nrow=2)
plsda_accall 
```


#Genotype AZ
```{r prepare dataset: agg_all_AZ}
#subset only rows in the Genotype AZ from agg_all
agg_all_AZ <- agg_all[agg_all$ATTRIBUTE_genotype == 'AZ',]
```

```{r AZ PLSDA: acclimation}
#select treatment names
Y <- agg_all_AZ$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_AZ[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

az_acc <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Source Colony: AZ",pch = c(3,4,5))$graph
az_acc <- az_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('38 Days', '24 Days', '0 Days'), values=c("#2a9d8f","#0d3b66","#B900E5"))
az_acc
```

#Genotype BY
```{r prepare dataset: agg_all_BY}
#subset only rows in the Genotype BY from agg_all
agg_all_BY <- agg_all[agg_all$ATTRIBUTE_genotype == 'BY',]
```

```{r BY PLSDA: acclimation}
#select treatment names
Y <- agg_all_BY$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_BY[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

by_acc <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Source Colony: BY",col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))$graph
by_acc <- by_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))
by_acc
```

#Genotype CX
```{r prepare dataset: agg_all_CX}
#subset only rows in the Genotype CX from agg_all
agg_all_CX <- agg_all[agg_all$ATTRIBUTE_genotype == 'CX',]
```

```{r CX PLSDA: acclimation}
#select treatment names
Y <- agg_all_CX$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_CX[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

cx_acc <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Source Colony: CX",col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))$graph
cx_acc <- cx_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))
cx_acc
```

#Genotype DW
```{r prepare dataset: agg_all_DW}
#subset only rows in the Genotype DW from agg_all
agg_all_DW <- agg_all[agg_all$ATTRIBUTE_genotype == 'DW',]
```

```{r DW PLSDA: acclimation}
#select treatment names
Y <- agg_all_DW$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_DW[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

dw_acc <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Source Colony: DW",col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))$graph
#dw_acc <- dw_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))
dw_acc
```

#Genotype EV
```{r prepare dataset: agg_all_EV}
#subset only rows in the Genotype EV from agg_all
agg_all_EV <- agg_all[agg_all$ATTRIBUTE_genotype == 'EV',]
```

```{r EV PLSDA: acclimation}
#select treatment names
Y <- agg_all_EV$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_EV[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

ev_acc <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Source Colony: EV",col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66"))$graph 
#ev_acc <- ev_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))
ev_acc
```

#Genotype FU
```{r prepare dataset: agg_all_FU}
#subset only rows in the Genotype FU from agg_all
agg_all_FU <- agg_all[agg_all$ATTRIBUTE_genotype == 'FU',]
```

```{r FU PLSDA: acclimation}
#select treatment names
Y <- agg_all_FU$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_FU[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

fu_acc <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Source Colony: FU",col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))$graph
#fu_acc <- fu_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))
fu_acc
```

#Genotype GT
```{r prepare dataset: agg_all_GT}
#subset only rows in the Genotype GT from agg_all
agg_all_GT <- agg_all[agg_all$ATTRIBUTE_genotype == 'GT',]
```

```{r GT PLSDA: acclimation}
#select treatment names
Y <- agg_all_GT$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_GT[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

gt_acc <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Source Colony: GT",col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))$graph
#gt_acc <- gt_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))
gt_acc
```

#Genotype HS
```{r prepare dataset: agg_all_HS}
#subset only rows in the Genotype HS from agg_all
agg_all_HS <- agg_all[agg_all$ATTRIBUTE_genotype == 'HS',]
```

```{r HS PLSDA: acclimation}
#select treatment names
Y <- agg_all_HS$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_HS[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

hs_acc <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Source Colony: HS",col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))$graph
#hs_acc <- hs_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("#3f8cd1", "#f28d0a", "#c2c2c2", "#249e6e", "#c979aa"))
hs_acc
```

#Genotype IR
```{r prepare dataset: agg_all_IR}
#subset only rows in the Genotype IR from agg_all
agg_all_IR <- agg_all[agg_all$ATTRIBUTE_genotype == 'IR',]
```

```{r IR PLSDA: acclimation}
#select treatment names
Y <- agg_all_IR$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_IR[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

ir_acc <- plotIndiv(MyResult.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Source Colony: IR",col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))$graph
#ir_acc <- ir_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("#3f8cd1", "#f28d0a", "#c2c2c2", "#249e6e", "#c979aa"))
ir_acc
```

#Genotype JQ
```{r prepare dataset: agg_all_JQ}
#subset only rows in the Genotype JQ from agg_all
agg_all_JQ <- agg_all[agg_all$ATTRIBUTE_genotype == 'JQ',]
```

```{r JQ PLSDA: acclimation}
#select treatment names
Yjq <- agg_all_JQ$ATTRIBUTE_acclimation

#select only data columns
Xjq <- agg_all_JQ[7:350]

#PLSDA without variable selection
JQ.plsda <- mixOmics::plsda(Xjq,Yjq) # 1 Run the method
plotIndiv(JQ.plsda)    # 2 Plot the samples
plotVar(JQ.plsda, cutoff = 0.5)

jq_acc <- plotIndiv(JQ.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Source Colony: JQ",size.title = rel(2),col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))$graph
jq_acc <- jq_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))
jq_acc

jq_acc2 <- plotIndiv(JQ.plsda, ind.names = FALSE, legend=FALSE,ellipse = TRUE,title="Source Colony: JQ",size.title = rel(2),col = c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))$graph
#jq_acc <- jq_acc + scale_color_manual(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days'), values=c("darkorange","#e9c46a","#2a9d8f","#0d3b66","#B900E5"))
```

#Arrange plots
```{r}
#arrange only PLSDA plots
plsda_gens <- grid.arrange(by_acc, cx_acc, dw_acc, ev_acc, fu_acc, gt_acc, hs_acc, ir_acc, jq_acc2, ncol = 3)
plsda_gens
```

```{r supplemental fig 3}
#extract legend
legend <- get_legend(jq_acc)
grid.newpage()
grid.draw(legend)

#specify proportions
layout <- matrix(c(1,1,1,1,2), ncol = 5, byrow = TRUE)

#combine legend and PLSDAs
figs3 <- grid.arrange(plsda_gens, legend, layout_matrix = layout)
```
