---
title: "plsda.rmd"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, warning=FALSE, message=FALSE}
#load required libraries
library(rlang)
library(tidyr)
library("reshape")
library(plyr)
library(dplyr)
library(ggplot2)
library("arsenal")
library("Rmisc")
library(gridExtra)
library(ggpubr)
library(factoextra)
library(ggplot2)
library(RColorBrewer)
library(lme4)
library(lmerTest)
library(car)
library(effects)
library(ggfortify)
library(cowplot)
library(vegan)
library(corrr)
library(ggcorrplot)
library(GGally)
library(broom)
library(cowplot)
library(RVAideMemoire)
library(arsenal)
library(patchwork)
library(tidyr)
library(ggrepel)
library(randomForest)
library("janitor")
library(varImp)
library(mdatools)
```

```{r}
#install latest version of mixOmics using Bioconducter 
library("BiocManager")
#BiocManager::install('mixOmics')
library("mixOmics")
```

#Prepare data

```{r}
#read in all_long2
all_long2 <- read.csv("all_long2.csv", check.names = FALSE)

#check variable types
summary(all_long2)
```

```{r}
#convert necessary variables to factor
all_long2$ATTRIBUTE_acclimation <- as.factor(all_long2$ATTRIBUTE_acclimation)
all_long2$ATTRIBUTE_genotype <- as.factor(all_long2$ATTRIBUTE_genotype)
all_long2$id <- as.factor(all_long2$id)
all_long2$X.featureID <- as.factor(all_long2$X.featureID)
all_long2$csi_smiles <- as.factor(all_long2$csi_smiles)
all_long2$ms2_smiles <- as.factor(all_long2$ms2_smiles)
all_long2$ms2_library_match <- as.factor(all_long2$ms2_library_match)
all_long2$parent_mass <- as.factor(all_long2$parent_mass)
all_long2$retention_time <- as.factor(all_long2$retention_time)
all_long2$table_number <- as.factor(all_long2$table_number)
all_long2$smiles <- as.factor(all_long2$smiles)
all_long2$structure_source <- as.factor(all_long2$structure_source)
all_long2$kingdom <- as.factor(all_long2$kingdom)
all_long2$superclass <- as.factor(all_long2$superclass)
all_long2$class <- as.factor(all_long2$class)
all_long2$subclass <- as.factor(all_long2$subclass)
all_long2$direct_parent <- as.factor(all_long2$direct_parent)
all_long2$ATTRIBUTE_sampleID <- as.factor(all_long2$ATTRIBUTE_sampleID)
```

```{r}
#use mdatools to convert all_long2 to matrix
all_long2_mat = mda.df2mat(all_long2, full = TRUE)
```

```{r}
#exclude unneeded columns: unknown taxonomic columns
all_long2_mat <- mda.exclcols(all_long2_mat, 1299:1507)
```

```{r}
#exclude unneeded columns: individual coral IDs
#earlier columns last so the counts are still correct 
all_long2_mat <- mda.exclcols(all_long2_mat, 4:1179)
```



#Partial least squares regression 

#From Arianna (modified from Kevin)

#use all_agg dataframe (generated in data_help.Rmd) using ACCLIMATION TREATMENT 

```{r load data}
agg_all <- read.csv("agg_all.csv", check.names = FALSE)
agg_parent_norm_all <- read.csv("agg_parent_norm_all.csv", check.names = FALSE)
agg_parent_norm_known <- read.csv("agg_parent_norm_known.csv", check.names = FALSE)
```

```{r}
#select treatment names
Y <- agg_all$ATTRIBUTE_acclimation
```

```{r}
#select only data columns
X <- agg_all[5:348]
```

```{r}
#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)  
```

```{r}
plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="PLS-DA")
```

#use all_agg dataframe (generated in data_help.Rmd) using GENOTYPE

```{r}
#select treatment names
Y <- agg_all$ATTRIBUTE_genotype
```

```{r}
#select only data columns
X <- agg_all[5:348]
```

```{r}
#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)  
```

```{r}
plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="PLS-DA")
```


#use agg_parent_norm_all dataframe (generated in data_help.Rmd) using ACCLIMATION TREATMENT

```{r}
#select treatment names
Y <- agg_parent_norm_all$ATTRIBUTE_acclimation
```

```{r}
#select only data columns
X <- agg_parent_norm_all[5:58]
```

```{r}
#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)  
```

```{r}
plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="PLS-DA")
```

#use agg_parent_norm_all dataframe (generated in data_help.Rmd) using GENOTYPE

```{r}
#select treatment names
Y <- agg_parent_norm_all$ATTRIBUTE_genotype
```

```{r}
#select only data columns
X <- agg_parent_norm_all[5:58]
```

```{r}
#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)  
```

```{r}
plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="PLS-DA")
```

#use only top direct parents, agg_parent_known3 (generated in vip.Rmd) using ACCLIMATION TREATMENT

```{r}
#select treatment names
Y <- agg_parent_top3$attribute_acclimation
```

```{r}
#select only data columns
X <- agg_parent_top3[5:7]
```

```{r}
#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)  
```

```{r}
plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="PLS-DA")
```

#use only top direct parents, agg_parent_known3 (generated in vip.Rmd) using GENOTYPE

```{r}
#select treatment names
Y <- agg_parent_top3$attribute_genotype
```

```{r}
#select only data columns
X <- agg_parent_top3[5:7]
```

```{r}
#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)  
```

```{r}
plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="PLS-DA")
```


#Methods stolen from Kevin

```{r variables as factors}
#make sure that all proper columns are being read as factors 
agg_parent_norm_all$ATTRIBUTE_acclimation <- as.factor(agg_parent_norm_all$ATTRIBUTE_acclimation)

agg_parent_norm_all$ATTRIBUTE_genotype <- as.factor(agg_parent_norm_all$ATTRIBUTE_genotype)

agg_parent_norm_known$ATTRIBUTE_acclimation <- as.factor(agg_parent_norm_known$ATTRIBUTE_acclimation)

agg_parent_norm_known$ATTRIBUTE_genotype <- as.factor(agg_parent_norm_known$ATTRIBUTE_genotype)
```

#subset datasets for analysis
#every possible combination of 2 acclimation treatments
```{r all pairwise acc}
#aggregated by all direct parents: single groups
parent_all_acc1 <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_acclimation == "1") %>%
  na.omit()

parent_all_acc2 <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_acclimation == "2") %>%
  na.omit()

parent_all_acc3 <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_acclimation == "3") %>%
  na.omit()

parent_all_acc4 <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_acclimation == "4") %>%
  na.omit()

parent_all_acc5 <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_acclimation == "5") %>%
  na.omit()

parent_all_acc1 <- droplevels(parent_all_acc1)
parent_all_acc2 <- droplevels(parent_all_acc2)
parent_all_acc3 <- droplevels(parent_all_acc3)
parent_all_acc4 <- droplevels(parent_all_acc4)
parent_all_acc5 <- droplevels(parent_all_acc5)

#bind together in every possible combo 
parent_all_acc1vs2 <- rbind(parent_all_acc1, parent_all_acc2)

parent_all_acc1vs3 <- rbind(parent_all_acc1, parent_all_acc3)

parent_all_acc1vs4 <- rbind(parent_all_acc1, parent_all_acc4)

parent_all_acc1vs5 <- rbind(parent_all_acc1, parent_all_acc5)

parent_all_acc2vs3 <- rbind(parent_all_acc2, parent_all_acc3)

parent_all_acc2vs4 <- rbind(parent_all_acc2, parent_all_acc4)

parent_all_acc2vs5 <- rbind(parent_all_acc2, parent_all_acc5)

parent_all_acc3vs4 <- rbind(parent_all_acc3, parent_all_acc4)

parent_all_acc3vs5 <- rbind(parent_all_acc3, parent_all_acc5)

parent_all_acc4vs5 <- rbind(parent_all_acc4, parent_all_acc5)
```

```{r known pairwise acc}
#aggregated by known direct parents: single groups
parent_known_acc1 <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_acclimation == "1") %>%
  na.omit()

parent_known_acc2 <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_acclimation == "2") %>%
  na.omit()

parent_known_acc3 <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_acclimation == "3") %>%
  na.omit()

parent_known_acc4 <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_acclimation == "4") %>%
  na.omit()

parent_known_acc5 <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_acclimation == "5") %>%
  na.omit()

parent_known_acc1 <- droplevels(parent_known_acc1)
parent_known_acc2 <- droplevels(parent_known_acc2)
parent_known_acc3 <- droplevels(parent_known_acc3)
parent_known_acc4 <- droplevels(parent_known_acc4)
parent_known_acc5 <- droplevels(parent_known_acc5)

#bind together in every possible combo 
parent_known_acc1vs2 <- rbind(parent_known_acc1, parent_known_acc2)

parent_known_acc1vs3 <- rbind(parent_known_acc1, parent_known_acc3)

parent_known_acc1vs4 <- rbind(parent_known_acc1, parent_known_acc4)

parent_known_acc1vs5 <- rbind(parent_known_acc1, parent_known_acc5)

parent_known_acc2vs3 <- rbind(parent_known_acc2, parent_known_acc3)

parent_known_acc2vs4 <- rbind(parent_known_acc2, parent_known_acc4)

parent_known_acc2vs5 <- rbind(parent_known_acc2, parent_known_acc5)

parent_known_acc3vs4 <- rbind(parent_known_acc3, parent_known_acc4)

parent_known_acc3vs5 <- rbind(parent_known_acc3, parent_known_acc5)

parent_known_acc4vs5 <- rbind(parent_known_acc4, parent_known_acc5)
```

#every possible combination of 2 genotypes
```{r all pairwise gen}
#aggregated by all direct parents: single groups
parent_all_AZ <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "AZ") %>%
  na.omit()
parent_all_BY <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "BY") %>%
  na.omit()
parent_all_CX <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "CX") %>%
  na.omit()
parent_all_DW <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "DW") %>%
  na.omit()
parent_all_EV <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "EV") %>%
  na.omit()
parent_all_FU <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "FU") %>%
  na.omit()
parent_all_GT <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "GT") %>%
  na.omit()
parent_all_HS <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "HS") %>%
  na.omit()
parent_all_IR <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "IR") %>%
  na.omit()
parent_all_JQ <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "JQ") %>%
  na.omit()

parent_all_AZvsBY <- rbind(parent_all_AZ, parent_all_BY)
parent_all_AZvsCX <- rbind(parent_all_AZ, parent_all_CX)
parent_all_AZvsDW <- rbind(parent_all_AZ, parent_all_DW)
parent_all_AZvsEV <- rbind(parent_all_AZ, parent_all_EV)
parent_all_AZvsFU <- rbind(parent_all_AZ, parent_all_FU)
parent_all_AZvsGT <- rbind(parent_all_AZ, parent_all_GT)
parent_all_AZvsHS <- rbind(parent_all_AZ, parent_all_HS)
parent_all_AZvsIR <- rbind(parent_all_AZ, parent_all_IR)
parent_all_AZvsJQ <- rbind(parent_all_AZ, parent_all_JQ)

parent_all_BYvsCX <- rbind(parent_all_BY, parent_all_CX)
parent_all_BYvsDW <- rbind(parent_all_BY, parent_all_DW)
parent_all_BYvsEV <- rbind(parent_all_BY, parent_all_EV)
parent_all_BYvsFU <- rbind(parent_all_BY, parent_all_FU)
parent_all_BYvsGT <- rbind(parent_all_BY, parent_all_GT)
parent_all_BYvsHS <- rbind(parent_all_BY, parent_all_HS)
parent_all_BYvsIR <- rbind(parent_all_BY, parent_all_IR)
parent_all_BYvsJQ <- rbind(parent_all_BY, parent_all_JQ)

parent_all_CXvsDW <- rbind(parent_all_CX, parent_all_DW)
parent_all_CXvsEV <- rbind(parent_all_CX, parent_all_EV)
parent_all_CXvsFU <- rbind(parent_all_CX, parent_all_FU)
parent_all_CXvsGT <- rbind(parent_all_CX, parent_all_GT)
parent_all_CXvsHS <- rbind(parent_all_CX, parent_all_HS)
parent_all_CXvsIR <- rbind(parent_all_CX, parent_all_IR)
parent_all_CXvsJQ <- rbind(parent_all_CX, parent_all_JQ)

parent_all_DWvsEV <- rbind(parent_all_DW, parent_all_EV)
parent_all_DWvsFU <- rbind(parent_all_DW, parent_all_FU)
parent_all_DWvsGT <- rbind(parent_all_DW, parent_all_GT)
parent_all_DWvsHS <- rbind(parent_all_DW, parent_all_HS)
parent_all_DWvsIR <- rbind(parent_all_DW, parent_all_IR)
parent_all_DWvsJQ <- rbind(parent_all_DW, parent_all_JQ)

parent_all_EVvsFU <- rbind(parent_all_EV, parent_all_FU)
parent_all_EVvsGT <- rbind(parent_all_EV, parent_all_GT)
parent_all_EVvsHS <- rbind(parent_all_EV, parent_all_HS)
parent_all_EVvsIR <- rbind(parent_all_EV, parent_all_IR)
parent_all_EVvsJQ <- rbind(parent_all_EV, parent_all_JQ)

parent_all_FUvsGT <- rbind(parent_all_FU, parent_all_GT)
parent_all_FUvsHS <- rbind(parent_all_FU, parent_all_HS)
parent_all_FUvsIR <- rbind(parent_all_FU, parent_all_IR)
parent_all_FUvsJQ <- rbind(parent_all_FU, parent_all_JQ)

parent_all_GTvsHS <- rbind(parent_all_GT, parent_all_HS)
parent_all_GTvsIR <- rbind(parent_all_GT, parent_all_IR)
parent_all_GTvsJQ <- rbind(parent_all_GT, parent_all_JQ)

parent_all_HSvsIR <- rbind(parent_all_HS, parent_all_IR)
parent_all_HSvsJQ <- rbind(parent_all_HS, parent_all_JQ)

parent_all_IRvsJQ <- rbind(parent_all_IR, parent_all_JQ)
```

```{r known pairwise gen}
#aggregated by known direct parents: single groups
parent_known_AZ <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "AZ") %>%
  na.omit()
parent_known_BY <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "BY") %>%
  na.omit()
parent_known_CX <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "CX") %>%
  na.omit()
parent_known_DW <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "DW") %>%
  na.omit()
parent_known_EV <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "EV") %>%
  na.omit()
parent_known_FU <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "FU") %>%
  na.omit()
parent_known_GT <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "GT") %>%
  na.omit()
parent_known_HS <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "HS") %>%
  na.omit()
parent_known_IR <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "IR") %>%
  na.omit()
parent_known_JQ <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "JQ") %>%
  na.omit()

parent_known_AZvsBY <- rbind(parent_known_AZ, parent_known_BY)
parent_known_AZvsCX <- rbind(parent_known_AZ, parent_known_CX)
parent_known_AZvsDW <- rbind(parent_known_AZ, parent_known_DW)
parent_known_AZvsEV <- rbind(parent_known_AZ, parent_known_EV)
parent_known_AZvsFU <- rbind(parent_known_AZ, parent_known_FU)
parent_known_AZvsGT <- rbind(parent_known_AZ, parent_known_GT)
parent_known_AZvsHS <- rbind(parent_known_AZ, parent_known_HS)
parent_known_AZvsIR <- rbind(parent_known_AZ, parent_known_IR)
parent_known_AZvsJQ <- rbind(parent_known_AZ, parent_known_JQ)

parent_known_BYvsCX <- rbind(parent_known_BY, parent_known_CX)
parent_known_BYvsDW <- rbind(parent_known_BY, parent_known_DW)
parent_known_BYvsEV <- rbind(parent_known_BY, parent_known_EV)
parent_known_BYvsFU <- rbind(parent_known_BY, parent_known_FU)
parent_known_BYvsGT <- rbind(parent_known_BY, parent_known_GT)
parent_known_BYvsHS <- rbind(parent_known_BY, parent_known_HS)
parent_known_BYvsIR <- rbind(parent_known_BY, parent_known_IR)
parent_known_BYvsJQ <- rbind(parent_known_BY, parent_known_JQ)

parent_known_CXvsDW <- rbind(parent_known_CX, parent_known_DW)
parent_known_CXvsEV <- rbind(parent_known_CX, parent_known_EV)
parent_known_CXvsFU <- rbind(parent_known_CX, parent_known_FU)
parent_known_CXvsGT <- rbind(parent_known_CX, parent_known_GT)
parent_known_CXvsHS <- rbind(parent_known_CX, parent_known_HS)
parent_known_CXvsIR <- rbind(parent_known_CX, parent_known_IR)
parent_known_CXvsJQ <- rbind(parent_known_CX, parent_known_JQ)

parent_known_DWvsEV <- rbind(parent_known_DW, parent_known_EV)
parent_known_DWvsFU <- rbind(parent_known_DW, parent_known_FU)
parent_known_DWvsGT <- rbind(parent_known_DW, parent_known_GT)
parent_known_DWvsHS <- rbind(parent_known_DW, parent_known_HS)
parent_known_DWvsIR <- rbind(parent_known_DW, parent_known_IR)
parent_known_DWvsJQ <- rbind(parent_known_DW, parent_known_JQ)

parent_known_EVvsFU <- rbind(parent_known_EV, parent_known_FU)
parent_known_EVvsGT <- rbind(parent_known_EV, parent_known_GT)
parent_known_EVvsHS <- rbind(parent_known_EV, parent_known_HS)
parent_known_EVvsIR <- rbind(parent_known_EV, parent_known_IR)
parent_known_EVvsJQ <- rbind(parent_known_EV, parent_known_JQ)

parent_known_FUvsGT <- rbind(parent_known_FU, parent_known_GT)
parent_known_FUvsHS <- rbind(parent_known_FU, parent_known_HS)
parent_known_FUvsIR <- rbind(parent_known_FU, parent_known_IR)
parent_known_FUvsJQ <- rbind(parent_known_FU, parent_known_JQ)

parent_known_GTvsHS <- rbind(parent_known_GT, parent_known_HS)
parent_known_GTvsIR <- rbind(parent_known_GT, parent_known_IR)
parent_known_GTvsJQ <- rbind(parent_known_GT, parent_known_JQ)

parent_known_HSvsIR <- rbind(parent_known_HS, parent_known_IR)
parent_known_HSvsJQ <- rbind(parent_known_HS, parent_known_JQ)

parent_known_IRvsJQ <- rbind(parent_known_IR, parent_known_JQ)
```


#Creating the PLS-DA function

``` {r plsdaFunction, echo=TRUE, warning=FALSE, message=FALSE}
vip.plsda <- function(data,         # input datas et with only the two variables being compared 
                      Y,            # column of the predictor variable
                      path,         # path to output folder for graphs
                      name          # name of the PLS-DA graphs
                      ) { 
col <- ncol(data)                   # Finding number of columns in data set                                 
X <- data[5:col]                    # assigning metabolites as X data set
Y <- as.factor(Y)                   # assigning groups as Y data set (predictor)
MyResult.plsda <- mixOmics::plsda(X, Y)       # Running PLS-DA

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE) # Plotting PLS-DA
pdf(file=paste0(path, name, "_plsda.pdf")) 
dev.off()

vip <- PLSDA.VIP(MyResult.plsda)                            # VIP Extraction from the PLS=DA
vip.df <- as.data.frame(vip[["tab"]])                       # Creating a readable data frame
vip.table <- tibble::rownames_to_column(vip.df, var = "DirectParent") # Creating a table format
vip.table_1 <- vip.table %>%                                # Filtering metabolites with VIPs >= 1
  filter(VIP >= 1)
return(vip.table_1)
}
```
#THIS WORKS AS OF 7/4/22


### PLD-DA and VIP Extraction

``` {r PLSDA all acc, echo=TRUE, warning=FALSE, message=FALSE}
path <- "/Users/cassieraker/Documents/_URI/_Research/Data/2019_PR_ch3_chemicalecology/2021_UTAustin_data/output/PLSDA_figs/"

#all direct parents by acclimation
parent_all_acc1vs2_VIP_1 <- vip.plsda(parent_all_acc1vs2, parent_all_acc1vs2$ATTRIBUTE_acclimation, path, "parent_all_acc1vs2")

parent_all_acc1vs3_VIP_1 <- vip.plsda(parent_all_acc1vs3, parent_all_acc1vs3$ATTRIBUTE_acclimation, path, "parent_all_acc1vs3")

parent_all_acc1vs4_VIP_1 <- vip.plsda(parent_all_acc1vs4, parent_all_acc1vs4$ATTRIBUTE_acclimation, path, "parent_all_acc1vs4")

parent_all_acc1vs5_VIP_1 <- vip.plsda(parent_all_acc1vs5, parent_all_acc1vs5$ATTRIBUTE_acclimation, path, "parent_all_acc1vs5")

parent_all_acc2vs3_VIP_1 <- vip.plsda(parent_all_acc2vs3, parent_all_acc2vs3$ATTRIBUTE_acclimation, path, "parent_all_acc2vs3")

parent_all_acc2vs4_VIP_1 <- vip.plsda(parent_all_acc2vs4, parent_all_acc2vs4$ATTRIBUTE_acclimation, path, "parent_all_acc2vs4")

parent_all_acc2vs5_VIP_1 <- vip.plsda(parent_all_acc2vs5, parent_all_acc2vs5$ATTRIBUTE_acclimation, path, "parent_all_acc2vs5")

parent_all_acc3vs4_VIP_1 <- vip.plsda(parent_all_acc3vs4, parent_all_acc3vs4$ATTRIBUTE_acclimation, path, "parent_all_acc3vs4")

parent_all_acc3vs5_VIP_1 <- vip.plsda(parent_all_acc3vs5, parent_all_acc3vs5$ATTRIBUTE_acclimation, path, "parent_all_acc3vs5")

parent_all_acc4vs5_VIP_1 <- vip.plsda(parent_all_acc4vs5, parent_all_acc4vs5$ATTRIBUTE_acclimation, path, "parent_all_acc4vs5")
```

``` {r PLSDA known acc, echo=TRUE, warning=FALSE, message=FALSE}
path <- "/Users/cassieraker/Documents/_URI/_Research/Data/2019_PR_ch3_chemicalecology/2021_UTAustin_data/output/PLSDA_figs/"

#known direct parents by acclimation 
parent_known_acc1vs2_VIP_1 <- vip.plsda(parent_known_acc1vs2, parent_known_acc1vs2$ATTRIBUTE_acclimation, path, "parent_known_acc1vs2")

parent_known_acc1vs3_VIP_1 <- vip.plsda(parent_known_acc1vs3, parent_known_acc1vs3$ATTRIBUTE_acclimation, path, "parent_known_acc1vs3")

parent_known_acc1vs4_VIP_1 <- vip.plsda(parent_known_acc1vs4, parent_known_acc1vs4$ATTRIBUTE_acclimation, path, "parent_known_acc1vs4")

parent_known_acc1vs5_VIP_1 <- vip.plsda(parent_known_acc1vs5, parent_known_acc1vs5$ATTRIBUTE_acclimation, path, "parent_known_acc1vs5")

parent_known_acc2vs3_VIP_1 <- vip.plsda(parent_known_acc2vs3, parent_known_acc2vs3$ATTRIBUTE_acclimation, path, "parent_known_acc2vs3")

parent_known_acc2vs4_VIP_1 <- vip.plsda(parent_known_acc2vs4, parent_known_acc2vs4$ATTRIBUTE_acclimation, path, "parent_known_acc2vs4")

parent_known_acc2vs5_VIP_1 <- vip.plsda(parent_known_acc2vs5, parent_known_acc2vs5$ATTRIBUTE_acclimation, path, "parent_known_acc2vs5")

parent_known_acc3vs4_VIP_1 <- vip.plsda(parent_known_acc3vs4, parent_known_acc3vs4$ATTRIBUTE_acclimation, path, "parent_known_acc3vs4")

parent_known_acc3vs5_VIP_1 <- vip.plsda(parent_known_acc3vs5, parent_known_acc3vs5$ATTRIBUTE_acclimation, path, "parent_known_acc3vs5")

parent_known_acc4vs5_VIP_1 <- vip.plsda(parent_known_acc4vs5, parent_known_acc4vs5$ATTRIBUTE_acclimation, path, "parent_known_acc4vs5")
```

``` {r PLSDA all gen, echo=TRUE, warning=FALSE, message=FALSE}
path <- "/Users/cassieraker/Documents/_URI/_Research/Data/2019_PR_ch3_chemicalecology/2021_UTAustin_data/output/PLSDA_figs/"

#all direct parents by genotype
parent_all_AZvsBY_VIP_1 <- vip.plsda(parent_all_AZvsBY, parent_all_AZvsBY$ATTRIBUTE_genotype, path, "parent_all_AZvsBY")

parent_all_AZvsCX_VIP_1 <- vip.plsda(parent_all_AZvsCX, parent_all_AZvsCX$ATTRIBUTE_genotype, path, "parent_all_AZvsCX")

parent_all_AZvsDW_VIP_1 <- vip.plsda(parent_all_AZvsDW, parent_all_AZvsDW$ATTRIBUTE_genotype, path, "parent_all_AZvsDW")

parent_all_AZvsEV_VIP_1 <- vip.plsda(parent_all_AZvsEV, parent_all_AZvsEV$ATTRIBUTE_genotype, path, "parent_all_AZvsEV")

parent_all_AZvsFU_VIP_1 <- vip.plsda(parent_all_AZvsFU, parent_all_AZvsFU$ATTRIBUTE_genotype, path, "parent_all_AZvsFU")

parent_all_AZvsGT_VIP_1 <- vip.plsda(parent_all_AZvsGT, parent_all_AZvsGT$ATTRIBUTE_genotype, path, "parent_all_AZvsGT")

parent_all_AZvsHS_VIP_1 <- vip.plsda(parent_all_AZvsHS, parent_all_AZvsHS$ATTRIBUTE_genotype, path, "parent_all_AZvsHS")

parent_all_AZvsIR_VIP_1 <- vip.plsda(parent_all_AZvsIR, parent_all_AZvsIR$ATTRIBUTE_genotype, path, "parent_all_AZvsIR")

parent_all_AZvsJQ_VIP_1 <- vip.plsda(parent_all_AZvsJQ, parent_all_AZvsJQ$ATTRIBUTE_genotype, path, "parent_all_AZvsJQ")


parent_all_BYvsCX_VIP_1 <- vip.plsda(parent_all_BYvsCX, parent_all_BYvsCX$ATTRIBUTE_genotype, path, "parent_all_BYvsCX")

parent_all_BYvsDW_VIP_1 <- vip.plsda(parent_all_BYvsDW, parent_all_BYvsDW$ATTRIBUTE_genotype, path, "parent_all_BYvsDW")

parent_all_BYvsEV_VIP_1 <- vip.plsda(parent_all_BYvsEV, parent_all_BYvsEV$ATTRIBUTE_genotype, path, "parent_all_BYvsEV")

parent_all_BYvsFU_VIP_1 <- vip.plsda(parent_all_BYvsFU, parent_all_BYvsFU$ATTRIBUTE_genotype, path, "parent_all_BYvsFU")

parent_all_BYvsGT_VIP_1 <- vip.plsda(parent_all_BYvsGT, parent_all_BYvsGT$ATTRIBUTE_genotype, path, "parent_all_BYvsGT")

parent_all_BYvsHS_VIP_1 <- vip.plsda(parent_all_BYvsHS, parent_all_BYvsHS$ATTRIBUTE_genotype, path, "parent_all_BYvsHS")

parent_all_BYvsIR_VIP_1 <- vip.plsda(parent_all_BYvsIR, parent_all_BYvsIR$ATTRIBUTE_genotype, path, "parent_all_BYvsIR")

parent_all_BYvsJQ_VIP_1 <- vip.plsda(parent_all_BYvsJQ, parent_all_BYvsJQ$ATTRIBUTE_genotype, path, "parent_all_BYvsJQ")


parent_all_CXvsDW_VIP_1 <- vip.plsda(parent_all_CXvsDW, parent_all_CXvsDW$ATTRIBUTE_genotype, path, "parent_all_CXvsDW")

parent_all_CXvsEV_VIP_1 <- vip.plsda(parent_all_CXvsEV, parent_all_CXvsEV$ATTRIBUTE_genotype, path, "parent_all_CXvsEV")

parent_all_CXvsFU_VIP_1 <- vip.plsda(parent_all_CXvsFU, parent_all_CXvsFU$ATTRIBUTE_genotype, path, "parent_all_CXvsFU")

parent_all_CXvsGT_VIP_1 <- vip.plsda(parent_all_CXvsGT, parent_all_CXvsGT$ATTRIBUTE_genotype, path, "parent_all_CXvsGT")

parent_all_CXvsHS_VIP_1 <- vip.plsda(parent_all_CXvsHS, parent_all_CXvsHS$ATTRIBUTE_genotype, path, "parent_all_CXvsHS")

parent_all_CXvsIR_VIP_1 <- vip.plsda(parent_all_CXvsIR, parent_all_CXvsIR$ATTRIBUTE_genotype, path, "parent_all_CXvsIR")

parent_all_CXvsJQ_VIP_1 <- vip.plsda(parent_all_CXvsJQ, parent_all_CXvsJQ$ATTRIBUTE_genotype, path, "parent_all_CXvsJQ")


parent_all_DWvsEV_VIP_1 <- vip.plsda(parent_all_DWvsEV, parent_all_DWvsEV$ATTRIBUTE_genotype, path, "parent_all_DWvsEV")

parent_all_DWvsFU_VIP_1 <- vip.plsda(parent_all_DWvsFU, parent_all_DWvsFU$ATTRIBUTE_genotype, path, "parent_all_DWvsFU")

parent_all_DWvsGT_VIP_1 <- vip.plsda(parent_all_DWvsGT, parent_all_DWvsGT$ATTRIBUTE_genotype, path, "parent_all_DWvsGT")

parent_all_DWvsHS_VIP_1 <- vip.plsda(parent_all_DWvsHS, parent_all_DWvsHS$ATTRIBUTE_genotype, path, "parent_all_DWvsHS")

parent_all_DWvsIR_VIP_1 <- vip.plsda(parent_all_DWvsIR, parent_all_DWvsIR$ATTRIBUTE_genotype, path, "parent_all_DWvsIR")

parent_all_DWvsJQ_VIP_1 <- vip.plsda(parent_all_DWvsJQ, parent_all_DWvsJQ$ATTRIBUTE_genotype, path, "parent_all_DWvsJQ")


parent_all_EVvsFU_VIP_1 <- vip.plsda(parent_all_EVvsFU, parent_all_EVvsFU$ATTRIBUTE_genotype, path, "parent_all_EVvsFU")

parent_all_EVvsGT_VIP_1 <- vip.plsda(parent_all_EVvsGT, parent_all_EVvsGT$ATTRIBUTE_genotype, path, "parent_all_EVvsGT")

parent_all_EVvsHS_VIP_1 <- vip.plsda(parent_all_EVvsHS, parent_all_EVvsHS$ATTRIBUTE_genotype, path, "parent_all_EVvsHS")

parent_all_EVvsIR_VIP_1 <- vip.plsda(parent_all_EVvsIR, parent_all_EVvsIR$ATTRIBUTE_genotype, path, "parent_all_EVvsIR")

parent_all_EVvsJQ_VIP_1 <- vip.plsda(parent_all_EVvsJQ, parent_all_EVvsJQ$ATTRIBUTE_genotype, path, "parent_all_EVvsJQ")


parent_all_FUvsGT_VIP_1 <- vip.plsda(parent_all_FUvsGT, parent_all_FUvsGT$ATTRIBUTE_genotype, path, "parent_all_FUvsGT")

parent_all_FUvsHS_VIP_1 <- vip.plsda(parent_all_FUvsHS, parent_all_FUvsHS$ATTRIBUTE_genotype, path, "parent_all_FUvsHS")

parent_all_FUvsIR_VIP_1 <- vip.plsda(parent_all_FUvsIR, parent_all_FUvsIR$ATTRIBUTE_genotype, path, "parent_all_FUvsIR")

parent_all_FUvsJQ_VIP_1 <- vip.plsda(parent_all_FUvsJQ, parent_all_FUvsJQ$ATTRIBUTE_genotype, path, "parent_all_FUvsJQ")


parent_all_GTvsHS_VIP_1 <- vip.plsda(parent_all_GTvsHS, parent_all_GTvsHS$ATTRIBUTE_genotype, path, "parent_all_GTvsHS")

parent_all_GTvsIR_VIP_1 <- vip.plsda(parent_all_GTvsIR, parent_all_GTvsIR$ATTRIBUTE_genotype, path, "parent_all_GTvsIR")

parent_all_GTvsJQ_VIP_1 <- vip.plsda(parent_all_GTvsJQ, parent_all_GTvsJQ$ATTRIBUTE_genotype, path, "parent_all_GTvsJQ")


parent_all_HSvsIR_VIP_1 <- vip.plsda(parent_all_HSvsIR, parent_all_HSvsIR$ATTRIBUTE_genotype, path, "parent_all_HSvsIR")

parent_all_HSvsJQ_VIP_1 <- vip.plsda(parent_all_HSvsJQ, parent_all_HSvsJQ$ATTRIBUTE_genotype, path, "parent_all_HSvsJQ")


parent_all_IRvsJQ_VIP_1 <- vip.plsda(parent_all_IRvsJQ, parent_all_IRvsJQ$ATTRIBUTE_genotype, path, "parent_all_IRvsJQ")
```

``` {r PLSDA known gen, echo=TRUE, warning=FALSE, message=FALSE}
path <- "/Users/cassieraker/Documents/_URI/_Research/Data/2019_PR_ch3_chemicalecology/2021_UTAustin_data/output/PLSDA_figs/"

#known direct parents by genotype
parent_known_AZvsBY_VIP_1 <- vip.plsda(parent_known_AZvsBY, parent_known_AZvsBY$ATTRIBUTE_genotype, path, "parent_known_AZvsBY")

parent_known_AZvsCX_VIP_1 <- vip.plsda(parent_known_AZvsCX, parent_known_AZvsCX$ATTRIBUTE_genotype, path, "parent_known_AZvsCX")

parent_known_AZvsDW_VIP_1 <- vip.plsda(parent_known_AZvsDW, parent_known_AZvsDW$ATTRIBUTE_genotype, path, "parent_known_AZvsDW")

parent_known_AZvsEV_VIP_1 <- vip.plsda(parent_known_AZvsEV, parent_known_AZvsEV$ATTRIBUTE_genotype, path, "parent_known_AZvsEV")

parent_known_AZvsFU_VIP_1 <- vip.plsda(parent_known_AZvsFU, parent_known_AZvsFU$ATTRIBUTE_genotype, path, "parent_known_AZvsFU")

parent_known_AZvsGT_VIP_1 <- vip.plsda(parent_known_AZvsGT, parent_known_AZvsGT$ATTRIBUTE_genotype, path, "parent_known_AZvsGT")

parent_known_AZvsHS_VIP_1 <- vip.plsda(parent_known_AZvsHS, parent_known_AZvsHS$ATTRIBUTE_genotype, path, "parent_known_AZvsHS")

parent_known_AZvsIR_VIP_1 <- vip.plsda(parent_known_AZvsIR, parent_known_AZvsIR$ATTRIBUTE_genotype, path, "parent_known_AZvsIR")

parent_known_AZvsJQ_VIP_1 <- vip.plsda(parent_known_AZvsJQ, parent_known_AZvsJQ$ATTRIBUTE_genotype, path, "parent_known_AZvsJQ")


parent_known_BYvsCX_VIP_1 <- vip.plsda(parent_known_BYvsCX, parent_known_BYvsCX$ATTRIBUTE_genotype, path, "parent_known_BYvsCX")

parent_known_BYvsDW_VIP_1 <- vip.plsda(parent_known_BYvsDW, parent_known_BYvsDW$ATTRIBUTE_genotype, path, "parent_known_BYvsDW")

parent_known_BYvsEV_VIP_1 <- vip.plsda(parent_known_BYvsEV, parent_known_BYvsEV$ATTRIBUTE_genotype, path, "parent_known_BYvsEV")

parent_known_BYvsFU_VIP_1 <- vip.plsda(parent_known_BYvsFU, parent_known_BYvsFU$ATTRIBUTE_genotype, path, "parent_known_BYvsFU")

parent_known_BYvsGT_VIP_1 <- vip.plsda(parent_known_BYvsGT, parent_known_BYvsGT$ATTRIBUTE_genotype, path, "parent_known_BYvsGT")

parent_known_BYvsHS_VIP_1 <- vip.plsda(parent_known_BYvsHS, parent_known_BYvsHS$ATTRIBUTE_genotype, path, "parent_known_BYvsHS")

parent_known_BYvsIR_VIP_1 <- vip.plsda(parent_known_BYvsIR, parent_known_BYvsIR$ATTRIBUTE_genotype, path, "parent_known_BYvsIR")

parent_known_BYvsJQ_VIP_1 <- vip.plsda(parent_known_BYvsJQ, parent_known_BYvsJQ$ATTRIBUTE_genotype, path, "parent_known_BYvsJQ")


parent_known_CXvsDW_VIP_1 <- vip.plsda(parent_known_CXvsDW, parent_known_CXvsDW$ATTRIBUTE_genotype, path, "parent_known_CXvsDW")

parent_known_CXvsEV_VIP_1 <- vip.plsda(parent_known_CXvsEV, parent_known_CXvsEV$ATTRIBUTE_genotype, path, "parent_known_CXvsEV")

parent_known_CXvsFU_VIP_1 <- vip.plsda(parent_known_CXvsFU, parent_known_CXvsFU$ATTRIBUTE_genotype, path, "parent_known_CXvsFU")

parent_known_CXvsGT_VIP_1 <- vip.plsda(parent_known_CXvsGT, parent_known_CXvsGT$ATTRIBUTE_genotype, path, "parent_known_CXvsGT")

parent_known_CXvsHS_VIP_1 <- vip.plsda(parent_known_CXvsHS, parent_known_CXvsHS$ATTRIBUTE_genotype, path, "parent_known_CXvsHS")

parent_known_CXvsIR_VIP_1 <- vip.plsda(parent_known_CXvsIR, parent_known_CXvsIR$ATTRIBUTE_genotype, path, "parent_known_CXvsIR")

parent_known_CXvsJQ_VIP_1 <- vip.plsda(parent_known_CXvsJQ, parent_known_CXvsJQ$ATTRIBUTE_genotype, path, "parent_known_CXvsJQ")


parent_known_DWvsEV_VIP_1 <- vip.plsda(parent_known_DWvsEV, parent_known_DWvsEV$ATTRIBUTE_genotype, path, "parent_known_DWvsEV")

parent_known_DWvsFU_VIP_1 <- vip.plsda(parent_known_DWvsFU, parent_known_DWvsFU$ATTRIBUTE_genotype, path, "parent_known_DWvsFU")

parent_known_DWvsGT_VIP_1 <- vip.plsda(parent_known_DWvsGT, parent_known_DWvsGT$ATTRIBUTE_genotype, path, "parent_known_DWvsGT")

parent_known_DWvsHS_VIP_1 <- vip.plsda(parent_known_DWvsHS, parent_known_DWvsHS$ATTRIBUTE_genotype, path, "parent_known_DWvsHS")

parent_known_DWvsIR_VIP_1 <- vip.plsda(parent_known_DWvsIR, parent_known_DWvsIR$ATTRIBUTE_genotype, path, "parent_known_DWvsIR")

parent_known_DWvsJQ_VIP_1 <- vip.plsda(parent_known_DWvsJQ, parent_known_DWvsJQ$ATTRIBUTE_genotype, path, "parent_known_DWvsJQ")


parent_known_EVvsFU_VIP_1 <- vip.plsda(parent_known_EVvsFU, parent_known_EVvsFU$ATTRIBUTE_genotype, path, "parent_known_EVvsFU")

parent_known_EVvsGT_VIP_1 <- vip.plsda(parent_known_EVvsGT, parent_known_EVvsGT$ATTRIBUTE_genotype, path, "parent_known_EVvsGT")

parent_known_EVvsHS_VIP_1 <- vip.plsda(parent_known_EVvsHS, parent_known_EVvsHS$ATTRIBUTE_genotype, path, "parent_known_EVvsHS")

parent_known_EVvsIR_VIP_1 <- vip.plsda(parent_known_EVvsIR, parent_known_EVvsIR$ATTRIBUTE_genotype, path, "parent_known_EVvsIR")

parent_known_EVvsJQ_VIP_1 <- vip.plsda(parent_known_EVvsJQ, parent_known_EVvsJQ$ATTRIBUTE_genotype, path, "parent_known_EVvsJQ")


parent_known_FUvsGT_VIP_1 <- vip.plsda(parent_known_FUvsGT, parent_known_FUvsGT$ATTRIBUTE_genotype, path, "parent_known_FUvsGT")

parent_known_FUvsHS_VIP_1 <- vip.plsda(parent_known_FUvsHS, parent_known_FUvsHS$ATTRIBUTE_genotype, path, "parent_known_FUvsHS")

parent_known_FUvsIR_VIP_1 <- vip.plsda(parent_known_FUvsIR, parent_known_FUvsIR$ATTRIBUTE_genotype, path, "parent_known_FUvsIR")

parent_known_FUvsJQ_VIP_1 <- vip.plsda(parent_known_FUvsJQ, parent_known_FUvsJQ$ATTRIBUTE_genotype, path, "parent_known_FUvsJQ")


parent_known_GTvsHS_VIP_1 <- vip.plsda(parent_known_GTvsHS, parent_known_GTvsHS$ATTRIBUTE_genotype, path, "parent_known_GTvsHS")

parent_known_GTvsIR_VIP_1 <- vip.plsda(parent_known_GTvsIR, parent_known_GTvsIR$ATTRIBUTE_genotype, path, "parent_known_GTvsIR")

parent_known_GTvsJQ_VIP_1 <- vip.plsda(parent_known_GTvsJQ, parent_known_GTvsJQ$ATTRIBUTE_genotype, path, "parent_known_GTvsJQ")


parent_known_HSvsIR_VIP_1 <- vip.plsda(parent_known_HSvsIR, parent_known_HSvsIR$ATTRIBUTE_genotype, path, "parent_known_HSvsIR")

parent_known_HSvsJQ_VIP_1 <- vip.plsda(parent_known_HSvsJQ, parent_known_HSvsJQ$ATTRIBUTE_genotype, path, "parent_known_HSvsJQ")


parent_known_IRvsJQ_VIP_1 <- vip.plsda(parent_known_IRvsJQ, parent_known_IRvsJQ$ATTRIBUTE_genotype, path, "parent_known_IRvsJQ")
```


### Creating a t-test and FDR correction function
### Two tests: one for acclimation treatments, one for genotypes 
#not working because data subsets are still reading too many factor levels
```{r testFunction acc, echo=TRUE, warning=FALSE, message=FALSE}

vip.ttest <- function(data, 
                      VIP_data,
                      est1,
                      est2
                      ) { 
## Gather data frame and group by metabolite 
data <- droplevels(data)
data_gather <- data %>% gather(key = "DirectParent", value = "Count", -ATTRIBUTE_sampleID, -ATTRIBUTE_genotype, -ATTRIBUTE_acclimation, -ATTRIBUTE_dryweight) %>% dplyr::select("ATTRIBUTE_acclimation", "DirectParent", "Count")

data_gather$ATTRIBUTE_acclimation <- as.factor(data_gather$ATTRIBUTE_acclimation)

data_gather$ATTRIBUTE_acclimation <- droplevels(data_gather$ATTRIBUTE_acclimation)

data_gather <- dplyr::group_by(data_gather, DirectParent)
data_gather$ATTRIBUTE_acclimation <- droplevels(data_gather$ATTRIBUTE_acclimation)

# Select metabolites only present from the PLS-DA with VIPs >1
VIP_Select <- subset(data_gather, data_gather$DirectParent %in% VIP_data$DirectParent)

VIP_Select$ATTRIBUTE_acclimation <- droplevels(VIP_Select$ATTRIBUTE_acclimation)

#Looped t-test for all metabolites with VIPs >1, estimate 1 = Bleached_Hot, estimate 2 = Control
t.test <-do(VIP_Select, tidy(t.test(.$Count ~ .$ATTRIBUTE_acclimation,
                 alternative = "two.sided",
                 mu = 0,
                 paired = FALSE,
                 var.equal = FALSE,
                 conf.level = 0.95
                 )))

#adjust p value for the number of comparisons
t.test$p.adj<-p.adjust(t.test$p.value, method=c("fdr"), n=length(VIP_data$DirectParent)) #length = number of metabolites tested, false discovery rate method

# Filter for significantly different metabolites (p < 0.05)
t.test.fdr <- t.test %>% filter(p.adj <= 0.05)

# Filter for metabolites accumulated for est1
t.test.sig.up <- t.test.fdr %>% filter(estimate1 > estimate2)
t.test.sig.up$Enrichment.dir <- est1

# Filter for metabolites accumulated for est2
t.test.sig.down <- t.test.fdr %>% filter(estimate1 < estimate2)
t.test.sig.down$Enrichment.dir <- est2

#Combining data sets
t.test.sig.final <- rbind(t.test.sig.up, t.test.sig.down)
return(t.test.sig.final)
}
```
#THIS WORKS AS OF 7/5/22: ERROR WAS BECAUSE OF A SPACE IN A COLUMN NAME IN THE PREVIOUS SCRIPT

```{r testFunction gen, echo=TRUE, warning=FALSE, message=FALSE}

vip.ttest2 <- function(data, 
                      VIP_data,
                      est1,
                      est2
                      ) { 
## Gather data frame and group by metabolite 
data <- droplevels(data)
data_gather <- data %>% gather(key = "DirectParent", value = "Count", -ATTRIBUTE_sampleID, -ATTRIBUTE_genotype, -ATTRIBUTE_acclimation, -ATTRIBUTE_dryweight) %>% dplyr::select("ATTRIBUTE_genotype", "DirectParent", "Count")

data_gather$ATTRIBUTE_genotype <- as.factor(data_gather$ATTRIBUTE_genotype)

data_gather$ATTRIBUTE_genotype <- droplevels(data_gather$ATTRIBUTE_genotype)

data_gather <- dplyr::group_by(data_gather, DirectParent)
data_gather$ATTRIBUTE_genotype <- droplevels(data_gather$ATTRIBUTE_genotype)

# Select metabolites only present from the PLS-DA with VIPs >1
VIP_Select <- subset(data_gather, data_gather$DirectParent %in% VIP_data$DirectParent)

VIP_Select$ATTRIBUTE_genotype <- droplevels(VIP_Select$ATTRIBUTE_genotype)

#Looped t-test for all metabolites with VIPs >1, estimate 1 = Bleached_Hot, estimate 2 = Control
t.test <-do(VIP_Select, tidy(t.test(.$Count ~ .$ATTRIBUTE_genotype,
                 alternative = "two.sided",
                 mu = 0,
                 paired = FALSE,
                 var.equal = FALSE,
                 conf.level = 0.95
                 )))

#adjust p value for the number of comparisons
t.test$p.adj<-p.adjust(t.test$p.value, method=c("fdr"), n=length(VIP_data$DirectParent)) #length = number of metabolites tested, false discovery rate method

# Filter for significantly different metabolites (p < 0.05)
t.test.fdr <- t.test %>% filter(p.adj <= 0.05)

# Filter for metabolites accumulated for est1
t.test.sig.up <- t.test.fdr %>% filter(estimate1 > estimate2)
t.test.sig.up$Enrichment.dir <- est1

# Filter for metabolites accumulated for est2
t.test.sig.down <- t.test.fdr %>% filter(estimate1 < estimate2)
t.test.sig.down$Enrichment.dir <- est2

#Combining data sets
t.test.sig.final <- rbind(t.test.sig.up, t.test.sig.down)
return(t.test.sig.final)
}
```


# T-test and FDR correction of metabolites with VIPs >1

``` {r ttest all acc, echo=TRUE}
#all compounds by acclimation treatment

parent_all_acc1vs2_VIP_sig <- vip.ttest(parent_all_acc1vs2, parent_all_acc1vs2_VIP_1, "Acclimation 1", "Acclimation 2")

parent_all_acc1vs3_VIP_sig <- vip.ttest(parent_all_acc1vs3, parent_all_acc1vs3_VIP_1, "Acclimation 1", "Acclimation 3")

parent_all_acc1vs4_VIP_sig <- vip.ttest(parent_all_acc1vs4, parent_all_acc1vs4_VIP_1, "Acclimation 1", "Acclimation 4")

parent_all_acc1vs5_VIP_sig <- vip.ttest(parent_all_acc1vs5, parent_all_acc1vs5_VIP_1, "Acclimation 1", "Acclimation 5")


parent_all_acc2vs3_VIP_sig <- vip.ttest(parent_all_acc2vs3, parent_all_acc2vs3_VIP_1, "Acclimation 2", "Acclimation 3")

parent_all_acc2vs4_VIP_sig <- vip.ttest(parent_all_acc2vs4, parent_all_acc2vs4_VIP_1, "Acclimation 2", "Acclimation 4")

parent_all_acc2vs5_VIP_sig <- vip.ttest(parent_all_acc2vs5, parent_all_acc2vs5_VIP_1, "Acclimation 2", "Acclimation 5")


parent_all_acc3vs4_VIP_sig <- vip.ttest(parent_all_acc3vs4, parent_all_acc3vs4_VIP_1, "Acclimation 3", "Acclimation 4")

parent_all_acc3vs5_VIP_sig <- vip.ttest(parent_all_acc3vs5, parent_all_acc3vs5_VIP_1, "Acclimation 3", "Acclimation 5")


parent_all_acc4vs5_VIP_sig <- vip.ttest(parent_all_acc4vs5, parent_all_acc4vs5_VIP_1, "Acclimation 4", "Acclimation 5")
```

``` {r ttest known acc, echo=TRUE}
#known compounds by acclimation treatment

parent_known_acc1vs2_VIP_sig <- vip.ttest(parent_known_acc1vs2, parent_known_acc1vs2_VIP_1, "Acclimation 1", "Acclimation 2")

parent_known_acc1vs3_VIP_sig <- vip.ttest(parent_known_acc1vs3, parent_known_acc1vs3_VIP_1, "Acclimation 1", "Acclimation 3")

parent_known_acc1vs4_VIP_sig <- vip.ttest(parent_known_acc1vs4, parent_known_acc1vs4_VIP_1, "Acclimation 1", "Acclimation 4")

parent_known_acc1vs5_VIP_sig <- vip.ttest(parent_known_acc1vs5, parent_known_acc1vs5_VIP_1, "Acclimation 1", "Acclimation 5")


parent_known_acc2vs3_VIP_sig <- vip.ttest(parent_known_acc2vs3, parent_known_acc2vs3_VIP_1, "Acclimation 2", "Acclimation 3")

parent_known_acc2vs4_VIP_sig <- vip.ttest(parent_known_acc2vs4, parent_known_acc2vs4_VIP_1, "Acclimation 2", "Acclimation 4")

parent_known_acc2vs5_VIP_sig <- vip.ttest(parent_known_acc2vs5, parent_known_acc2vs5_VIP_1, "Acclimation 2", "Acclimation 5")


parent_known_acc3vs4_VIP_sig <- vip.ttest(parent_known_acc3vs4, parent_known_acc3vs4_VIP_1, "Acclimation 3", "Acclimation 4")

parent_known_acc3vs5_VIP_sig <- vip.ttest(parent_known_acc3vs5, parent_known_acc3vs5_VIP_1, "Acclimation 3", "Acclimation 5")


parent_known_acc4vs5_VIP_sig <- vip.ttest(parent_known_acc4vs5, parent_known_acc4vs5_VIP_1, "Acclimation 4", "Acclimation 5")
```

```{r ttest all gen, echo=TRUE}
#all compounds by genotype
parent_all_AZvsBY_VIP_sig <- vip.ttest2(parent_all_AZvsBY, parent_all_AZvsBY_VIP_1, "AZ", "BY")
parent_all_AZvsCX_VIP_sig <- vip.ttest2(parent_all_AZvsCX, parent_all_AZvsCX_VIP_1, "AZ", "CX")
parent_all_AZvsDW_VIP_sig <- vip.ttest2(parent_all_AZvsDW, parent_all_AZvsDW_VIP_1, "AZ", "DW")
parent_all_AZvsEV_VIP_sig <- vip.ttest2(parent_all_AZvsEV, parent_all_AZvsEV_VIP_1, "AZ", "EV")
parent_all_AZvsFU_VIP_sig <- vip.ttest2(parent_all_AZvsFU, parent_all_AZvsFU_VIP_1, "AZ", "FU")
parent_all_AZvsGT_VIP_sig <- vip.ttest2(parent_all_AZvsGT, parent_all_AZvsGT_VIP_1, "AZ", "GT")
parent_all_AZvsHS_VIP_sig <- vip.ttest2(parent_all_AZvsHS, parent_all_AZvsHS_VIP_1, "AZ", "HS")
parent_all_AZvsIR_VIP_sig <- vip.ttest2(parent_all_AZvsIR, parent_all_AZvsIR_VIP_1, "AZ", "IR")
parent_all_AZvsJQ_VIP_sig <- vip.ttest2(parent_all_AZvsJQ, parent_all_AZvsJQ_VIP_1, "AZ", "JQ")

parent_all_BYvsCX_VIP_sig <- vip.ttest2(parent_all_BYvsCX, parent_all_BYvsCX_VIP_1, "BY", "CX")
parent_all_BYvsDW_VIP_sig <- vip.ttest2(parent_all_BYvsDW, parent_all_BYvsDW_VIP_1, "BY", "DW")
parent_all_BYvsEV_VIP_sig <- vip.ttest2(parent_all_BYvsEV, parent_all_BYvsEV_VIP_1, "BY", "EV")
parent_all_BYvsFU_VIP_sig <- vip.ttest2(parent_all_BYvsFU, parent_all_BYvsFU_VIP_1, "BY", "FU")
parent_all_BYvsGT_VIP_sig <- vip.ttest2(parent_all_BYvsGT, parent_all_BYvsGT_VIP_1, "BY", "GT")
parent_all_BYvsHS_VIP_sig <- vip.ttest2(parent_all_BYvsHS, parent_all_BYvsHS_VIP_1, "BY", "HS")
parent_all_BYvsIR_VIP_sig <- vip.ttest2(parent_all_BYvsIR, parent_all_BYvsIR_VIP_1, "BY", "IR")
parent_all_BYvsJQ_VIP_sig <- vip.ttest2(parent_all_BYvsJQ, parent_all_BYvsJQ_VIP_1, "BY", "JQ")

parent_all_CXvsDW_VIP_sig <- vip.ttest2(parent_all_CXvsDW, parent_all_CXvsDW_VIP_1, "CX", "DW")
parent_all_CXvsEV_VIP_sig <- vip.ttest2(parent_all_CXvsEV, parent_all_CXvsEV_VIP_1, "CX", "EV")
parent_all_CXvsFU_VIP_sig <- vip.ttest2(parent_all_CXvsFU, parent_all_CXvsFU_VIP_1, "CX", "FU")
parent_all_CXvsGT_VIP_sig <- vip.ttest2(parent_all_CXvsGT, parent_all_CXvsGT_VIP_1, "CX", "GT")
parent_all_CXvsHS_VIP_sig <- vip.ttest2(parent_all_CXvsHS, parent_all_CXvsHS_VIP_1, "CX", "HS")
parent_all_CXvsIR_VIP_sig <- vip.ttest2(parent_all_CXvsIR, parent_all_CXvsIR_VIP_1, "CX", "IR")
parent_all_CXvsJQ_VIP_sig <- vip.ttest2(parent_all_CXvsJQ, parent_all_CXvsJQ_VIP_1, "CX", "JQ")

parent_all_DWvsEV_VIP_sig <- vip.ttest2(parent_all_DWvsEV, parent_all_DWvsEV_VIP_1, "DW", "EV")
parent_all_DWvsFU_VIP_sig <- vip.ttest2(parent_all_DWvsFU, parent_all_DWvsFU_VIP_1, "DW", "FU")
parent_all_DWvsGT_VIP_sig <- vip.ttest2(parent_all_DWvsGT, parent_all_DWvsGT_VIP_1, "DW", "GT")
parent_all_DWvsHS_VIP_sig <- vip.ttest2(parent_all_DWvsHS, parent_all_DWvsHS_VIP_1, "DW", "HS")
parent_all_DWvsIR_VIP_sig <- vip.ttest2(parent_all_DWvsIR, parent_all_DWvsIR_VIP_1, "DW", "IR")
parent_all_DWvsJQ_VIP_sig <- vip.ttest2(parent_all_DWvsJQ, parent_all_DWvsJQ_VIP_1, "DW", "JQ")

parent_all_EVvsFU_VIP_sig <- vip.ttest2(parent_all_EVvsFU, parent_all_EVvsFU_VIP_1, "EV", "FU")
parent_all_EVvsGT_VIP_sig <- vip.ttest2(parent_all_EVvsGT, parent_all_EVvsGT_VIP_1, "EV", "GT")
parent_all_EVvsHS_VIP_sig <- vip.ttest2(parent_all_EVvsHS, parent_all_EVvsHS_VIP_1, "EV", "HS")
parent_all_EVvsIR_VIP_sig <- vip.ttest2(parent_all_EVvsIR, parent_all_EVvsIR_VIP_1, "EV", "IR")
parent_all_EVvsJQ_VIP_sig <- vip.ttest2(parent_all_EVvsJQ, parent_all_EVvsJQ_VIP_1, "EV", "JQ")

parent_all_FUvsGT_VIP_sig <- vip.ttest2(parent_all_FUvsGT, parent_all_FUvsGT_VIP_1, "FU", "GT")
parent_all_FUvsHS_VIP_sig <- vip.ttest2(parent_all_FUvsHS, parent_all_FUvsHS_VIP_1, "FU", "HS")
parent_all_FUvsIR_VIP_sig <- vip.ttest2(parent_all_FUvsIR, parent_all_FUvsIR_VIP_1, "FU", "IR")
parent_all_FUvsJQ_VIP_sig <- vip.ttest2(parent_all_FUvsJQ, parent_all_FUvsJQ_VIP_1, "FU", "JQ")

parent_all_GTvsHS_VIP_sig <- vip.ttest2(parent_all_GTvsHS, parent_all_GTvsHS_VIP_1, "GT", "HS")
parent_all_GTvsIR_VIP_sig <- vip.ttest2(parent_all_GTvsIR, parent_all_GTvsIR_VIP_1, "GT", "IR")
parent_all_GTvsJQ_VIP_sig <- vip.ttest2(parent_all_GTvsJQ, parent_all_GTvsJQ_VIP_1, "GT", "JQ")

parent_all_HSvsIR_VIP_sig <- vip.ttest2(parent_all_HSvsIR, parent_all_HSvsIR_VIP_1, "HS", "IR")
parent_all_HSvsJQ_VIP_sig <- vip.ttest2(parent_all_HSvsJQ, parent_all_HSvsJQ_VIP_1, "HS", "JQ")

parent_all_IRvsJQ_VIP_sig <- vip.ttest2(parent_all_IRvsJQ, parent_all_IRvsJQ_VIP_1, "IR", "JQ")
```

```{r ttest known gen, echo=TRUE}
#all compounds by genotype
parent_known_AZvsBY_VIP_sig <- vip.ttest2(parent_known_AZvsBY, parent_known_AZvsBY_VIP_1, "AZ", "BY")
parent_known_AZvsCX_VIP_sig <- vip.ttest2(parent_known_AZvsCX, parent_known_AZvsCX_VIP_1, "AZ", "CX")
parent_known_AZvsDW_VIP_sig <- vip.ttest2(parent_known_AZvsDW, parent_known_AZvsDW_VIP_1, "AZ", "DW")
parent_known_AZvsEV_VIP_sig <- vip.ttest2(parent_known_AZvsEV, parent_known_AZvsEV_VIP_1, "AZ", "EV")
parent_known_AZvsFU_VIP_sig <- vip.ttest2(parent_known_AZvsFU, parent_known_AZvsFU_VIP_1, "AZ", "FU")
parent_known_AZvsGT_VIP_sig <- vip.ttest2(parent_known_AZvsGT, parent_known_AZvsGT_VIP_1, "AZ", "GT")
parent_known_AZvsHS_VIP_sig <- vip.ttest2(parent_known_AZvsHS, parent_known_AZvsHS_VIP_1, "AZ", "HS")
parent_known_AZvsIR_VIP_sig <- vip.ttest2(parent_known_AZvsIR, parent_known_AZvsIR_VIP_1, "AZ", "IR")
parent_known_AZvsJQ_VIP_sig <- vip.ttest2(parent_known_AZvsJQ, parent_known_AZvsJQ_VIP_1, "AZ", "JQ")

parent_known_BYvsCX_VIP_sig <- vip.ttest2(parent_known_BYvsCX, parent_known_BYvsCX_VIP_1, "BY", "CX")
parent_known_BYvsDW_VIP_sig <- vip.ttest2(parent_known_BYvsDW, parent_known_BYvsDW_VIP_1, "BY", "DW")
parent_known_BYvsEV_VIP_sig <- vip.ttest2(parent_known_BYvsEV, parent_known_BYvsEV_VIP_1, "BY", "EV")
parent_known_BYvsFU_VIP_sig <- vip.ttest2(parent_known_BYvsFU, parent_known_BYvsFU_VIP_1, "BY", "FU")
parent_known_BYvsGT_VIP_sig <- vip.ttest2(parent_known_BYvsGT, parent_known_BYvsGT_VIP_1, "BY", "GT")
parent_known_BYvsHS_VIP_sig <- vip.ttest2(parent_known_BYvsHS, parent_known_BYvsHS_VIP_1, "BY", "HS")
parent_known_BYvsIR_VIP_sig <- vip.ttest2(parent_known_BYvsIR, parent_known_BYvsIR_VIP_1, "BY", "IR")
parent_known_BYvsJQ_VIP_sig <- vip.ttest2(parent_known_BYvsJQ, parent_known_BYvsJQ_VIP_1, "BY", "JQ")

parent_known_CXvsDW_VIP_sig <- vip.ttest2(parent_known_CXvsDW, parent_known_CXvsDW_VIP_1, "CX", "DW")
parent_known_CXvsEV_VIP_sig <- vip.ttest2(parent_known_CXvsEV, parent_known_CXvsEV_VIP_1, "CX", "EV")
parent_known_CXvsFU_VIP_sig <- vip.ttest2(parent_known_CXvsFU, parent_known_CXvsFU_VIP_1, "CX", "FU")
parent_known_CXvsGT_VIP_sig <- vip.ttest2(parent_known_CXvsGT, parent_known_CXvsGT_VIP_1, "CX", "GT")
parent_known_CXvsHS_VIP_sig <- vip.ttest2(parent_known_CXvsHS, parent_known_CXvsHS_VIP_1, "CX", "HS")
parent_known_CXvsIR_VIP_sig <- vip.ttest2(parent_known_CXvsIR, parent_known_CXvsIR_VIP_1, "CX", "IR")
parent_known_CXvsJQ_VIP_sig <- vip.ttest2(parent_known_CXvsJQ, parent_known_CXvsJQ_VIP_1, "CX", "JQ")

parent_known_DWvsEV_VIP_sig <- vip.ttest2(parent_known_DWvsEV, parent_known_DWvsEV_VIP_1, "DW", "EV")
parent_known_DWvsFU_VIP_sig <- vip.ttest2(parent_known_DWvsFU, parent_known_DWvsFU_VIP_1, "DW", "FU")
parent_known_DWvsGT_VIP_sig <- vip.ttest2(parent_known_DWvsGT, parent_known_DWvsGT_VIP_1, "DW", "GT")
parent_known_DWvsHS_VIP_sig <- vip.ttest2(parent_known_DWvsHS, parent_known_DWvsHS_VIP_1, "DW", "HS")
parent_known_DWvsIR_VIP_sig <- vip.ttest2(parent_known_DWvsIR, parent_known_DWvsIR_VIP_1, "DW", "IR")
parent_known_DWvsJQ_VIP_sig <- vip.ttest2(parent_known_DWvsJQ, parent_known_DWvsJQ_VIP_1, "DW", "JQ")

parent_known_EVvsFU_VIP_sig <- vip.ttest2(parent_known_EVvsFU, parent_known_EVvsFU_VIP_1, "EV", "FU")
parent_known_EVvsGT_VIP_sig <- vip.ttest2(parent_known_EVvsGT, parent_known_EVvsGT_VIP_1, "EV", "GT")
parent_known_EVvsHS_VIP_sig <- vip.ttest2(parent_known_EVvsHS, parent_known_EVvsHS_VIP_1, "EV", "HS")
parent_known_EVvsIR_VIP_sig <- vip.ttest2(parent_known_EVvsIR, parent_known_EVvsIR_VIP_1, "EV", "IR")
parent_known_EVvsJQ_VIP_sig <- vip.ttest2(parent_known_EVvsJQ, parent_known_EVvsJQ_VIP_1, "EV", "JQ")

parent_known_FUvsGT_VIP_sig <- vip.ttest2(parent_known_FUvsGT, parent_known_FUvsGT_VIP_1, "FU", "GT")
parent_known_FUvsHS_VIP_sig <- vip.ttest2(parent_known_FUvsHS, parent_known_FUvsHS_VIP_1, "FU", "HS")
parent_known_FUvsIR_VIP_sig <- vip.ttest2(parent_known_FUvsIR, parent_known_FUvsIR_VIP_1, "FU", "IR")
parent_known_FUvsJQ_VIP_sig <- vip.ttest2(parent_known_FUvsJQ, parent_known_FUvsJQ_VIP_1, "FU", "JQ")

parent_known_GTvsHS_VIP_sig <- vip.ttest2(parent_known_GTvsHS, parent_known_GTvsHS_VIP_1, "GT", "HS")
parent_known_GTvsIR_VIP_sig <- vip.ttest2(parent_known_GTvsIR, parent_known_GTvsIR_VIP_1, "GT", "IR")
parent_known_GTvsJQ_VIP_sig <- vip.ttest2(parent_known_GTvsJQ, parent_known_GTvsJQ_VIP_1, "GT", "JQ")

parent_known_HSvsIR_VIP_sig <- vip.ttest2(parent_known_HSvsIR, parent_known_HSvsIR_VIP_1, "HS", "IR")
parent_known_HSvsJQ_VIP_sig <- vip.ttest2(parent_known_HSvsJQ, parent_known_HSvsJQ_VIP_1, "HS", "JQ")

parent_known_IRvsJQ_VIP_sig <- vip.ttest2(parent_known_IRvsJQ, parent_known_IRvsJQ_VIP_1, "IR", "JQ")
```


### Assigning known and unknown values to All detected metabolite datasets

``` {r knownunknown acc, echo=TRUE, warning=FALSE, message=FALSE}
parent_all_acc1vs2_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc1vs2_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc1vs3_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc1vs3_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc1vs4_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc1vs4_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc1vs5_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc1vs5_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_acc2vs3_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc2vs3_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc2vs4_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc2vs4_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc2vs5_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc2vs5_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_acc3vs4_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc3vs4_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc3vs5_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc3vs5_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_acc4vs5_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc4vs5_VIP_sig$DirectParent), 'Unknown', 'Identified')
```

``` {r knownunknown gen, echo=TRUE, warning=FALSE, message=FALSE}
parent_all_AZvsBY_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsBY_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsCX_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsCX_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsDW_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsDW_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsEV_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsEV_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsFU_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsFU_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_BYvsCX_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsCX_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsDW_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsDW_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsEV_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsEV_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsFU_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsFU_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_CXvsDW_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsDW_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsEV_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsEV_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsFU_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsFU_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_DWvsEV_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsEV_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_DWvsFU_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsFU_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_DWvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_DWvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_DWvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_DWvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_EVvsFU_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_EVvsFU_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_EVvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_EVvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_EVvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_EVvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_EVvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_EVvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_EVvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_EVvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_FUvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_FUvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_FUvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_FUvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_FUvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_FUvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_FUvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_FUvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_GTvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_GTvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_GTvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_GTvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_GTvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_GTvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_HSvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_HSvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_HSvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_HSvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_IRvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_IRvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')
```


### Summary statsitics of known vs unknown metabolites

``` {r Knownstats acc, echo=TRUE, warning=FALSE, message=FALSE}
path2 <- "/Users/cassieraker/Documents/_URI/_Research/Data/2019_PR_ch3_chemicalecology/2021_UTAustin_data/output/"

filenames <- list.files(path = path2, pattern="csv$") #figure out how to loop this

parent_all_acc1vs2_VIP_table <- as.data.frame(t(table(parent_all_acc1vs2_VIP_sig['Feature.status'])))

parent_all_acc1vs3_VIP_table <- as.data.frame(t(table(parent_all_acc1vs3_VIP_sig['Feature.status'])))

parent_all_acc1vs4_VIP_table <- as.data.frame(t(table(parent_all_acc1vs4_VIP_sig['Feature.status'])))

parent_all_acc1vs5_VIP_table <- as.data.frame(t(table(parent_all_acc1vs5_VIP_sig['Feature.status'])))


parent_all_acc2vs3_VIP_table <- as.data.frame(t(table(parent_all_acc2vs3_VIP_sig['Feature.status'])))

parent_all_acc2vs4_VIP_table <- as.data.frame(t(table(parent_all_acc2vs4_VIP_sig['Feature.status'])))

parent_all_acc2vs5_VIP_table <- as.data.frame(t(table(parent_all_acc2vs5_VIP_sig['Feature.status'])))


parent_all_acc3vs4_VIP_table <- as.data.frame(t(table(parent_all_acc3vs4_VIP_sig['Feature.status'])))

parent_all_acc3vs5_VIP_table <- as.data.frame(t(table(parent_all_acc3vs5_VIP_sig['Feature.status'])))

parent_all_acc4vs5_VIP_table <- as.data.frame(t(table(parent_all_acc4vs5_VIP_sig['Feature.status'])))


parent_all_acc1vs2_VIP_table$Comparison <- "acc1vs2"
parent_all_acc1vs3_VIP_table$Comparison <- "acc1vs3"
parent_all_acc1vs4_VIP_table$Comparison <- "acc1vs4"
parent_all_acc1vs5_VIP_table$Comparison <- "acc1vs5"

parent_all_acc2vs3_VIP_table$Comparison <- "acc2vs3"
parent_all_acc2vs4_VIP_table$Comparison <- "acc2vs4"
parent_all_acc2vs5_VIP_table$Comparison <- "acc2vs5"

parent_all_acc3vs4_VIP_table$Comparison <- "acc3vs4"
#parent_all_acc3vs5_VIP_table$Comparison <- "acc3vs5" #Error in `$<-.data.frame`(`*tmp*`, Comparison, value = "acc3vs5") : replacement has 1 row, data has 0

parent_all_acc4vs5_VIP_table$Comparison <- "acc4vs5"


feat.stat.table <- rbind(parent_all_acc1vs2_VIP_table, 
                         parent_all_acc1vs3_VIP_table, 
                         parent_all_acc1vs4_VIP_table, 
                         parent_all_acc1vs5_VIP_table, 
                         parent_all_acc2vs3_VIP_table, 
                         parent_all_acc2vs4_VIP_table, 
                         parent_all_acc2vs5_VIP_table, 
                         parent_all_acc3vs4_VIP_table, 
                         parent_all_acc4vs5_VIP_table)


feat.stat.table.acc <- feat.stat.table %>% spread(key = Var1, value = Freq)

feat.stat.table.acc

write.csv(feat.stat.table.acc, "/Users/cassieraker/Documents/_URI/_Research/Data/2019_PR_ch3_chemicalecology/2021_UTAustin_data/output/feat.stat.table.acc.csv")
```

``` {r Knownstats gen, echo=TRUE, warning=FALSE, message=FALSE}
path2 <- "/Users/cassieraker/Documents/_URI/_Research/Data/2019_PR_ch3_chemicalecology/2021_UTAustin_data/output/"

filenames <- list.files(path = path2, pattern="csv$") #figure out how to loop this

parent_all_AZvsBY_VIP_table <- as.data.frame(t(table(parent_all_AZvsBY_VIP_sig['Feature.status'])))

parent_all_AZvsCX_VIP_table <- as.data.frame(t(table(parent_all_AZvsCX_VIP_sig['Feature.status'])))

parent_all_AZvsDW_VIP_table <- as.data.frame(t(table(parent_all_AZvsDW_VIP_sig['Feature.status'])))

parent_all_AZvsEV_VIP_table <- as.data.frame(t(table(parent_all_AZvsEV_VIP_sig['Feature.status'])))

parent_all_AZvsFU_VIP_table <- as.data.frame(t(table(parent_all_AZvsFU_VIP_sig['Feature.status'])))

parent_all_AZvsGT_VIP_table <- as.data.frame(t(table(parent_all_AZvsGT_VIP_sig['Feature.status'])))

parent_all_AZvsHS_VIP_table <- as.data.frame(t(table(parent_all_AZvsHS_VIP_sig['Feature.status'])))

parent_all_AZvsIR_VIP_table <- as.data.frame(t(table(parent_all_AZvsIR_VIP_sig['Feature.status'])))

parent_all_AZvsJQ_VIP_table <- as.data.frame(t(table(parent_all_AZvsJQ_VIP_sig['Feature.status'])))


parent_all_BYvsCX_VIP_table <- as.data.frame(t(table(parent_all_BYvsCX_VIP_sig['Feature.status'])))

parent_all_BYvsDW_VIP_table <- as.data.frame(t(table(parent_all_BYvsDW_VIP_sig['Feature.status'])))

parent_all_BYvsEV_VIP_table <- as.data.frame(t(table(parent_all_BYvsEV_VIP_sig['Feature.status'])))

parent_all_BYvsFU_VIP_table <- as.data.frame(t(table(parent_all_BYvsFU_VIP_sig['Feature.status'])))

parent_all_BYvsGT_VIP_table <- as.data.frame(t(table(parent_all_BYvsGT_VIP_sig['Feature.status'])))

parent_all_BYvsHS_VIP_table <- as.data.frame(t(table(parent_all_BYvsHS_VIP_sig['Feature.status'])))

parent_all_BYvsIR_VIP_table <- as.data.frame(t(table(parent_all_BYvsIR_VIP_sig['Feature.status'])))

parent_all_BYvsJQ_VIP_table <- as.data.frame(t(table(parent_all_BYvsJQ_VIP_sig['Feature.status'])))


parent_all_CXvsDW_VIP_table <- as.data.frame(t(table(parent_all_CXvsDW_VIP_sig['Feature.status'])))

parent_all_CXvsEV_VIP_table <- as.data.frame(t(table(parent_all_CXvsEV_VIP_sig['Feature.status'])))

parent_all_CXvsFU_VIP_table <- as.data.frame(t(table(parent_all_CXvsFU_VIP_sig['Feature.status'])))

parent_all_CXvsGT_VIP_table <- as.data.frame(t(table(parent_all_CXvsGT_VIP_sig['Feature.status'])))

parent_all_CXvsHS_VIP_table <- as.data.frame(t(table(parent_all_CXvsHS_VIP_sig['Feature.status'])))

parent_all_CXvsIR_VIP_table <- as.data.frame(t(table(parent_all_CXvsIR_VIP_sig['Feature.status'])))

parent_all_CXvsJQ_VIP_table <- as.data.frame(t(table(parent_all_CXvsJQ_VIP_sig['Feature.status'])))


parent_all_DWvsEV_VIP_table <- as.data.frame(t(table(parent_all_DWvsEV_VIP_sig['Feature.status'])))

parent_all_DWvsFU_VIP_table <- as.data.frame(t(table(parent_all_DWvsFU_VIP_sig['Feature.status'])))

parent_all_DWvsGT_VIP_table <- as.data.frame(t(table(parent_all_DWvsGT_VIP_sig['Feature.status'])))

parent_all_DWvsHS_VIP_table <- as.data.frame(t(table(parent_all_DWvsHS_VIP_sig['Feature.status'])))

parent_all_DWvsIR_VIP_table <- as.data.frame(t(table(parent_all_DWvsIR_VIP_sig['Feature.status'])))

parent_all_DWvsJQ_VIP_table <- as.data.frame(t(table(parent_all_DWvsJQ_VIP_sig['Feature.status'])))


parent_all_EVvsFU_VIP_table <- as.data.frame(t(table(parent_all_EVvsFU_VIP_sig['Feature.status'])))

parent_all_EVvsGT_VIP_table <- as.data.frame(t(table(parent_all_EVvsGT_VIP_sig['Feature.status'])))

parent_all_EVvsHS_VIP_table <- as.data.frame(t(table(parent_all_EVvsHS_VIP_sig['Feature.status'])))

parent_all_EVvsIR_VIP_table <- as.data.frame(t(table(parent_all_EVvsIR_VIP_sig['Feature.status'])))

parent_all_EVvsJQ_VIP_table <- as.data.frame(t(table(parent_all_EVvsJQ_VIP_sig['Feature.status'])))


parent_all_FUvsGT_VIP_table <- as.data.frame(t(table(parent_all_FUvsGT_VIP_sig['Feature.status'])))

parent_all_FUvsHS_VIP_table <- as.data.frame(t(table(parent_all_FUvsHS_VIP_sig['Feature.status'])))

parent_all_FUvsIR_VIP_table <- as.data.frame(t(table(parent_all_FUvsIR_VIP_sig['Feature.status'])))

parent_all_FUvsJQ_VIP_table <- as.data.frame(t(table(parent_all_FUvsJQ_VIP_sig['Feature.status'])))


parent_all_GTvsHS_VIP_table <- as.data.frame(t(table(parent_all_GTvsHS_VIP_sig['Feature.status'])))

parent_all_GTvsIR_VIP_table <- as.data.frame(t(table(parent_all_GTvsIR_VIP_sig['Feature.status'])))

parent_all_GTvsJQ_VIP_table <- as.data.frame(t(table(parent_all_GTvsJQ_VIP_sig['Feature.status'])))


parent_all_HSvsIR_VIP_table <- as.data.frame(t(table(parent_all_HSvsIR_VIP_sig['Feature.status'])))

parent_all_HSvsJQ_VIP_table <- as.data.frame(t(table(parent_all_HSvsJQ_VIP_sig['Feature.status'])))


parent_all_IRvsJQ_VIP_table <- as.data.frame(t(table(parent_all_IRvsJQ_VIP_sig['Feature.status'])))


parent_all_AZvsBY_VIP_table$Comparison <- "AZvsBY"
#parent_all_AZvsCX_VIP_table$Comparison <- "AZvsCX"
#parent_all_AZvsDW_VIP_table$Comparison <- "AZvsDW"
#parent_all_AZvsEV_VIP_table$Comparison <- "AZvsEV"
#parent_all_AZvsFU_VIP_table$Comparison <- "AZvsFU"
#parent_all_AZvsGT_VIP_table$Comparison <- "AZvsGT"
#parent_all_AZvsHS_VIP_table$Comparison <- "AZvsHS"
#parent_all_AZvsIR_VIP_table$Comparison <- "AZvsIR"
#parent_all_AZvsJQ_VIP_table$Comparison <- "AZvsJQ"

parent_all_BYvsCX_VIP_table$Comparison <- "BYvsCX"
parent_all_BYvsDW_VIP_table$Comparison <- "BYvsDW"
parent_all_BYvsEV_VIP_table$Comparison <- "BYvsEV"
parent_all_BYvsFU_VIP_table$Comparison <- "BYvsFU"
#parent_all_BYvsGT_VIP_table$Comparison <- "BYvsGT"
#parent_all_BYvsHS_VIP_table$Comparison <- "BYvsHS"
#parent_all_BYvsIR_VIP_table$Comparison <- "BYvsIR"
parent_all_BYvsJQ_VIP_table$Comparison <- "BYvsJQ"

#parent_all_CXvsDW_VIP_table$Comparison <- "CXvsDW"
#parent_all_CXvsEV_VIP_table$Comparison <- "CXvsEV"
#parent_all_CXvsFU_VIP_table$Comparison <- "CXvsFU"
#parent_all_CXvsGT_VIP_table$Comparison <- "CXvsGT"
#parent_all_CXvsHS_VIP_table$Comparison <- "CXvsHS"
#parent_all_CXvsIR_VIP_table$Comparison <- "CXvsIR"
#parent_all_CXvsJQ_VIP_table$Comparison <- "CXvsJQ"

#parent_all_DWvsEV_VIP_table$Comparison <- "DWvsEV"
#parent_all_DWvsFU_VIP_table$Comparison <- "DWvsFU"
#parent_all_DWvsGT_VIP_table$Comparison <- "DWvsGT"
#parent_all_DWvsHS_VIP_table$Comparison <- "DWvsHS"
#parent_all_DWvsIR_VIP_table$Comparison <- "DWvsIR"
#parent_all_DWvsJQ_VIP_table$Comparison <- "DWvsJQ"

parent_all_EVvsFU_VIP_table$Comparison <- "EVvsFU"
#parent_all_EVvsGT_VIP_table$Comparison <- "EVvsGT"
#parent_all_EVvsHS_VIP_table$Comparison <- "EVvsHS"
parent_all_EVvsIR_VIP_table$Comparison <- "EVvsIR"
parent_all_EVvsJQ_VIP_table$Comparison <- "EVvsJQ"

#parent_all_FUvsGT_VIP_table$Comparison <- "FUvsGT"
#parent_all_FUvsHS_VIP_table$Comparison <- "FUvsHS"
parent_all_FUvsIR_VIP_table$Comparison <- "FUvsIR"
#parent_all_FUvsJQ_VIP_table$Comparison <- "FUvsJQ"

#parent_all_GTvsHS_VIP_table$Comparison <- "GTvsHS"
#parent_all_GTvsIR_VIP_table$Comparison <- "GTvsIR"
#parent_all_GTvsJQ_VIP_table$Comparison <- "GTvsJQ"

#parent_all_HSvsIR_VIP_table$Comparison <- "HSvsIR"
#parent_all_HSvsJQ_VIP_table$Comparison <- "HSvsJQ"

#parent_all_IRvsJQ_VIP_table$Comparison <- "IRvsJQ"


feat.stat.table2 <- rbind(parent_all_AZvsBY_VIP_table, 
                         parent_all_BYvsCX_VIP_table, 
                         parent_all_BYvsDW_VIP_table, 
                         parent_all_BYvsEV_VIP_table, 
                         parent_all_BYvsFU_VIP_table, 
                         parent_all_BYvsJQ_VIP_table, 
                         parent_all_EVvsFU_VIP_table, 
                         parent_all_EVvsIR_VIP_table, 
                         parent_all_EVvsJQ_VIP_table, 
                         parent_all_FUvsIR_VIP_table)

feat.stat.table.gen <- feat.stat.table2 %>% spread(key = Var1, value = Freq)

feat.stat.table.gen

write.csv(feat.stat.table.gen, "/Users/cassieraker/Documents/_URI/_Research/Data/2019_PR_ch3_chemicalecology/2021_UTAustin_data/output/feat.stat.table.gen.csv")
```


### VIP plotting after t-test validation
                         
``` {r prepare VIP plot acc, echo=TRUE, warning=FALSE, message=FALSE}
# Attaching VIPs to t-test dataframes
parent_all_acc1vs2_VIP_sig2 <- merge(parent_all_acc1vs2_VIP_sig, parent_all_acc1vs2_VIP_1, by = "DirectParent")

parent_all_acc1vs3_VIP_sig2 <- merge(parent_all_acc1vs3_VIP_sig, parent_all_acc1vs3_VIP_1, by = "DirectParent")

parent_all_acc1vs4_VIP_sig2 <- merge(parent_all_acc1vs4_VIP_sig, parent_all_acc1vs4_VIP_1, by = "DirectParent")

parent_all_acc1vs5_VIP_sig2 <- merge(parent_all_acc1vs5_VIP_sig, parent_all_acc1vs5_VIP_1, by = "DirectParent")


parent_all_acc2vs3_VIP_sig2 <- merge(parent_all_acc2vs3_VIP_sig, parent_all_acc2vs3_VIP_1, by = "DirectParent")

parent_all_acc2vs4_VIP_sig2 <- merge(parent_all_acc2vs4_VIP_sig, parent_all_acc2vs4_VIP_1, by = "DirectParent")

parent_all_acc2vs5_VIP_sig2 <- merge(parent_all_acc2vs5_VIP_sig, parent_all_acc2vs5_VIP_1, by = "DirectParent")


parent_all_acc3vs4_VIP_sig2 <- merge(parent_all_acc3vs4_VIP_sig, parent_all_acc3vs4_VIP_1, by = "DirectParent")

parent_all_acc4vs5_VIP_sig2 <- merge(parent_all_acc4vs5_VIP_sig, parent_all_acc4vs5_VIP_1, by = "DirectParent")

```

```{r VIP plot acc, echo=TRUE, warning=FALSE, message=FALSE}
#View(parent_all_acc1vs3_VIP_sig2)
```

```{r}
library(forcats)

#plot one comparison
plot_1vs3 <- parent_all_acc1vs3_VIP_sig2 %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) +
  #scale_colour_manual(values=c("#8B0046", "#468B00")) +
  #scale_fill_manual(values=c("#8B0046", "#468B00")) +
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_1vs3
```

```{r}
#plot one comparison
plot_4vs5 <- parent_all_acc4vs5_VIP_sig2 %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) +
  #scale_colour_manual(values=c("#8B0046", "#468B00")) +
  #scale_fill_manual(values=c("#8B0046", "#468B00")) +
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_4vs5
```

```{r combine VIP plot files}
parent_all_COMBO_sig2 <- rbind(parent_all_acc1vs2_VIP_sig2, parent_all_acc1vs3_VIP_sig2, parent_all_acc1vs4_VIP_sig2, parent_all_acc1vs5_VIP_sig2, parent_all_acc2vs3_VIP_sig2, parent_all_acc2vs4_VIP_sig2, parent_all_acc2vs5_VIP_sig2, parent_all_acc3vs4_VIP_sig2, parent_all_acc4vs5_VIP_sig2)
```

```{r}
plot_COMBO <- parent_all_COMBO_sig2 %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) + 
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_COMBO
```

```{r}
#filter only repeated metabolites 
#parent_all_COMBO_sig3 <- parent_all_COMBO_sig2 %>% group_by(DirectParent) %>% filter(n()>1)

parent_all_COMBO_sig3 <- parent_all_COMBO_sig2 %>% group_by(DirectParent, Enrichment.dir) %>% summarise_at(vars("VIP"), mean)

parent_all_COMBO_sig3 <- parent_all_COMBO_sig3 %>% group_by(DirectParent) %>% 
  arrange(VIP) %>% 
  mutate(order = row_number())
```

```{r}
plot_COMBO2 <- parent_all_COMBO_sig3 %>% ungroup() %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP, .fun = mean)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) + 
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_COMBO2
```




``` {r prepare VIP plot gen, echo=TRUE, warning=FALSE, message=FALSE}
# Attaching VIPs to t-test dataframes
parent_all_AZvsBY_VIP_sig2 <- merge(parent_all_AZvsBY_VIP_sig, parent_all_AZvsBY_VIP_1, by = "DirectParent")
parent_all_AZvsCX_VIP_sig2 <- merge(parent_all_AZvsCX_VIP_sig, parent_all_AZvsCX_VIP_1, by = "DirectParent")
parent_all_AZvsDW_VIP_sig2 <- merge(parent_all_AZvsDW_VIP_sig, parent_all_AZvsDW_VIP_1, by = "DirectParent")
parent_all_AZvsEV_VIP_sig2 <- merge(parent_all_AZvsEV_VIP_sig, parent_all_AZvsEV_VIP_1, by = "DirectParent")
parent_all_AZvsFU_VIP_sig2 <- merge(parent_all_AZvsFU_VIP_sig, parent_all_AZvsFU_VIP_1, by = "DirectParent")
parent_all_AZvsGT_VIP_sig2 <- merge(parent_all_AZvsGT_VIP_sig, parent_all_AZvsGT_VIP_1, by = "DirectParent")
parent_all_AZvsHS_VIP_sig2 <- merge(parent_all_AZvsHS_VIP_sig, parent_all_AZvsHS_VIP_1, by = "DirectParent")
parent_all_AZvsIR_VIP_sig2 <- merge(parent_all_AZvsIR_VIP_sig, parent_all_AZvsIR_VIP_1, by = "DirectParent")
parent_all_AZvsJQ_VIP_sig2 <- merge(parent_all_AZvsJQ_VIP_sig, parent_all_AZvsJQ_VIP_1, by = "DirectParent")

parent_all_BYvsCX_VIP_sig2 <- merge(parent_all_BYvsCX_VIP_sig, parent_all_BYvsCX_VIP_1, by = "DirectParent")
parent_all_BYvsDW_VIP_sig2 <- merge(parent_all_BYvsDW_VIP_sig, parent_all_BYvsDW_VIP_1, by = "DirectParent")
parent_all_BYvsEV_VIP_sig2 <- merge(parent_all_BYvsEV_VIP_sig, parent_all_BYvsEV_VIP_1, by = "DirectParent")
parent_all_BYvsFU_VIP_sig2 <- merge(parent_all_BYvsFU_VIP_sig, parent_all_BYvsFU_VIP_1, by = "DirectParent")
parent_all_BYvsGT_VIP_sig2 <- merge(parent_all_BYvsGT_VIP_sig, parent_all_BYvsGT_VIP_1, by = "DirectParent")
parent_all_BYvsHS_VIP_sig2 <- merge(parent_all_BYvsHS_VIP_sig, parent_all_BYvsHS_VIP_1, by = "DirectParent")
parent_all_BYvsIR_VIP_sig2 <- merge(parent_all_BYvsIR_VIP_sig, parent_all_BYvsIR_VIP_1, by = "DirectParent")
parent_all_BYvsJQ_VIP_sig2 <- merge(parent_all_BYvsJQ_VIP_sig, parent_all_BYvsJQ_VIP_1, by = "DirectParent")

parent_all_CXvsDW_VIP_sig2 <- merge(parent_all_CXvsDW_VIP_sig, parent_all_CXvsDW_VIP_1, by = "DirectParent")
parent_all_CXvsEV_VIP_sig2 <- merge(parent_all_CXvsEV_VIP_sig, parent_all_CXvsEV_VIP_1, by = "DirectParent")
parent_all_CXvsFU_VIP_sig2 <- merge(parent_all_CXvsFU_VIP_sig, parent_all_CXvsFU_VIP_1, by = "DirectParent")
parent_all_CXvsGT_VIP_sig2 <- merge(parent_all_CXvsGT_VIP_sig, parent_all_CXvsGT_VIP_1, by = "DirectParent")
parent_all_CXvsHS_VIP_sig2 <- merge(parent_all_CXvsHS_VIP_sig, parent_all_CXvsHS_VIP_1, by = "DirectParent")
parent_all_CXvsIR_VIP_sig2 <- merge(parent_all_CXvsIR_VIP_sig, parent_all_CXvsIR_VIP_1, by = "DirectParent")
parent_all_CXvsJQ_VIP_sig2 <- merge(parent_all_CXvsJQ_VIP_sig, parent_all_CXvsJQ_VIP_1, by = "DirectParent")

parent_all_DWvsEV_VIP_sig2 <- merge(parent_all_DWvsEV_VIP_sig, parent_all_DWvsEV_VIP_1, by = "DirectParent")
parent_all_DWvsFU_VIP_sig2 <- merge(parent_all_DWvsFU_VIP_sig, parent_all_DWvsFU_VIP_1, by = "DirectParent")
parent_all_DWvsGT_VIP_sig2 <- merge(parent_all_DWvsGT_VIP_sig, parent_all_DWvsGT_VIP_1, by = "DirectParent")
parent_all_DWvsHS_VIP_sig2 <- merge(parent_all_DWvsHS_VIP_sig, parent_all_DWvsHS_VIP_1, by = "DirectParent")
parent_all_DWvsIR_VIP_sig2 <- merge(parent_all_DWvsIR_VIP_sig, parent_all_DWvsIR_VIP_1, by = "DirectParent")
parent_all_DWvsJQ_VIP_sig2 <- merge(parent_all_DWvsJQ_VIP_sig, parent_all_DWvsJQ_VIP_1, by = "DirectParent")

parent_all_EVvsFU_VIP_sig2 <- merge(parent_all_EVvsFU_VIP_sig, parent_all_EVvsFU_VIP_1, by = "DirectParent")
parent_all_EVvsGT_VIP_sig2 <- merge(parent_all_EVvsGT_VIP_sig, parent_all_EVvsGT_VIP_1, by = "DirectParent")
parent_all_EVvsHS_VIP_sig2 <- merge(parent_all_EVvsHS_VIP_sig, parent_all_EVvsHS_VIP_1, by = "DirectParent")
parent_all_EVvsIR_VIP_sig2 <- merge(parent_all_EVvsIR_VIP_sig, parent_all_EVvsIR_VIP_1, by = "DirectParent")
parent_all_EVvsJQ_VIP_sig2 <- merge(parent_all_EVvsJQ_VIP_sig, parent_all_EVvsJQ_VIP_1, by = "DirectParent")

parent_all_FUvsGT_VIP_sig2 <- merge(parent_all_FUvsGT_VIP_sig, parent_all_FUvsGT_VIP_1, by = "DirectParent")
parent_all_FUvsHS_VIP_sig2 <- merge(parent_all_FUvsHS_VIP_sig, parent_all_FUvsHS_VIP_1, by = "DirectParent")
parent_all_FUvsIR_VIP_sig2 <- merge(parent_all_FUvsIR_VIP_sig, parent_all_FUvsIR_VIP_1, by = "DirectParent")
parent_all_FUvsJQ_VIP_sig2 <- merge(parent_all_FUvsJQ_VIP_sig, parent_all_FUvsJQ_VIP_1, by = "DirectParent")

parent_all_GTvsHS_VIP_sig2 <- merge(parent_all_GTvsHS_VIP_sig, parent_all_GTvsHS_VIP_1, by = "DirectParent")
parent_all_GTvsIR_VIP_sig2 <- merge(parent_all_GTvsIR_VIP_sig, parent_all_GTvsIR_VIP_1, by = "DirectParent")
parent_all_GTvsJQ_VIP_sig2 <- merge(parent_all_GTvsJQ_VIP_sig, parent_all_GTvsJQ_VIP_1, by = "DirectParent")

parent_all_HSvsIR_VIP_sig2 <- merge(parent_all_HSvsIR_VIP_sig, parent_all_HSvsIR_VIP_1, by = "DirectParent")
parent_all_HSvsJQ_VIP_sig2 <- merge(parent_all_HSvsJQ_VIP_sig, parent_all_HSvsJQ_VIP_1, by = "DirectParent")

parent_all_IRvsJQ_VIP_sig2 <- merge(parent_all_IRvsJQ_VIP_sig, parent_all_IRvsJQ_VIP_1, by = "DirectParent")
```

```{r}
#plot one comparison
plot_BYvsCX <- parent_all_BYvsCX_VIP_sig2 %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) +
  #scale_colour_manual(values=c("#8B0046", "#468B00")) +
  #scale_fill_manual(values=c("#8B0046", "#468B00")) +
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_BYvsCX
```

```{r combine VIP plot files gen}
parent_allgen_COMBO_sig2 <- rbind(parent_all_AZvsBY_VIP_sig2,parent_all_AZvsCX_VIP_sig2,parent_all_AZvsDW_VIP_sig2,parent_all_AZvsEV_VIP_sig2,parent_all_AZvsFU_VIP_sig2,parent_all_AZvsGT_VIP_sig2,parent_all_AZvsHS_VIP_sig2,parent_all_AZvsIR_VIP_sig2,parent_all_AZvsJQ_VIP_sig2,parent_all_BYvsCX_VIP_sig2,parent_all_BYvsDW_VIP_sig2,parent_all_BYvsEV_VIP_sig2,parent_all_BYvsFU_VIP_sig2,parent_all_BYvsGT_VIP_sig2,parent_all_BYvsHS_VIP_sig2,parent_all_BYvsIR_VIP_sig2,parent_all_BYvsJQ_VIP_sig2,parent_all_CXvsDW_VIP_sig2,parent_all_CXvsEV_VIP_sig2,parent_all_CXvsFU_VIP_sig2,parent_all_CXvsGT_VIP_sig2,parent_all_CXvsHS_VIP_sig2,parent_all_CXvsIR_VIP_sig2,parent_all_CXvsJQ_VIP_sig2,parent_all_DWvsEV_VIP_sig2,parent_all_DWvsFU_VIP_sig2,parent_all_DWvsGT_VIP_sig2,parent_all_DWvsHS_VIP_sig2,parent_all_DWvsIR_VIP_sig2,parent_all_DWvsJQ_VIP_sig2,parent_all_EVvsFU_VIP_sig2,parent_all_EVvsGT_VIP_sig2,parent_all_EVvsHS_VIP_sig2,parent_all_EVvsIR_VIP_sig2,parent_all_EVvsJQ_VIP_sig2,parent_all_FUvsGT_VIP_sig2,parent_all_FUvsHS_VIP_sig2,parent_all_FUvsIR_VIP_sig2,parent_all_FUvsJQ_VIP_sig2,parent_all_GTvsHS_VIP_sig2,parent_all_GTvsIR_VIP_sig2,parent_all_GTvsJQ_VIP_sig2,parent_all_HSvsIR_VIP_sig2,parent_all_HSvsJQ_VIP_sig2,parent_all_IRvsJQ_VIP_sig2)
```

```{r}
plot_COMBO_gen <- parent_allgen_COMBO_sig2 %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) + 
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_COMBO_gen
```

```{r}
#filter only repeated metabolites 
#parent_all_COMBO_sig3 <- parent_all_COMBO_sig2 %>% group_by(DirectParent) %>% filter(n()>1)

parent_allgen_COMBO_sig3 <- parent_allgen_COMBO_sig2 %>% group_by(DirectParent, Enrichment.dir) %>% summarise_at(vars("VIP"), mean)

parent_allgen_COMBO_sig3 <- parent_allgen_COMBO_sig3 %>% group_by(DirectParent) %>% 
  arrange(VIP) %>% 
  mutate(order = row_number())
```

```{r}
plot_COMBO_gen2 <- parent_allgen_COMBO_sig3 %>% ungroup() %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP, .fun = mean)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) + 
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_COMBO_gen2
```


#PLS-DA with WGCNA results

#grey module
```{r prepare dataset: agg_all_grey}
#create vector of list of compounds in grey module 
grey <- modgrey$id

#subset columns from agg_all (created in data_help.Rmd) using grey vector
agg_all_grey <- agg_all[, grey]

#re-attach metadata columns from agg_all
agg_all_grey <- cbind(agg_all[ ,3:6],agg_all_grey)

#make sure acclimation treatment and genotype columns are being read as factor
agg_all_grey$ATTRIBUTE_acclimation <- as.factor(agg_all_grey$ATTRIBUTE_acclimation)
agg_all_grey$ATTRIBUTE_genotype <- as.factor(agg_all_grey$ATTRIBUTE_genotype)
```

```{r modgrey PLSDA: acclimation}
#select treatment names
Y <- agg_all_grey$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_grey[5:16]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Grey Module PLS-DA: Acclimation")
```

```{r modgrey PLSDA: genotype}
#select treatment names
Y <- agg_all_grey$ATTRIBUTE_genotype

#select only data columns
X <- agg_all_grey[5:16]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Grey Module PLS-DA: Genotype")
```

#blue module
```{r prepare dataset: agg_all_blue}
#create vector of list of compounds in grey module 
blue <- modblue$id

#subset columns from agg_all (created in data_help.Rmd) using grey vector
agg_all_blue <- agg_all[, blue]

#re-attach metadata columns from agg_all
agg_all_blue <- cbind(agg_all[ ,3:6],agg_all_blue)

#make sure acclimation treatment and genotype columns are being read as factor
agg_all_blue$ATTRIBUTE_acclimation <- as.factor(agg_all_blue$ATTRIBUTE_acclimation)
agg_all_blue$ATTRIBUTE_genotype <- as.factor(agg_all_blue$ATTRIBUTE_genotype)
```

```{r modblue PLSDA: acclimation}
#select treatment names
Y <- agg_all_blue$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_blue[5:49]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Blue Module PLS-DA: Acclimation")
```

```{r modblue PLSDA: genotype}
#select treatment names
Y <- agg_all_blue$ATTRIBUTE_genotype

#select only data columns
X <- agg_all_blue[5:49]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Blue Module PLS-DA: Genotype")
```

#red module
```{r prepare dataset: agg_all_red}
#create vector of list of compounds in grey module 
red <- modred$id

#subset columns from agg_all (created in data_help.Rmd) using grey vector
agg_all_red <- agg_all[, red]

#re-attach metadata columns from agg_all
agg_all_red <- cbind(agg_all[ ,3:6],agg_all_red)

#make sure acclimation treatment and genotype columns are being read as factor
agg_all_red$ATTRIBUTE_acclimation <- as.factor(agg_all_red$ATTRIBUTE_acclimation)
agg_all_red$ATTRIBUTE_genotype <- as.factor(agg_all_red$ATTRIBUTE_genotype)
#View(agg_all_red)
```

```{r modred PLSDA: acclimation}
#select treatment names
Y <- agg_all_red$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_red[5:13]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Red Module PLS-DA: Acclimation")
```

```{r modred PLSDA: genotype}
#select treatment names
Y <- agg_all_red$ATTRIBUTE_genotype

#select only data columns
X <- agg_all_red[5:13]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Red Module PLS-DA: Genotype")
```

#turquoise module
```{r prepare dataset: agg_all_turq}
#create vector of list of compounds in grey module 
turq <- modturquoise$id

#subset columns from agg_all (created in data_help.Rmd) using grey vector
agg_all_turq <- agg_all[, turq]

#re-attach metadata columns from agg_all
#agg_all_grey <- rbind(agg_all(,c[3:6]))
agg_all_turq <- cbind(agg_all[ ,3:6],agg_all_turq)

#make sure acclimation treatment and genotype columns are being read as factor
agg_all_turq$ATTRIBUTE_acclimation <- as.factor(agg_all_turq$ATTRIBUTE_acclimation)
agg_all_turq$ATTRIBUTE_genotype <- as.factor(agg_all_turq$ATTRIBUTE_genotype)
#View(agg_all_turq)
```

```{r modturquoise PLSDA: acclimation}
#select treatment names
Y <- agg_all_turq$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_turq[5:225]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Turquoise Module PLS-DA: Acclimation")
```

```{r modturquoise PLSDA: genotype}
#select treatment names
Y <- agg_all_turq$ATTRIBUTE_genotype

#select only data columns
X <- agg_all_turq[5:225]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Turquoise Module PLS-DA: Genotype")
```


#PLS-DA within acclimation treatments and genotypes

#Acclimation 1
```{r prepare dataset: agg_all_1}
#subset only rows in the Acclimation 1 from agg_all
agg_all_acc1 <- agg_all[agg_all$ATTRIBUTE_acclimation == '1',]
View(agg_all_acc1)
```

```{r acc1 PLSDA: genotype}
#select treatment names
Yacc1 <- agg_all_acc1$ATTRIBUTE_genotype

#select only data columns
Xacc1 <- agg_all_acc1[7:350]

#PLSDA without variable selection
acc1.plsda <- mixOmics::plsda(Xacc1,Yacc1) # 1 Run the method
plotIndiv(acc1.plsda)    # 2 Plot the samples
plotVar(acc1.plsda, cutoff = 0.5)

plsda_acc1 <- plotIndiv(acc1.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Acclimation 1 PLS-DA: Genotype")

plsda_acc1
```

#Acclimation 2
```{r prepare dataset: agg_all_2}
#subset only rows in the Acclimation 2 from agg_all
agg_all_acc2 <- agg_all[agg_all$ATTRIBUTE_acclimation == '2',]
```

```{r acc2 PLSDA: genotype}
#select treatment names
Yacc2 <- agg_all_acc2$ATTRIBUTE_genotype

#select only data columns
Xacc2 <- agg_all_acc2[7:350]

#PLSDA without variable selection
acc2.plsda <- mixOmics::plsda(Xacc2,Yacc2) # 1 Run the method
plotIndiv(acc2.plsda)    # 2 Plot the samples
plotVar(acc2.plsda, cutoff = 0.5)

plsda_acc2 <- plotIndiv(acc2.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Acclimation 2 PLS-DA: Genotype")

plsda_acc2
```

#Acclimation 3
```{r prepare dataset: agg_all_3}
#subset only rows in the Acclimation 3 from agg_all
agg_all_acc3 <- agg_all[agg_all$ATTRIBUTE_acclimation == '3',]
```

```{r acc3 PLSDA: genotype}
#select treatment names
Yacc3 <- agg_all_acc3$ATTRIBUTE_genotype

#select only data columns
Xacc3 <- agg_all_acc3[7:350]

#PLSDA without variable selection
acc3.plsda <- mixOmics::plsda(Xacc3,Yacc3) # 1 Run the method
plotIndiv(acc3.plsda)    # 2 Plot the samples
plotVar(acc3.plsda, cutoff = 0.5)

plsda_acc3 <- plotIndiv(acc3.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Acclimation 3 PLS-DA: Genotype")

plsda_acc3
```

#Acclimation 4
```{r prepare dataset: agg_all_4}
#subset only rows in the Acclimation 4 from agg_all
agg_all_acc4 <- agg_all[agg_all$ATTRIBUTE_acclimation == '4',]
```

```{r acc4 PLSDA: genotype}
#select treatment names
Yacc4 <- agg_all_acc4$ATTRIBUTE_genotype

#select only data columns
Xacc4 <- agg_all_acc4[7:350]

#PLSDA without variable selection
acc4.plsda <- mixOmics::plsda(Xacc4,Yacc4) # 1 Run the method
plotIndiv(acc4.plsda)    # 2 Plot the samples
plotVar(acc4.plsda, cutoff = 0.5)

plsda_acc4 <- plotIndiv(acc4.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Acclimation 4 PLS-DA: Genotype")

plsda_acc4
```

#Acclimation 5
```{r prepare dataset: agg_all_5}
#subset only rows in the Acclimation 5 from agg_all
agg_all_acc5 <- agg_all[agg_all$ATTRIBUTE_acclimation == '5',]
```

```{r acc5 PLSDA: genotype}
#select treatment names
Yacc5 <- agg_all_acc5$ATTRIBUTE_genotype

#select only data columns
Xacc5 <- agg_all_acc5[7:350]

#PLSDA without variable selection
acc5.plsda <- mixOmics::plsda(Xacc5,Yacc5) # 1 Run the method
plotIndiv(acc5.plsda)    # 2 Plot the samples
plotVar(acc5.plsda, cutoff = 0.5)

plsda_acc5 <- plotIndiv(acc5.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Acclimation 5 PLS-DA: Genotype")

plsda_acc5
```

#Arrange PLSDA: Acclimation figures
```{r arrange PLSDA acclimation figs}
plsda_accall <- grid.arrange(plsda_acc1, plsda_acc2, plsda_acc3, plsda_acc4, plsda_acc5)
plsda_accall 
#Error in gList(list(df = list(x = c(0.190511332669252, -4.32063542143726, : only 'grobs' allowed in "gList"
```

#Genotype AZ
```{r prepare dataset: agg_all_AZ}
#subset only rows in the Genotype AZ from agg_all
agg_all_AZ <- agg_all[agg_all$ATTRIBUTE_genotype == 'AZ',]
```

```{r AZ PLSDA: acclimation}
#select treatment names
Y <- agg_all_AZ$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_AZ[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Genotype AZ PLS-DA: Acclimation")
```

#Genotype BY
```{r prepare dataset: agg_all_BY}
#subset only rows in the Genotype BY from agg_all
agg_all_BY <- agg_all[agg_all$ATTRIBUTE_genotype == 'BY',]
```

```{r BY PLSDA: acclimation}
#select treatment names
Y <- agg_all_BY$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_BY[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Genotype BY PLS-DA: Acclimation")
```

#Genotype CX
```{r prepare dataset: agg_all_CX}
#subset only rows in the Genotype CX from agg_all
agg_all_CX <- agg_all[agg_all$ATTRIBUTE_genotype == 'CX',]
```

```{r CX PLSDA: acclimation}
#select treatment names
Y <- agg_all_CX$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_CX[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Genotype CX PLS-DA: Acclimation")
```

#Genotype DW
```{r prepare dataset: agg_all_DW}
#subset only rows in the Genotype DW from agg_all
agg_all_DW <- agg_all[agg_all$ATTRIBUTE_genotype == 'DW',]
```

```{r DW PLSDA: acclimation}
#select treatment names
Y <- agg_all_DW$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_DW[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Genotype DW PLS-DA: Acclimation")
```

#Genotype EV
```{r prepare dataset: agg_all_EV}
#subset only rows in the Genotype EV from agg_all
agg_all_EV <- agg_all[agg_all$ATTRIBUTE_genotype == 'EV',]
```

```{r EV PLSDA: acclimation}
#select treatment names
Y <- agg_all_EV$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_EV[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Genotype EV PLS-DA: Acclimation")
```

#Genotype FU
```{r prepare dataset: agg_all_FU}
#subset only rows in the Genotype FU from agg_all
agg_all_FU <- agg_all[agg_all$ATTRIBUTE_genotype == 'FU',]
```

```{r FU PLSDA: acclimation}
#select treatment names
Y <- agg_all_FU$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_FU[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Genotype FU PLS-DA: Acclimation")
```

#Genotype GT
```{r prepare dataset: agg_all_GT}
#subset only rows in the Genotype GT from agg_all
agg_all_GT <- agg_all[agg_all$ATTRIBUTE_genotype == 'GT',]
```

```{r GT PLSDA: acclimation}
#select treatment names
Y <- agg_all_GT$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_GT[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Genotype GT PLS-DA: Acclimation")
```

#Genotype HS
```{r prepare dataset: agg_all_HS}
#subset only rows in the Genotype HS from agg_all
agg_all_HS <- agg_all[agg_all$ATTRIBUTE_genotype == 'HS',]
```

```{r HS PLSDA: acclimation}
#select treatment names
Y <- agg_all_HS$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_HS[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Genotype HS PLS-DA: Acclimation")
```

#Genotype IR
```{r prepare dataset: agg_all_IR}
#subset only rows in the Genotype IR from agg_all
agg_all_IR <- agg_all[agg_all$ATTRIBUTE_genotype == 'IR',]
```

```{r IR PLSDA: acclimation}
#select treatment names
Y <- agg_all_IR$ATTRIBUTE_acclimation

#select only data columns
X <- agg_all_IR[7:350]

#PLSDA without variable selection
MyResult.plsda <- mixOmics::plsda(X,Y) # 1 Run the method
plotIndiv(MyResult.plsda)    # 2 Plot the samples
plotVar(MyResult.plsda, cutoff = 0.5)

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Genotype IR PLS-DA: Acclimation")
```

#Genotype JQ
```{r prepare dataset: agg_all_JQ}
#subset only rows in the Genotype JQ from agg_all
agg_all_JQ <- agg_all[agg_all$ATTRIBUTE_genotype == 'JQ',]
```

```{r JQ PLSDA: acclimation}
#select treatment names
Yjq <- agg_all_JQ$ATTRIBUTE_acclimation

#select only data columns
Xjq <- agg_all_JQ[7:350]

#PLSDA without variable selection
JQ.plsda <- mixOmics::plsda(Xjq,Yjq) # 1 Run the method
plotIndiv(JQ.plsda)    # 2 Plot the samples
plotVar(JQ.plsda, cutoff = 0.5)

plsda_jq <- plotIndiv(JQ.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Genotype JQ PLS-DA: Acclimation")

plsda_jq
```


#PLSDA with key compounds
```{r prepare dataset: agg_all_keycomps}
#select only columns of key compounds from agg_all using keycompounds.txt
agg_all_keycomps <- agg_all %>% dplyr::select(c('baca416990c75e3ce98b889c7cb02f18', '50c4567910430a7cbcc0799315924ec9', '100e039fcf15e05226be0a807cbcc627','947a5d4c7ad27a42b75192942695c109','c619eb858d1b5afd0ac936c3015e5f80'))

#recombine with attribute columns
agg_all_keycomps <- cbind(agg_all[ ,3:6],agg_all_keycomps)
```

```{r keycomps: acclimation}
#select treatment names
Ykeycomps <- agg_all_keycomps$ATTRIBUTE_acclimation

#select only data columns
Xkeycomps <- agg_all_keycomps[5:9]

#PLSDA without variable selection
keycomps.plsda <- mixOmics::plsda(Xkeycomps,Ykeycomps) # 1 Run the method
plotIndiv(keycomps.plsda)    # 2 Plot the samples
plotVar(keycomps.plsda, cutoff = 0.5)

plsda_keycomps <- plotIndiv(keycomps.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Key Compounds PLS-DA: Acclimation")

plsda_keycomps
```

```{r keycomps: genotype}
#select treatment names
Ykeycomps_g <- agg_all_keycomps$ATTRIBUTE_genotype

#select only data columns
Xkeycomps <- agg_all_keycomps[5:9]

#PLSDA without variable selection
keycomps_g.plsda <- mixOmics::plsda(Xkeycomps,Ykeycomps_g) # 1 Run the method
plotIndiv(keycomps_g.plsda)    # 2 Plot the samples
plotVar(keycomps_g.plsda, cutoff = 0.5)

plsda_keycomps_g <- plotIndiv(keycomps_g.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Key Compounds PLS-DA: Genotype")

plsda_keycomps_g
```

#PLSDA with alpha amino acids
```{r prepare dataset: agg_all_aaa}
#select only columns of key compounds from agg_all using keycompounds.txt
agg_all_aaa <- agg_all %>% dplyr::select(c('baca416990c75e3ce98b889c7cb02f18', '47c0cbbc8f2c445fd8af445c4785f491'))

#recombine with attribute columns
agg_all_aaa <- cbind(agg_all[ ,3:6],agg_all_aaa)
#View(agg_all_aaa)
```

```{r keycomps: acclimation}
#select treatment names
Yaaa <- agg_all_aaa$ATTRIBUTE_acclimation

#select only data columns
Xaaa <- agg_all_aaa[5:6]
#doesn't work because there need to be at least three compounds

#PLSDA without variable selection
aaa.plsda <- mixOmics::plsda(Xaaa,Yaaa) # 1 Run the method
plotIndiv(aaa.plsda)    # 2 Plot the samples
plotVar(aaa.plsda, cutoff = 0.5)

plsda_aaa <- plotIndiv(aaa.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Alpha Amino Acids PLS-DA: Acclimation")

plsda_aaa
```

#PLSDA with Amino acids, peptides, and analogues
```{r prepare dataset: agg_amino}
#select only columns of compounds Amiono acids subclass from agg_all using amino$id
agg_amino <- agg_all %>% dplyr::select(amino$id)

#recombine with attribute columns
agg_amino <- cbind(agg_all[ ,3:6],agg_amino)
#View(agg_amino)
```

```{r amino: acclimation}
#select treatment names
Yamino <- agg_amino$ATTRIBUTE_acclimation

#select only data columns
Xamino <- agg_amino[5:39]

#PLSDA without variable selection
amino.plsda <- mixOmics::plsda(Xamino,Yamino) # 1 Run the method
plotIndiv(amino.plsda)    # 2 Plot the samples
plotVar(amino.plsda, cutoff = 0.5)

plsda_amino <- plotIndiv(amino.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Amino Acids Subclass PLS-DA: Acclimation")

plsda_amino
```

```{r amino: genotype}
#select treatment names
Yamino_g <- agg_amino$ATTRIBUTE_genotype

#select only data columns
Xamino <- agg_amino[5:39]

#PLSDA without variable selection
amino_g.plsda <- mixOmics::plsda(Xamino,Yamino_g) # 1 Run the method
plotIndiv(amino_g.plsda)    # 2 Plot the samples
plotVar(amino_g.plsda, cutoff = 0.5)

plsda_amino_g <- plotIndiv(amino_g.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE,title="Amino Acids Subclass PLS-DA: Genotype")

plsda_amino_g
```



.