---
title: "vip"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
#load required libraries
library(tidyr)
library("reshape")
library(plyr)
library(dplyr)
library(ggplot2)
library("arsenal")
library("Rmisc")
library(gridExtra)
library(ggpubr)
library(factoextra)
library(ggplot2)
library(RColorBrewer)
library(lme4)
library(lmerTest)
library(car)
library(effects)
library(ggfortify)
library(cowplot)
library(vegan)
library(corrr)
library(ggcorrplot)
library(GGally)
library(broom)
library(cowplot)
library(RVAideMemoire)
library(arsenal)
library(patchwork)
library(tidyr)
library(ggrepel)
library(randomForest)
library("janitor")
library(caret)
library(varImp)
```

```{r}
#packages from paper 
library(readxl)
library(cowplot)
library(RColorBrewer)
library(janitor)
library(viridis)
library(vegan)
library(car)
library(magicfor)
library(grid)
library(factoextra)
#install.packages("egg")
library(egg)
```

#Methods from Dr. Kevin Wong: https://github.com/kevinhwong1/Porites_Rim_Bleaching_2019/blob/623b8aa21bc53d030c6bda2c79c8e0b5e5445f32/scripts/Metabolomics/Metabolomics_VIP_Known.Rmd#L4

```{r variables as factors}
#make sure that all proper columns are being read as factors 
agg_parent_norm_all$ATTRIBUTE_acclimation <- as.factor(agg_parent_norm_all$ATTRIBUTE_acclimation)

agg_parent_norm_all$ATTRIBUTE_genotype <- as.factor(agg_parent_norm_all$ATTRIBUTE_genotype)

agg_parent_norm_known$ATTRIBUTE_acclimation <- as.factor(agg_parent_norm_known$ATTRIBUTE_acclimation)

agg_parent_norm_known$ATTRIBUTE_genotype <- as.factor(agg_parent_norm_known$ATTRIBUTE_genotype)
```

#subset datasets for analysis
#every possible combination of 2 acclimation treatments
```{r all pairwise acc}
#aggregated by all direct parents: single groups
parent_all_acc1 <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_acclimation == "1") %>%
  na.omit()

parent_all_acc2 <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_acclimation == "2") %>%
  na.omit()

parent_all_acc3 <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_acclimation == "3") %>%
  na.omit()

parent_all_acc4 <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_acclimation == "4") %>%
  na.omit()

parent_all_acc5 <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_acclimation == "5") %>%
  na.omit()

parent_all_acc1 <- droplevels(parent_all_acc1)
parent_all_acc2 <- droplevels(parent_all_acc2)
parent_all_acc3 <- droplevels(parent_all_acc3)
parent_all_acc4 <- droplevels(parent_all_acc4)
parent_all_acc5 <- droplevels(parent_all_acc5)

#bind together in every possible combo 
parent_all_acc1vs2 <- rbind(parent_all_acc1, parent_all_acc2)

parent_all_acc1vs3 <- rbind(parent_all_acc1, parent_all_acc3)

parent_all_acc1vs4 <- rbind(parent_all_acc1, parent_all_acc4)

parent_all_acc1vs5 <- rbind(parent_all_acc1, parent_all_acc5)

parent_all_acc2vs3 <- rbind(parent_all_acc2, parent_all_acc3)

parent_all_acc2vs4 <- rbind(parent_all_acc2, parent_all_acc4)

parent_all_acc2vs5 <- rbind(parent_all_acc2, parent_all_acc5)

parent_all_acc3vs4 <- rbind(parent_all_acc3, parent_all_acc4)

parent_all_acc3vs5 <- rbind(parent_all_acc3, parent_all_acc5)

parent_all_acc4vs5 <- rbind(parent_all_acc4, parent_all_acc5)
```

```{r known pairwise acc}
#aggregated by known direct parents: single groups
parent_known_acc1 <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_acclimation == "1") %>%
  na.omit()

parent_known_acc2 <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_acclimation == "2") %>%
  na.omit()

parent_known_acc3 <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_acclimation == "3") %>%
  na.omit()

parent_known_acc4 <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_acclimation == "4") %>%
  na.omit()

parent_known_acc5 <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_acclimation == "5") %>%
  na.omit()

parent_known_acc1 <- droplevels(parent_known_acc1)
parent_known_acc2 <- droplevels(parent_known_acc2)
parent_known_acc3 <- droplevels(parent_known_acc3)
parent_known_acc4 <- droplevels(parent_known_acc4)
parent_known_acc5 <- droplevels(parent_known_acc5)

#bind together in every possible combo 
parent_known_acc1vs2 <- rbind(parent_known_acc1, parent_known_acc2)

parent_known_acc1vs3 <- rbind(parent_known_acc1, parent_known_acc3)

parent_known_acc1vs4 <- rbind(parent_known_acc1, parent_known_acc4)

parent_known_acc1vs5 <- rbind(parent_known_acc1, parent_known_acc5)

parent_known_acc2vs3 <- rbind(parent_known_acc2, parent_known_acc3)

parent_known_acc2vs4 <- rbind(parent_known_acc2, parent_known_acc4)

parent_known_acc2vs5 <- rbind(parent_known_acc2, parent_known_acc5)

parent_known_acc3vs4 <- rbind(parent_known_acc3, parent_known_acc4)

parent_known_acc3vs5 <- rbind(parent_known_acc3, parent_known_acc5)

parent_known_acc4vs5 <- rbind(parent_known_acc4, parent_known_acc5)
```

#every possible combination of 2 genotypes
```{r all pairwise gen}
#aggregated by all direct parents: single groups
parent_all_AZ <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "AZ") %>%
  na.omit()
parent_all_BY <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "BY") %>%
  na.omit()
parent_all_CX <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "CX") %>%
  na.omit()
parent_all_DW <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "DW") %>%
  na.omit()
parent_all_EV <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "EV") %>%
  na.omit()
parent_all_FU <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "FU") %>%
  na.omit()
parent_all_GT <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "GT") %>%
  na.omit()
parent_all_HS <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "HS") %>%
  na.omit()
parent_all_IR <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "IR") %>%
  na.omit()
parent_all_JQ <- agg_parent_norm_all %>%
  filter(ATTRIBUTE_genotype == "JQ") %>%
  na.omit()

parent_all_AZvsBY <- rbind(parent_all_AZ, parent_all_BY)
parent_all_AZvsCX <- rbind(parent_all_AZ, parent_all_CX)
parent_all_AZvsDW <- rbind(parent_all_AZ, parent_all_DW)
parent_all_AZvsEV <- rbind(parent_all_AZ, parent_all_EV)
parent_all_AZvsFU <- rbind(parent_all_AZ, parent_all_FU)
parent_all_AZvsGT <- rbind(parent_all_AZ, parent_all_GT)
parent_all_AZvsHS <- rbind(parent_all_AZ, parent_all_HS)
parent_all_AZvsIR <- rbind(parent_all_AZ, parent_all_IR)
parent_all_AZvsJQ <- rbind(parent_all_AZ, parent_all_JQ)

parent_all_BYvsCX <- rbind(parent_all_BY, parent_all_CX)
parent_all_BYvsDW <- rbind(parent_all_BY, parent_all_DW)
parent_all_BYvsEV <- rbind(parent_all_BY, parent_all_EV)
parent_all_BYvsFU <- rbind(parent_all_BY, parent_all_FU)
parent_all_BYvsGT <- rbind(parent_all_BY, parent_all_GT)
parent_all_BYvsHS <- rbind(parent_all_BY, parent_all_HS)
parent_all_BYvsIR <- rbind(parent_all_BY, parent_all_IR)
parent_all_BYvsJQ <- rbind(parent_all_BY, parent_all_JQ)

parent_all_CXvsDW <- rbind(parent_all_CX, parent_all_DW)
parent_all_CXvsEV <- rbind(parent_all_CX, parent_all_EV)
parent_all_CXvsFU <- rbind(parent_all_CX, parent_all_FU)
parent_all_CXvsGT <- rbind(parent_all_CX, parent_all_GT)
parent_all_CXvsHS <- rbind(parent_all_CX, parent_all_HS)
parent_all_CXvsIR <- rbind(parent_all_CX, parent_all_IR)
parent_all_CXvsJQ <- rbind(parent_all_CX, parent_all_JQ)

parent_all_DWvsEV <- rbind(parent_all_DW, parent_all_EV)
parent_all_DWvsFU <- rbind(parent_all_DW, parent_all_FU)
parent_all_DWvsGT <- rbind(parent_all_DW, parent_all_GT)
parent_all_DWvsHS <- rbind(parent_all_DW, parent_all_HS)
parent_all_DWvsIR <- rbind(parent_all_DW, parent_all_IR)
parent_all_DWvsJQ <- rbind(parent_all_DW, parent_all_JQ)

parent_all_EVvsFU <- rbind(parent_all_EV, parent_all_FU)
parent_all_EVvsGT <- rbind(parent_all_EV, parent_all_GT)
parent_all_EVvsHS <- rbind(parent_all_EV, parent_all_HS)
parent_all_EVvsIR <- rbind(parent_all_EV, parent_all_IR)
parent_all_EVvsJQ <- rbind(parent_all_EV, parent_all_JQ)

parent_all_FUvsGT <- rbind(parent_all_FU, parent_all_GT)
parent_all_FUvsHS <- rbind(parent_all_FU, parent_all_HS)
parent_all_FUvsIR <- rbind(parent_all_FU, parent_all_IR)
parent_all_FUvsJQ <- rbind(parent_all_FU, parent_all_JQ)

parent_all_GTvsHS <- rbind(parent_all_GT, parent_all_HS)
parent_all_GTvsIR <- rbind(parent_all_GT, parent_all_IR)
parent_all_GTvsJQ <- rbind(parent_all_GT, parent_all_JQ)

parent_all_HSvsIR <- rbind(parent_all_HS, parent_all_IR)
parent_all_HSvsJQ <- rbind(parent_all_HS, parent_all_JQ)

parent_all_IRvsJQ <- rbind(parent_all_IR, parent_all_JQ)
```

```{r known pairwise gen}
#aggregated by known direct parents: single groups
parent_known_AZ <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "AZ") %>%
  na.omit()
parent_known_BY <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "BY") %>%
  na.omit()
parent_known_CX <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "CX") %>%
  na.omit()
parent_known_DW <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "DW") %>%
  na.omit()
parent_known_EV <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "EV") %>%
  na.omit()
parent_known_FU <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "FU") %>%
  na.omit()
parent_known_GT <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "GT") %>%
  na.omit()
parent_known_HS <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "HS") %>%
  na.omit()
parent_known_IR <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "IR") %>%
  na.omit()
parent_known_JQ <- agg_parent_norm_known %>%
  filter(ATTRIBUTE_genotype == "JQ") %>%
  na.omit()

parent_known_AZvsBY <- rbind(parent_known_AZ, parent_known_BY)
parent_known_AZvsCX <- rbind(parent_known_AZ, parent_known_CX)
parent_known_AZvsDW <- rbind(parent_known_AZ, parent_known_DW)
parent_known_AZvsEV <- rbind(parent_known_AZ, parent_known_EV)
parent_known_AZvsFU <- rbind(parent_known_AZ, parent_known_FU)
parent_known_AZvsGT <- rbind(parent_known_AZ, parent_known_GT)
parent_known_AZvsHS <- rbind(parent_known_AZ, parent_known_HS)
parent_known_AZvsIR <- rbind(parent_known_AZ, parent_known_IR)
parent_known_AZvsJQ <- rbind(parent_known_AZ, parent_known_JQ)

parent_known_BYvsCX <- rbind(parent_known_BY, parent_known_CX)
parent_known_BYvsDW <- rbind(parent_known_BY, parent_known_DW)
parent_known_BYvsEV <- rbind(parent_known_BY, parent_known_EV)
parent_known_BYvsFU <- rbind(parent_known_BY, parent_known_FU)
parent_known_BYvsGT <- rbind(parent_known_BY, parent_known_GT)
parent_known_BYvsHS <- rbind(parent_known_BY, parent_known_HS)
parent_known_BYvsIR <- rbind(parent_known_BY, parent_known_IR)
parent_known_BYvsJQ <- rbind(parent_known_BY, parent_known_JQ)

parent_known_CXvsDW <- rbind(parent_known_CX, parent_known_DW)
parent_known_CXvsEV <- rbind(parent_known_CX, parent_known_EV)
parent_known_CXvsFU <- rbind(parent_known_CX, parent_known_FU)
parent_known_CXvsGT <- rbind(parent_known_CX, parent_known_GT)
parent_known_CXvsHS <- rbind(parent_known_CX, parent_known_HS)
parent_known_CXvsIR <- rbind(parent_known_CX, parent_known_IR)
parent_known_CXvsJQ <- rbind(parent_known_CX, parent_known_JQ)

parent_known_DWvsEV <- rbind(parent_known_DW, parent_known_EV)
parent_known_DWvsFU <- rbind(parent_known_DW, parent_known_FU)
parent_known_DWvsGT <- rbind(parent_known_DW, parent_known_GT)
parent_known_DWvsHS <- rbind(parent_known_DW, parent_known_HS)
parent_known_DWvsIR <- rbind(parent_known_DW, parent_known_IR)
parent_known_DWvsJQ <- rbind(parent_known_DW, parent_known_JQ)

parent_known_EVvsFU <- rbind(parent_known_EV, parent_known_FU)
parent_known_EVvsGT <- rbind(parent_known_EV, parent_known_GT)
parent_known_EVvsHS <- rbind(parent_known_EV, parent_known_HS)
parent_known_EVvsIR <- rbind(parent_known_EV, parent_known_IR)
parent_known_EVvsJQ <- rbind(parent_known_EV, parent_known_JQ)

parent_known_FUvsGT <- rbind(parent_known_FU, parent_known_GT)
parent_known_FUvsHS <- rbind(parent_known_FU, parent_known_HS)
parent_known_FUvsIR <- rbind(parent_known_FU, parent_known_IR)
parent_known_FUvsJQ <- rbind(parent_known_FU, parent_known_JQ)

parent_known_GTvsHS <- rbind(parent_known_GT, parent_known_HS)
parent_known_GTvsIR <- rbind(parent_known_GT, parent_known_IR)
parent_known_GTvsJQ <- rbind(parent_known_GT, parent_known_JQ)

parent_known_HSvsIR <- rbind(parent_known_HS, parent_known_IR)
parent_known_HSvsJQ <- rbind(parent_known_HS, parent_known_JQ)

parent_known_IRvsJQ <- rbind(parent_known_IR, parent_known_JQ)
```


#Creating the PLS-DA function

``` {r plsdaFunction, echo=TRUE, warning=FALSE, message=FALSE}
vip.plsda <- function(data,         # input datas et with only the two variables being compared 
                      Y,            # column of the predictor variable
                      path,         # path to output folder for graphs
                      name          # name of the PLS-DA graphs
                      ) { 
col <- ncol(data)                   # Finding number of columns in data set                                 
X <- data[5:col]                    # assigning metabolites as X data set
Y <- as.factor(Y)                   # assigning groups as Y data set (predictor)
MyResult.plsda <- mixOmics::plsda(X, Y)       # Running PLS-DA

plotIndiv(MyResult.plsda, ind.names = FALSE, legend=TRUE,ellipse = TRUE) # Plotting PLS-DA
pdf(file=paste0(path, name, "_plsda.pdf")) 
dev.off()

vip <- PLSDA.VIP(MyResult.plsda)                            # VIP Extraction from the PLS=DA
vip.df <- as.data.frame(vip[["tab"]])                       # Creating a readable data frame
vip.table <- tibble::rownames_to_column(vip.df, var = "DirectParent") # Creating a table format
vip.table_1 <- vip.table %>%                                # Filtering metabolites with VIPs >= 1
  filter(VIP >= 1)
return(vip.table_1)
}
```


### PLD-DA and VIP Extraction

``` {r PLSDA all acc, echo=TRUE, warning=FALSE, message=FALSE}
path <- "output/PLSDA_figs/"

#all direct parents by acclimation
parent_all_acc1vs2_VIP_1 <- vip.plsda(parent_all_acc1vs2, parent_all_acc1vs2$ATTRIBUTE_acclimation, path, "parent_all_acc1vs2")

parent_all_acc1vs3_VIP_1 <- vip.plsda(parent_all_acc1vs3, parent_all_acc1vs3$ATTRIBUTE_acclimation, path, "parent_all_acc1vs3")

parent_all_acc1vs4_VIP_1 <- vip.plsda(parent_all_acc1vs4, parent_all_acc1vs4$ATTRIBUTE_acclimation, path, "parent_all_acc1vs4")

parent_all_acc1vs5_VIP_1 <- vip.plsda(parent_all_acc1vs5, parent_all_acc1vs5$ATTRIBUTE_acclimation, path, "parent_all_acc1vs5")

parent_all_acc2vs3_VIP_1 <- vip.plsda(parent_all_acc2vs3, parent_all_acc2vs3$ATTRIBUTE_acclimation, path, "parent_all_acc2vs3")

parent_all_acc2vs4_VIP_1 <- vip.plsda(parent_all_acc2vs4, parent_all_acc2vs4$ATTRIBUTE_acclimation, path, "parent_all_acc2vs4")

parent_all_acc2vs5_VIP_1 <- vip.plsda(parent_all_acc2vs5, parent_all_acc2vs5$ATTRIBUTE_acclimation, path, "parent_all_acc2vs5")

parent_all_acc3vs4_VIP_1 <- vip.plsda(parent_all_acc3vs4, parent_all_acc3vs4$ATTRIBUTE_acclimation, path, "parent_all_acc3vs4")

parent_all_acc3vs5_VIP_1 <- vip.plsda(parent_all_acc3vs5, parent_all_acc3vs5$ATTRIBUTE_acclimation, path, "parent_all_acc3vs5")

parent_all_acc4vs5_VIP_1 <- vip.plsda(parent_all_acc4vs5, parent_all_acc4vs5$ATTRIBUTE_acclimation, path, "parent_all_acc4vs5")
```

``` {r PLSDA known acc, echo=TRUE, warning=FALSE, message=FALSE}
path <- "output/PLSDA_figs/"

#known direct parents by acclimation 
parent_known_acc1vs2_VIP_1 <- vip.plsda(parent_known_acc1vs2, parent_known_acc1vs2$ATTRIBUTE_acclimation, path, "parent_known_acc1vs2")

parent_known_acc1vs3_VIP_1 <- vip.plsda(parent_known_acc1vs3, parent_known_acc1vs3$ATTRIBUTE_acclimation, path, "parent_known_acc1vs3")

parent_known_acc1vs4_VIP_1 <- vip.plsda(parent_known_acc1vs4, parent_known_acc1vs4$ATTRIBUTE_acclimation, path, "parent_known_acc1vs4")

parent_known_acc1vs5_VIP_1 <- vip.plsda(parent_known_acc1vs5, parent_known_acc1vs5$ATTRIBUTE_acclimation, path, "parent_known_acc1vs5")

parent_known_acc2vs3_VIP_1 <- vip.plsda(parent_known_acc2vs3, parent_known_acc2vs3$ATTRIBUTE_acclimation, path, "parent_known_acc2vs3")

parent_known_acc2vs4_VIP_1 <- vip.plsda(parent_known_acc2vs4, parent_known_acc2vs4$ATTRIBUTE_acclimation, path, "parent_known_acc2vs4")

parent_known_acc2vs5_VIP_1 <- vip.plsda(parent_known_acc2vs5, parent_known_acc2vs5$ATTRIBUTE_acclimation, path, "parent_known_acc2vs5")

parent_known_acc3vs4_VIP_1 <- vip.plsda(parent_known_acc3vs4, parent_known_acc3vs4$ATTRIBUTE_acclimation, path, "parent_known_acc3vs4")

parent_known_acc3vs5_VIP_1 <- vip.plsda(parent_known_acc3vs5, parent_known_acc3vs5$ATTRIBUTE_acclimation, path, "parent_known_acc3vs5")

parent_known_acc4vs5_VIP_1 <- vip.plsda(parent_known_acc4vs5, parent_known_acc4vs5$ATTRIBUTE_acclimation, path, "parent_known_acc4vs5")
```

``` {r PLSDA all gen, echo=TRUE, warning=FALSE, message=FALSE}
path <- "output/PLSDA_figs/"

#all direct parents by genotype
parent_all_AZvsBY_VIP_1 <- vip.plsda(parent_all_AZvsBY, parent_all_AZvsBY$ATTRIBUTE_genotype, path, "parent_all_AZvsBY")

parent_all_AZvsCX_VIP_1 <- vip.plsda(parent_all_AZvsCX, parent_all_AZvsCX$ATTRIBUTE_genotype, path, "parent_all_AZvsCX")

parent_all_AZvsDW_VIP_1 <- vip.plsda(parent_all_AZvsDW, parent_all_AZvsDW$ATTRIBUTE_genotype, path, "parent_all_AZvsDW")

parent_all_AZvsEV_VIP_1 <- vip.plsda(parent_all_AZvsEV, parent_all_AZvsEV$ATTRIBUTE_genotype, path, "parent_all_AZvsEV")

parent_all_AZvsFU_VIP_1 <- vip.plsda(parent_all_AZvsFU, parent_all_AZvsFU$ATTRIBUTE_genotype, path, "parent_all_AZvsFU")

parent_all_AZvsGT_VIP_1 <- vip.plsda(parent_all_AZvsGT, parent_all_AZvsGT$ATTRIBUTE_genotype, path, "parent_all_AZvsGT")

parent_all_AZvsHS_VIP_1 <- vip.plsda(parent_all_AZvsHS, parent_all_AZvsHS$ATTRIBUTE_genotype, path, "parent_all_AZvsHS")

parent_all_AZvsIR_VIP_1 <- vip.plsda(parent_all_AZvsIR, parent_all_AZvsIR$ATTRIBUTE_genotype, path, "parent_all_AZvsIR")

parent_all_AZvsJQ_VIP_1 <- vip.plsda(parent_all_AZvsJQ, parent_all_AZvsJQ$ATTRIBUTE_genotype, path, "parent_all_AZvsJQ")


parent_all_BYvsCX_VIP_1 <- vip.plsda(parent_all_BYvsCX, parent_all_BYvsCX$ATTRIBUTE_genotype, path, "parent_all_BYvsCX")

parent_all_BYvsDW_VIP_1 <- vip.plsda(parent_all_BYvsDW, parent_all_BYvsDW$ATTRIBUTE_genotype, path, "parent_all_BYvsDW")

parent_all_BYvsEV_VIP_1 <- vip.plsda(parent_all_BYvsEV, parent_all_BYvsEV$ATTRIBUTE_genotype, path, "parent_all_BYvsEV")

parent_all_BYvsFU_VIP_1 <- vip.plsda(parent_all_BYvsFU, parent_all_BYvsFU$ATTRIBUTE_genotype, path, "parent_all_BYvsFU")

parent_all_BYvsGT_VIP_1 <- vip.plsda(parent_all_BYvsGT, parent_all_BYvsGT$ATTRIBUTE_genotype, path, "parent_all_BYvsGT")

parent_all_BYvsHS_VIP_1 <- vip.plsda(parent_all_BYvsHS, parent_all_BYvsHS$ATTRIBUTE_genotype, path, "parent_all_BYvsHS")

parent_all_BYvsIR_VIP_1 <- vip.plsda(parent_all_BYvsIR, parent_all_BYvsIR$ATTRIBUTE_genotype, path, "parent_all_BYvsIR")

parent_all_BYvsJQ_VIP_1 <- vip.plsda(parent_all_BYvsJQ, parent_all_BYvsJQ$ATTRIBUTE_genotype, path, "parent_all_BYvsJQ")


parent_all_CXvsDW_VIP_1 <- vip.plsda(parent_all_CXvsDW, parent_all_CXvsDW$ATTRIBUTE_genotype, path, "parent_all_CXvsDW")

parent_all_CXvsEV_VIP_1 <- vip.plsda(parent_all_CXvsEV, parent_all_CXvsEV$ATTRIBUTE_genotype, path, "parent_all_CXvsEV")

parent_all_CXvsFU_VIP_1 <- vip.plsda(parent_all_CXvsFU, parent_all_CXvsFU$ATTRIBUTE_genotype, path, "parent_all_CXvsFU")

parent_all_CXvsGT_VIP_1 <- vip.plsda(parent_all_CXvsGT, parent_all_CXvsGT$ATTRIBUTE_genotype, path, "parent_all_CXvsGT")

parent_all_CXvsHS_VIP_1 <- vip.plsda(parent_all_CXvsHS, parent_all_CXvsHS$ATTRIBUTE_genotype, path, "parent_all_CXvsHS")

parent_all_CXvsIR_VIP_1 <- vip.plsda(parent_all_CXvsIR, parent_all_CXvsIR$ATTRIBUTE_genotype, path, "parent_all_CXvsIR")

parent_all_CXvsJQ_VIP_1 <- vip.plsda(parent_all_CXvsJQ, parent_all_CXvsJQ$ATTRIBUTE_genotype, path, "parent_all_CXvsJQ")


parent_all_DWvsEV_VIP_1 <- vip.plsda(parent_all_DWvsEV, parent_all_DWvsEV$ATTRIBUTE_genotype, path, "parent_all_DWvsEV")

parent_all_DWvsFU_VIP_1 <- vip.plsda(parent_all_DWvsFU, parent_all_DWvsFU$ATTRIBUTE_genotype, path, "parent_all_DWvsFU")

parent_all_DWvsGT_VIP_1 <- vip.plsda(parent_all_DWvsGT, parent_all_DWvsGT$ATTRIBUTE_genotype, path, "parent_all_DWvsGT")

parent_all_DWvsHS_VIP_1 <- vip.plsda(parent_all_DWvsHS, parent_all_DWvsHS$ATTRIBUTE_genotype, path, "parent_all_DWvsHS")

parent_all_DWvsIR_VIP_1 <- vip.plsda(parent_all_DWvsIR, parent_all_DWvsIR$ATTRIBUTE_genotype, path, "parent_all_DWvsIR")

parent_all_DWvsJQ_VIP_1 <- vip.plsda(parent_all_DWvsJQ, parent_all_DWvsJQ$ATTRIBUTE_genotype, path, "parent_all_DWvsJQ")


parent_all_EVvsFU_VIP_1 <- vip.plsda(parent_all_EVvsFU, parent_all_EVvsFU$ATTRIBUTE_genotype, path, "parent_all_EVvsFU")

parent_all_EVvsGT_VIP_1 <- vip.plsda(parent_all_EVvsGT, parent_all_EVvsGT$ATTRIBUTE_genotype, path, "parent_all_EVvsGT")

parent_all_EVvsHS_VIP_1 <- vip.plsda(parent_all_EVvsHS, parent_all_EVvsHS$ATTRIBUTE_genotype, path, "parent_all_EVvsHS")

parent_all_EVvsIR_VIP_1 <- vip.plsda(parent_all_EVvsIR, parent_all_EVvsIR$ATTRIBUTE_genotype, path, "parent_all_EVvsIR")

parent_all_EVvsJQ_VIP_1 <- vip.plsda(parent_all_EVvsJQ, parent_all_EVvsJQ$ATTRIBUTE_genotype, path, "parent_all_EVvsJQ")


parent_all_FUvsGT_VIP_1 <- vip.plsda(parent_all_FUvsGT, parent_all_FUvsGT$ATTRIBUTE_genotype, path, "parent_all_FUvsGT")

parent_all_FUvsHS_VIP_1 <- vip.plsda(parent_all_FUvsHS, parent_all_FUvsHS$ATTRIBUTE_genotype, path, "parent_all_FUvsHS")

parent_all_FUvsIR_VIP_1 <- vip.plsda(parent_all_FUvsIR, parent_all_FUvsIR$ATTRIBUTE_genotype, path, "parent_all_FUvsIR")

parent_all_FUvsJQ_VIP_1 <- vip.plsda(parent_all_FUvsJQ, parent_all_FUvsJQ$ATTRIBUTE_genotype, path, "parent_all_FUvsJQ")


parent_all_GTvsHS_VIP_1 <- vip.plsda(parent_all_GTvsHS, parent_all_GTvsHS$ATTRIBUTE_genotype, path, "parent_all_GTvsHS")

parent_all_GTvsIR_VIP_1 <- vip.plsda(parent_all_GTvsIR, parent_all_GTvsIR$ATTRIBUTE_genotype, path, "parent_all_GTvsIR")

parent_all_GTvsJQ_VIP_1 <- vip.plsda(parent_all_GTvsJQ, parent_all_GTvsJQ$ATTRIBUTE_genotype, path, "parent_all_GTvsJQ")


parent_all_HSvsIR_VIP_1 <- vip.plsda(parent_all_HSvsIR, parent_all_HSvsIR$ATTRIBUTE_genotype, path, "parent_all_HSvsIR")

parent_all_HSvsJQ_VIP_1 <- vip.plsda(parent_all_HSvsJQ, parent_all_HSvsJQ$ATTRIBUTE_genotype, path, "parent_all_HSvsJQ")


parent_all_IRvsJQ_VIP_1 <- vip.plsda(parent_all_IRvsJQ, parent_all_IRvsJQ$ATTRIBUTE_genotype, path, "parent_all_IRvsJQ")
```

``` {r PLSDA known gen, echo=TRUE, warning=FALSE, message=FALSE}
path <- "output/PLSDA_figs/"

#known direct parents by genotype
parent_known_AZvsBY_VIP_1 <- vip.plsda(parent_known_AZvsBY, parent_known_AZvsBY$ATTRIBUTE_genotype, path, "parent_known_AZvsBY")

parent_known_AZvsCX_VIP_1 <- vip.plsda(parent_known_AZvsCX, parent_known_AZvsCX$ATTRIBUTE_genotype, path, "parent_known_AZvsCX")

parent_known_AZvsDW_VIP_1 <- vip.plsda(parent_known_AZvsDW, parent_known_AZvsDW$ATTRIBUTE_genotype, path, "parent_known_AZvsDW")

parent_known_AZvsEV_VIP_1 <- vip.plsda(parent_known_AZvsEV, parent_known_AZvsEV$ATTRIBUTE_genotype, path, "parent_known_AZvsEV")

parent_known_AZvsFU_VIP_1 <- vip.plsda(parent_known_AZvsFU, parent_known_AZvsFU$ATTRIBUTE_genotype, path, "parent_known_AZvsFU")

parent_known_AZvsGT_VIP_1 <- vip.plsda(parent_known_AZvsGT, parent_known_AZvsGT$ATTRIBUTE_genotype, path, "parent_known_AZvsGT")

parent_known_AZvsHS_VIP_1 <- vip.plsda(parent_known_AZvsHS, parent_known_AZvsHS$ATTRIBUTE_genotype, path, "parent_known_AZvsHS")

parent_known_AZvsIR_VIP_1 <- vip.plsda(parent_known_AZvsIR, parent_known_AZvsIR$ATTRIBUTE_genotype, path, "parent_known_AZvsIR")

parent_known_AZvsJQ_VIP_1 <- vip.plsda(parent_known_AZvsJQ, parent_known_AZvsJQ$ATTRIBUTE_genotype, path, "parent_known_AZvsJQ")


parent_known_BYvsCX_VIP_1 <- vip.plsda(parent_known_BYvsCX, parent_known_BYvsCX$ATTRIBUTE_genotype, path, "parent_known_BYvsCX")

parent_known_BYvsDW_VIP_1 <- vip.plsda(parent_known_BYvsDW, parent_known_BYvsDW$ATTRIBUTE_genotype, path, "parent_known_BYvsDW")

parent_known_BYvsEV_VIP_1 <- vip.plsda(parent_known_BYvsEV, parent_known_BYvsEV$ATTRIBUTE_genotype, path, "parent_known_BYvsEV")

parent_known_BYvsFU_VIP_1 <- vip.plsda(parent_known_BYvsFU, parent_known_BYvsFU$ATTRIBUTE_genotype, path, "parent_known_BYvsFU")

parent_known_BYvsGT_VIP_1 <- vip.plsda(parent_known_BYvsGT, parent_known_BYvsGT$ATTRIBUTE_genotype, path, "parent_known_BYvsGT")

parent_known_BYvsHS_VIP_1 <- vip.plsda(parent_known_BYvsHS, parent_known_BYvsHS$ATTRIBUTE_genotype, path, "parent_known_BYvsHS")

parent_known_BYvsIR_VIP_1 <- vip.plsda(parent_known_BYvsIR, parent_known_BYvsIR$ATTRIBUTE_genotype, path, "parent_known_BYvsIR")

parent_known_BYvsJQ_VIP_1 <- vip.plsda(parent_known_BYvsJQ, parent_known_BYvsJQ$ATTRIBUTE_genotype, path, "parent_known_BYvsJQ")


parent_known_CXvsDW_VIP_1 <- vip.plsda(parent_known_CXvsDW, parent_known_CXvsDW$ATTRIBUTE_genotype, path, "parent_known_CXvsDW")

parent_known_CXvsEV_VIP_1 <- vip.plsda(parent_known_CXvsEV, parent_known_CXvsEV$ATTRIBUTE_genotype, path, "parent_known_CXvsEV")

parent_known_CXvsFU_VIP_1 <- vip.plsda(parent_known_CXvsFU, parent_known_CXvsFU$ATTRIBUTE_genotype, path, "parent_known_CXvsFU")

parent_known_CXvsGT_VIP_1 <- vip.plsda(parent_known_CXvsGT, parent_known_CXvsGT$ATTRIBUTE_genotype, path, "parent_known_CXvsGT")

parent_known_CXvsHS_VIP_1 <- vip.plsda(parent_known_CXvsHS, parent_known_CXvsHS$ATTRIBUTE_genotype, path, "parent_known_CXvsHS")

parent_known_CXvsIR_VIP_1 <- vip.plsda(parent_known_CXvsIR, parent_known_CXvsIR$ATTRIBUTE_genotype, path, "parent_known_CXvsIR")

parent_known_CXvsJQ_VIP_1 <- vip.plsda(parent_known_CXvsJQ, parent_known_CXvsJQ$ATTRIBUTE_genotype, path, "parent_known_CXvsJQ")


parent_known_DWvsEV_VIP_1 <- vip.plsda(parent_known_DWvsEV, parent_known_DWvsEV$ATTRIBUTE_genotype, path, "parent_known_DWvsEV")

parent_known_DWvsFU_VIP_1 <- vip.plsda(parent_known_DWvsFU, parent_known_DWvsFU$ATTRIBUTE_genotype, path, "parent_known_DWvsFU")

parent_known_DWvsGT_VIP_1 <- vip.plsda(parent_known_DWvsGT, parent_known_DWvsGT$ATTRIBUTE_genotype, path, "parent_known_DWvsGT")

parent_known_DWvsHS_VIP_1 <- vip.plsda(parent_known_DWvsHS, parent_known_DWvsHS$ATTRIBUTE_genotype, path, "parent_known_DWvsHS")

parent_known_DWvsIR_VIP_1 <- vip.plsda(parent_known_DWvsIR, parent_known_DWvsIR$ATTRIBUTE_genotype, path, "parent_known_DWvsIR")

parent_known_DWvsJQ_VIP_1 <- vip.plsda(parent_known_DWvsJQ, parent_known_DWvsJQ$ATTRIBUTE_genotype, path, "parent_known_DWvsJQ")


parent_known_EVvsFU_VIP_1 <- vip.plsda(parent_known_EVvsFU, parent_known_EVvsFU$ATTRIBUTE_genotype, path, "parent_known_EVvsFU")

parent_known_EVvsGT_VIP_1 <- vip.plsda(parent_known_EVvsGT, parent_known_EVvsGT$ATTRIBUTE_genotype, path, "parent_known_EVvsGT")

parent_known_EVvsHS_VIP_1 <- vip.plsda(parent_known_EVvsHS, parent_known_EVvsHS$ATTRIBUTE_genotype, path, "parent_known_EVvsHS")

parent_known_EVvsIR_VIP_1 <- vip.plsda(parent_known_EVvsIR, parent_known_EVvsIR$ATTRIBUTE_genotype, path, "parent_known_EVvsIR")

parent_known_EVvsJQ_VIP_1 <- vip.plsda(parent_known_EVvsJQ, parent_known_EVvsJQ$ATTRIBUTE_genotype, path, "parent_known_EVvsJQ")


parent_known_FUvsGT_VIP_1 <- vip.plsda(parent_known_FUvsGT, parent_known_FUvsGT$ATTRIBUTE_genotype, path, "parent_known_FUvsGT")

parent_known_FUvsHS_VIP_1 <- vip.plsda(parent_known_FUvsHS, parent_known_FUvsHS$ATTRIBUTE_genotype, path, "parent_known_FUvsHS")

parent_known_FUvsIR_VIP_1 <- vip.plsda(parent_known_FUvsIR, parent_known_FUvsIR$ATTRIBUTE_genotype, path, "parent_known_FUvsIR")

parent_known_FUvsJQ_VIP_1 <- vip.plsda(parent_known_FUvsJQ, parent_known_FUvsJQ$ATTRIBUTE_genotype, path, "parent_known_FUvsJQ")


parent_known_GTvsHS_VIP_1 <- vip.plsda(parent_known_GTvsHS, parent_known_GTvsHS$ATTRIBUTE_genotype, path, "parent_known_GTvsHS")

parent_known_GTvsIR_VIP_1 <- vip.plsda(parent_known_GTvsIR, parent_known_GTvsIR$ATTRIBUTE_genotype, path, "parent_known_GTvsIR")

parent_known_GTvsJQ_VIP_1 <- vip.plsda(parent_known_GTvsJQ, parent_known_GTvsJQ$ATTRIBUTE_genotype, path, "parent_known_GTvsJQ")


parent_known_HSvsIR_VIP_1 <- vip.plsda(parent_known_HSvsIR, parent_known_HSvsIR$ATTRIBUTE_genotype, path, "parent_known_HSvsIR")

parent_known_HSvsJQ_VIP_1 <- vip.plsda(parent_known_HSvsJQ, parent_known_HSvsJQ$ATTRIBUTE_genotype, path, "parent_known_HSvsJQ")


parent_known_IRvsJQ_VIP_1 <- vip.plsda(parent_known_IRvsJQ, parent_known_IRvsJQ$ATTRIBUTE_genotype, path, "parent_known_IRvsJQ")
```


### Creating a t-test and FDR correction function
### Two tests: one for acclimation treatments, one for genotypes 
```{r testFunction acc, echo=TRUE, warning=FALSE, message=FALSE}

vip.ttest <- function(data, 
                      VIP_data,
                      est1,
                      est2
                      ) { 
## Gather data frame and group by metabolite 
data <- droplevels(data)
data_gather <- data %>% gather(key = "DirectParent", value = "Count", -ATTRIBUTE_sampleID, -ATTRIBUTE_genotype, -ATTRIBUTE_acclimation, -ATTRIBUTE_dryweight) %>% dplyr::select("ATTRIBUTE_acclimation", "DirectParent", "Count")

data_gather$ATTRIBUTE_acclimation <- as.factor(data_gather$ATTRIBUTE_acclimation)

data_gather$ATTRIBUTE_acclimation <- droplevels(data_gather$ATTRIBUTE_acclimation)

data_gather <- dplyr::group_by(data_gather, DirectParent)
data_gather$ATTRIBUTE_acclimation <- droplevels(data_gather$ATTRIBUTE_acclimation)

# Select metabolites only present from the PLS-DA with VIPs >1
VIP_Select <- subset(data_gather, data_gather$DirectParent %in% VIP_data$DirectParent)

VIP_Select$ATTRIBUTE_acclimation <- droplevels(VIP_Select$ATTRIBUTE_acclimation)

#Looped t-test for all metabolites with VIPs >1, estimate 1 = Bleached_Hot, estimate 2 = Control
t.test <-do(VIP_Select, tidy(t.test(.$Count ~ .$ATTRIBUTE_acclimation,
                 alternative = "two.sided",
                 mu = 0,
                 paired = FALSE,
                 var.equal = FALSE,
                 conf.level = 0.95
                 )))

#adjust p value for the number of comparisons
t.test$p.adj<-p.adjust(t.test$p.value, method=c("fdr"), n=length(VIP_data$DirectParent)) #length = number of metabolites tested, false discovery rate method

# Filter for significantly different metabolites (p < 0.05)
t.test.fdr <- t.test %>% filter(p.adj <= 0.05)

# Filter for metabolites accumulated for est1
t.test.sig.up <- t.test.fdr %>% filter(estimate1 > estimate2)
t.test.sig.up$Enrichment.dir <- est1

# Filter for metabolites accumulated for est2
t.test.sig.down <- t.test.fdr %>% filter(estimate1 < estimate2)
t.test.sig.down$Enrichment.dir <- est2

#Combining data sets
t.test.sig.final <- rbind(t.test.sig.up, t.test.sig.down)
return(t.test.sig.final)
}
```

```{r testFunction gen, echo=TRUE, warning=FALSE, message=FALSE}

vip.ttest2 <- function(data, 
                      VIP_data,
                      est1,
                      est2
                      ) { 
## Gather data frame and group by metabolite 
data <- droplevels(data)
data_gather <- data %>% gather(key = "DirectParent", value = "Count", -ATTRIBUTE_sampleID, -ATTRIBUTE_genotype, -ATTRIBUTE_acclimation, -ATTRIBUTE_dryweight) %>% dplyr::select("ATTRIBUTE_genotype", "DirectParent", "Count")

data_gather$ATTRIBUTE_genotype <- as.factor(data_gather$ATTRIBUTE_genotype)

data_gather$ATTRIBUTE_genotype <- droplevels(data_gather$ATTRIBUTE_genotype)

data_gather <- dplyr::group_by(data_gather, DirectParent)
data_gather$ATTRIBUTE_genotype <- droplevels(data_gather$ATTRIBUTE_genotype)

# Select metabolites only present from the PLS-DA with VIPs >1
VIP_Select <- subset(data_gather, data_gather$DirectParent %in% VIP_data$DirectParent)

VIP_Select$ATTRIBUTE_genotype <- droplevels(VIP_Select$ATTRIBUTE_genotype)

#Looped t-test for all metabolites with VIPs >1, estimate 1 = Bleached_Hot, estimate 2 = Control
t.test <-do(VIP_Select, tidy(t.test(.$Count ~ .$ATTRIBUTE_genotype,
                 alternative = "two.sided",
                 mu = 0,
                 paired = FALSE,
                 var.equal = FALSE,
                 conf.level = 0.95
                 )))

#adjust p value for the number of comparisons
t.test$p.adj<-p.adjust(t.test$p.value, method=c("fdr"), n=length(VIP_data$DirectParent)) #length = number of metabolites tested, false discovery rate method

# Filter for significantly different metabolites (p < 0.05)
t.test.fdr <- t.test %>% filter(p.adj <= 0.05)

# Filter for metabolites accumulated for est1
t.test.sig.up <- t.test.fdr %>% filter(estimate1 > estimate2)
t.test.sig.up$Enrichment.dir <- est1

# Filter for metabolites accumulated for est2
t.test.sig.down <- t.test.fdr %>% filter(estimate1 < estimate2)
t.test.sig.down$Enrichment.dir <- est2

#Combining data sets
t.test.sig.final <- rbind(t.test.sig.up, t.test.sig.down)
return(t.test.sig.final)
}
```


# T-test and FDR correction of metabolites with VIPs >1

``` {r ttest all acc, echo=TRUE}
#all compounds by acclimation treatment

parent_all_acc1vs2_VIP_sig <- vip.ttest(parent_all_acc1vs2, parent_all_acc1vs2_VIP_1, "Acclimation 1", "Acclimation 2")

parent_all_acc1vs3_VIP_sig <- vip.ttest(parent_all_acc1vs3, parent_all_acc1vs3_VIP_1, "Acclimation 1", "Acclimation 3")

parent_all_acc1vs4_VIP_sig <- vip.ttest(parent_all_acc1vs4, parent_all_acc1vs4_VIP_1, "Acclimation 1", "Acclimation 4")

parent_all_acc1vs5_VIP_sig <- vip.ttest(parent_all_acc1vs5, parent_all_acc1vs5_VIP_1, "Acclimation 1", "Acclimation 5")


parent_all_acc2vs3_VIP_sig <- vip.ttest(parent_all_acc2vs3, parent_all_acc2vs3_VIP_1, "Acclimation 2", "Acclimation 3")

parent_all_acc2vs4_VIP_sig <- vip.ttest(parent_all_acc2vs4, parent_all_acc2vs4_VIP_1, "Acclimation 2", "Acclimation 4")

parent_all_acc2vs5_VIP_sig <- vip.ttest(parent_all_acc2vs5, parent_all_acc2vs5_VIP_1, "Acclimation 2", "Acclimation 5")


parent_all_acc3vs4_VIP_sig <- vip.ttest(parent_all_acc3vs4, parent_all_acc3vs4_VIP_1, "Acclimation 3", "Acclimation 4")

parent_all_acc3vs5_VIP_sig <- vip.ttest(parent_all_acc3vs5, parent_all_acc3vs5_VIP_1, "Acclimation 3", "Acclimation 5")


parent_all_acc4vs5_VIP_sig <- vip.ttest(parent_all_acc4vs5, parent_all_acc4vs5_VIP_1, "Acclimation 4", "Acclimation 5")
```

``` {r ttest known acc, echo=TRUE}
#known compounds by acclimation treatment

parent_known_acc1vs2_VIP_sig <- vip.ttest(parent_known_acc1vs2, parent_known_acc1vs2_VIP_1, "Acclimation 1", "Acclimation 2")

parent_known_acc1vs3_VIP_sig <- vip.ttest(parent_known_acc1vs3, parent_known_acc1vs3_VIP_1, "Acclimation 1", "Acclimation 3")

parent_known_acc1vs4_VIP_sig <- vip.ttest(parent_known_acc1vs4, parent_known_acc1vs4_VIP_1, "Acclimation 1", "Acclimation 4")

parent_known_acc1vs5_VIP_sig <- vip.ttest(parent_known_acc1vs5, parent_known_acc1vs5_VIP_1, "Acclimation 1", "Acclimation 5")


parent_known_acc2vs3_VIP_sig <- vip.ttest(parent_known_acc2vs3, parent_known_acc2vs3_VIP_1, "Acclimation 2", "Acclimation 3")

parent_known_acc2vs4_VIP_sig <- vip.ttest(parent_known_acc2vs4, parent_known_acc2vs4_VIP_1, "Acclimation 2", "Acclimation 4")

parent_known_acc2vs5_VIP_sig <- vip.ttest(parent_known_acc2vs5, parent_known_acc2vs5_VIP_1, "Acclimation 2", "Acclimation 5")


parent_known_acc3vs4_VIP_sig <- vip.ttest(parent_known_acc3vs4, parent_known_acc3vs4_VIP_1, "Acclimation 3", "Acclimation 4")

parent_known_acc3vs5_VIP_sig <- vip.ttest(parent_known_acc3vs5, parent_known_acc3vs5_VIP_1, "Acclimation 3", "Acclimation 5")


parent_known_acc4vs5_VIP_sig <- vip.ttest(parent_known_acc4vs5, parent_known_acc4vs5_VIP_1, "Acclimation 4", "Acclimation 5")
```

```{r ttest all gen, echo=TRUE}
#all compounds by genotype
parent_all_AZvsBY_VIP_sig <- vip.ttest2(parent_all_AZvsBY, parent_all_AZvsBY_VIP_1, "AZ", "BY")
parent_all_AZvsCX_VIP_sig <- vip.ttest2(parent_all_AZvsCX, parent_all_AZvsCX_VIP_1, "AZ", "CX")
parent_all_AZvsDW_VIP_sig <- vip.ttest2(parent_all_AZvsDW, parent_all_AZvsDW_VIP_1, "AZ", "DW")
parent_all_AZvsEV_VIP_sig <- vip.ttest2(parent_all_AZvsEV, parent_all_AZvsEV_VIP_1, "AZ", "EV")
parent_all_AZvsFU_VIP_sig <- vip.ttest2(parent_all_AZvsFU, parent_all_AZvsFU_VIP_1, "AZ", "FU")
parent_all_AZvsGT_VIP_sig <- vip.ttest2(parent_all_AZvsGT, parent_all_AZvsGT_VIP_1, "AZ", "GT")
parent_all_AZvsHS_VIP_sig <- vip.ttest2(parent_all_AZvsHS, parent_all_AZvsHS_VIP_1, "AZ", "HS")
parent_all_AZvsIR_VIP_sig <- vip.ttest2(parent_all_AZvsIR, parent_all_AZvsIR_VIP_1, "AZ", "IR")
parent_all_AZvsJQ_VIP_sig <- vip.ttest2(parent_all_AZvsJQ, parent_all_AZvsJQ_VIP_1, "AZ", "JQ")

parent_all_BYvsCX_VIP_sig <- vip.ttest2(parent_all_BYvsCX, parent_all_BYvsCX_VIP_1, "BY", "CX")
parent_all_BYvsDW_VIP_sig <- vip.ttest2(parent_all_BYvsDW, parent_all_BYvsDW_VIP_1, "BY", "DW")
parent_all_BYvsEV_VIP_sig <- vip.ttest2(parent_all_BYvsEV, parent_all_BYvsEV_VIP_1, "BY", "EV")
parent_all_BYvsFU_VIP_sig <- vip.ttest2(parent_all_BYvsFU, parent_all_BYvsFU_VIP_1, "BY", "FU")
parent_all_BYvsGT_VIP_sig <- vip.ttest2(parent_all_BYvsGT, parent_all_BYvsGT_VIP_1, "BY", "GT")
parent_all_BYvsHS_VIP_sig <- vip.ttest2(parent_all_BYvsHS, parent_all_BYvsHS_VIP_1, "BY", "HS")
parent_all_BYvsIR_VIP_sig <- vip.ttest2(parent_all_BYvsIR, parent_all_BYvsIR_VIP_1, "BY", "IR")
parent_all_BYvsJQ_VIP_sig <- vip.ttest2(parent_all_BYvsJQ, parent_all_BYvsJQ_VIP_1, "BY", "JQ")

parent_all_CXvsDW_VIP_sig <- vip.ttest2(parent_all_CXvsDW, parent_all_CXvsDW_VIP_1, "CX", "DW")
parent_all_CXvsEV_VIP_sig <- vip.ttest2(parent_all_CXvsEV, parent_all_CXvsEV_VIP_1, "CX", "EV")
parent_all_CXvsFU_VIP_sig <- vip.ttest2(parent_all_CXvsFU, parent_all_CXvsFU_VIP_1, "CX", "FU")
parent_all_CXvsGT_VIP_sig <- vip.ttest2(parent_all_CXvsGT, parent_all_CXvsGT_VIP_1, "CX", "GT")
parent_all_CXvsHS_VIP_sig <- vip.ttest2(parent_all_CXvsHS, parent_all_CXvsHS_VIP_1, "CX", "HS")
parent_all_CXvsIR_VIP_sig <- vip.ttest2(parent_all_CXvsIR, parent_all_CXvsIR_VIP_1, "CX", "IR")
parent_all_CXvsJQ_VIP_sig <- vip.ttest2(parent_all_CXvsJQ, parent_all_CXvsJQ_VIP_1, "CX", "JQ")

parent_all_DWvsEV_VIP_sig <- vip.ttest2(parent_all_DWvsEV, parent_all_DWvsEV_VIP_1, "DW", "EV")
parent_all_DWvsFU_VIP_sig <- vip.ttest2(parent_all_DWvsFU, parent_all_DWvsFU_VIP_1, "DW", "FU")
parent_all_DWvsGT_VIP_sig <- vip.ttest2(parent_all_DWvsGT, parent_all_DWvsGT_VIP_1, "DW", "GT")
parent_all_DWvsHS_VIP_sig <- vip.ttest2(parent_all_DWvsHS, parent_all_DWvsHS_VIP_1, "DW", "HS")
parent_all_DWvsIR_VIP_sig <- vip.ttest2(parent_all_DWvsIR, parent_all_DWvsIR_VIP_1, "DW", "IR")
parent_all_DWvsJQ_VIP_sig <- vip.ttest2(parent_all_DWvsJQ, parent_all_DWvsJQ_VIP_1, "DW", "JQ")

parent_all_EVvsFU_VIP_sig <- vip.ttest2(parent_all_EVvsFU, parent_all_EVvsFU_VIP_1, "EV", "FU")
parent_all_EVvsGT_VIP_sig <- vip.ttest2(parent_all_EVvsGT, parent_all_EVvsGT_VIP_1, "EV", "GT")
parent_all_EVvsHS_VIP_sig <- vip.ttest2(parent_all_EVvsHS, parent_all_EVvsHS_VIP_1, "EV", "HS")
parent_all_EVvsIR_VIP_sig <- vip.ttest2(parent_all_EVvsIR, parent_all_EVvsIR_VIP_1, "EV", "IR")
parent_all_EVvsJQ_VIP_sig <- vip.ttest2(parent_all_EVvsJQ, parent_all_EVvsJQ_VIP_1, "EV", "JQ")

parent_all_FUvsGT_VIP_sig <- vip.ttest2(parent_all_FUvsGT, parent_all_FUvsGT_VIP_1, "FU", "GT")
parent_all_FUvsHS_VIP_sig <- vip.ttest2(parent_all_FUvsHS, parent_all_FUvsHS_VIP_1, "FU", "HS")
parent_all_FUvsIR_VIP_sig <- vip.ttest2(parent_all_FUvsIR, parent_all_FUvsIR_VIP_1, "FU", "IR")
parent_all_FUvsJQ_VIP_sig <- vip.ttest2(parent_all_FUvsJQ, parent_all_FUvsJQ_VIP_1, "FU", "JQ")

parent_all_GTvsHS_VIP_sig <- vip.ttest2(parent_all_GTvsHS, parent_all_GTvsHS_VIP_1, "GT", "HS")
parent_all_GTvsIR_VIP_sig <- vip.ttest2(parent_all_GTvsIR, parent_all_GTvsIR_VIP_1, "GT", "IR")
parent_all_GTvsJQ_VIP_sig <- vip.ttest2(parent_all_GTvsJQ, parent_all_GTvsJQ_VIP_1, "GT", "JQ")

parent_all_HSvsIR_VIP_sig <- vip.ttest2(parent_all_HSvsIR, parent_all_HSvsIR_VIP_1, "HS", "IR")
parent_all_HSvsJQ_VIP_sig <- vip.ttest2(parent_all_HSvsJQ, parent_all_HSvsJQ_VIP_1, "HS", "JQ")

parent_all_IRvsJQ_VIP_sig <- vip.ttest2(parent_all_IRvsJQ, parent_all_IRvsJQ_VIP_1, "IR", "JQ")
```

```{r ttest known gen, echo=TRUE}
#all compounds by genotype
parent_known_AZvsBY_VIP_sig <- vip.ttest2(parent_known_AZvsBY, parent_known_AZvsBY_VIP_1, "AZ", "BY")
parent_known_AZvsCX_VIP_sig <- vip.ttest2(parent_known_AZvsCX, parent_known_AZvsCX_VIP_1, "AZ", "CX")
parent_known_AZvsDW_VIP_sig <- vip.ttest2(parent_known_AZvsDW, parent_known_AZvsDW_VIP_1, "AZ", "DW")
parent_known_AZvsEV_VIP_sig <- vip.ttest2(parent_known_AZvsEV, parent_known_AZvsEV_VIP_1, "AZ", "EV")
parent_known_AZvsFU_VIP_sig <- vip.ttest2(parent_known_AZvsFU, parent_known_AZvsFU_VIP_1, "AZ", "FU")
parent_known_AZvsGT_VIP_sig <- vip.ttest2(parent_known_AZvsGT, parent_known_AZvsGT_VIP_1, "AZ", "GT")
parent_known_AZvsHS_VIP_sig <- vip.ttest2(parent_known_AZvsHS, parent_known_AZvsHS_VIP_1, "AZ", "HS")
parent_known_AZvsIR_VIP_sig <- vip.ttest2(parent_known_AZvsIR, parent_known_AZvsIR_VIP_1, "AZ", "IR")
parent_known_AZvsJQ_VIP_sig <- vip.ttest2(parent_known_AZvsJQ, parent_known_AZvsJQ_VIP_1, "AZ", "JQ")

parent_known_BYvsCX_VIP_sig <- vip.ttest2(parent_known_BYvsCX, parent_known_BYvsCX_VIP_1, "BY", "CX")
parent_known_BYvsDW_VIP_sig <- vip.ttest2(parent_known_BYvsDW, parent_known_BYvsDW_VIP_1, "BY", "DW")
parent_known_BYvsEV_VIP_sig <- vip.ttest2(parent_known_BYvsEV, parent_known_BYvsEV_VIP_1, "BY", "EV")
parent_known_BYvsFU_VIP_sig <- vip.ttest2(parent_known_BYvsFU, parent_known_BYvsFU_VIP_1, "BY", "FU")
parent_known_BYvsGT_VIP_sig <- vip.ttest2(parent_known_BYvsGT, parent_known_BYvsGT_VIP_1, "BY", "GT")
parent_known_BYvsHS_VIP_sig <- vip.ttest2(parent_known_BYvsHS, parent_known_BYvsHS_VIP_1, "BY", "HS")
parent_known_BYvsIR_VIP_sig <- vip.ttest2(parent_known_BYvsIR, parent_known_BYvsIR_VIP_1, "BY", "IR")
parent_known_BYvsJQ_VIP_sig <- vip.ttest2(parent_known_BYvsJQ, parent_known_BYvsJQ_VIP_1, "BY", "JQ")

parent_known_CXvsDW_VIP_sig <- vip.ttest2(parent_known_CXvsDW, parent_known_CXvsDW_VIP_1, "CX", "DW")
parent_known_CXvsEV_VIP_sig <- vip.ttest2(parent_known_CXvsEV, parent_known_CXvsEV_VIP_1, "CX", "EV")
parent_known_CXvsFU_VIP_sig <- vip.ttest2(parent_known_CXvsFU, parent_known_CXvsFU_VIP_1, "CX", "FU")
parent_known_CXvsGT_VIP_sig <- vip.ttest2(parent_known_CXvsGT, parent_known_CXvsGT_VIP_1, "CX", "GT")
parent_known_CXvsHS_VIP_sig <- vip.ttest2(parent_known_CXvsHS, parent_known_CXvsHS_VIP_1, "CX", "HS")
parent_known_CXvsIR_VIP_sig <- vip.ttest2(parent_known_CXvsIR, parent_known_CXvsIR_VIP_1, "CX", "IR")
parent_known_CXvsJQ_VIP_sig <- vip.ttest2(parent_known_CXvsJQ, parent_known_CXvsJQ_VIP_1, "CX", "JQ")

parent_known_DWvsEV_VIP_sig <- vip.ttest2(parent_known_DWvsEV, parent_known_DWvsEV_VIP_1, "DW", "EV")
parent_known_DWvsFU_VIP_sig <- vip.ttest2(parent_known_DWvsFU, parent_known_DWvsFU_VIP_1, "DW", "FU")
parent_known_DWvsGT_VIP_sig <- vip.ttest2(parent_known_DWvsGT, parent_known_DWvsGT_VIP_1, "DW", "GT")
parent_known_DWvsHS_VIP_sig <- vip.ttest2(parent_known_DWvsHS, parent_known_DWvsHS_VIP_1, "DW", "HS")
parent_known_DWvsIR_VIP_sig <- vip.ttest2(parent_known_DWvsIR, parent_known_DWvsIR_VIP_1, "DW", "IR")
parent_known_DWvsJQ_VIP_sig <- vip.ttest2(parent_known_DWvsJQ, parent_known_DWvsJQ_VIP_1, "DW", "JQ")

parent_known_EVvsFU_VIP_sig <- vip.ttest2(parent_known_EVvsFU, parent_known_EVvsFU_VIP_1, "EV", "FU")
parent_known_EVvsGT_VIP_sig <- vip.ttest2(parent_known_EVvsGT, parent_known_EVvsGT_VIP_1, "EV", "GT")
parent_known_EVvsHS_VIP_sig <- vip.ttest2(parent_known_EVvsHS, parent_known_EVvsHS_VIP_1, "EV", "HS")
parent_known_EVvsIR_VIP_sig <- vip.ttest2(parent_known_EVvsIR, parent_known_EVvsIR_VIP_1, "EV", "IR")
parent_known_EVvsJQ_VIP_sig <- vip.ttest2(parent_known_EVvsJQ, parent_known_EVvsJQ_VIP_1, "EV", "JQ")

parent_known_FUvsGT_VIP_sig <- vip.ttest2(parent_known_FUvsGT, parent_known_FUvsGT_VIP_1, "FU", "GT")
parent_known_FUvsHS_VIP_sig <- vip.ttest2(parent_known_FUvsHS, parent_known_FUvsHS_VIP_1, "FU", "HS")
parent_known_FUvsIR_VIP_sig <- vip.ttest2(parent_known_FUvsIR, parent_known_FUvsIR_VIP_1, "FU", "IR")
parent_known_FUvsJQ_VIP_sig <- vip.ttest2(parent_known_FUvsJQ, parent_known_FUvsJQ_VIP_1, "FU", "JQ")

parent_known_GTvsHS_VIP_sig <- vip.ttest2(parent_known_GTvsHS, parent_known_GTvsHS_VIP_1, "GT", "HS")
parent_known_GTvsIR_VIP_sig <- vip.ttest2(parent_known_GTvsIR, parent_known_GTvsIR_VIP_1, "GT", "IR")
parent_known_GTvsJQ_VIP_sig <- vip.ttest2(parent_known_GTvsJQ, parent_known_GTvsJQ_VIP_1, "GT", "JQ")

parent_known_HSvsIR_VIP_sig <- vip.ttest2(parent_known_HSvsIR, parent_known_HSvsIR_VIP_1, "HS", "IR")
parent_known_HSvsJQ_VIP_sig <- vip.ttest2(parent_known_HSvsJQ, parent_known_HSvsJQ_VIP_1, "HS", "JQ")

parent_known_IRvsJQ_VIP_sig <- vip.ttest2(parent_known_IRvsJQ, parent_known_IRvsJQ_VIP_1, "IR", "JQ")
```


### Assigning known and unknown values to All detected metabolite datasets

``` {r knownunknown acc, echo=TRUE, warning=FALSE, message=FALSE}
parent_all_acc1vs2_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc1vs2_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc1vs3_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc1vs3_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc1vs4_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc1vs4_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc1vs5_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc1vs5_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_acc2vs3_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc2vs3_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc2vs4_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc2vs4_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc2vs5_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc2vs5_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_acc3vs4_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc3vs4_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_acc3vs5_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc3vs5_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_acc4vs5_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_acc4vs5_VIP_sig$DirectParent), 'Unknown', 'Identified')
```

``` {r knownunknown gen, echo=TRUE, warning=FALSE, message=FALSE}
parent_all_AZvsBY_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsBY_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsCX_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsCX_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsDW_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsDW_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsEV_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsEV_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsFU_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsFU_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_AZvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_AZvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_BYvsCX_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsCX_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsDW_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsDW_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsEV_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsEV_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsFU_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsFU_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_BYvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_BYvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_CXvsDW_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsDW_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsEV_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsEV_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsFU_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsFU_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_CXvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_CXvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_DWvsEV_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsEV_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_DWvsFU_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsFU_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_DWvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_DWvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_DWvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_DWvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_DWvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_EVvsFU_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_EVvsFU_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_EVvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_EVvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_EVvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_EVvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_EVvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_EVvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_EVvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_EVvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_FUvsGT_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_FUvsGT_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_FUvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_FUvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_FUvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_FUvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_FUvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_FUvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_GTvsHS_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_GTvsHS_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_GTvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_GTvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_GTvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_GTvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_HSvsIR_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_HSvsIR_VIP_sig$DirectParent), 'Unknown', 'Identified')

parent_all_HSvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_HSvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')


parent_all_IRvsJQ_VIP_sig$Feature.status <- ifelse(grepl("unclassified", parent_all_IRvsJQ_VIP_sig$DirectParent), 'Unknown', 'Identified')
```


### Summary statsitics of known vs unknown metabolites

``` {r Knownstats acc, echo=TRUE, warning=FALSE, message=FALSE}
path2 <- "output/"

filenames <- list.files(path = path2, pattern="csv$") #figure out how to loop this

parent_all_acc1vs2_VIP_table <- as.data.frame(t(table(parent_all_acc1vs2_VIP_sig['Feature.status'])))

parent_all_acc1vs3_VIP_table <- as.data.frame(t(table(parent_all_acc1vs3_VIP_sig['Feature.status'])))

parent_all_acc1vs4_VIP_table <- as.data.frame(t(table(parent_all_acc1vs4_VIP_sig['Feature.status'])))

parent_all_acc1vs5_VIP_table <- as.data.frame(t(table(parent_all_acc1vs5_VIP_sig['Feature.status'])))


parent_all_acc2vs3_VIP_table <- as.data.frame(t(table(parent_all_acc2vs3_VIP_sig['Feature.status'])))

parent_all_acc2vs4_VIP_table <- as.data.frame(t(table(parent_all_acc2vs4_VIP_sig['Feature.status'])))

parent_all_acc2vs5_VIP_table <- as.data.frame(t(table(parent_all_acc2vs5_VIP_sig['Feature.status'])))


parent_all_acc3vs4_VIP_table <- as.data.frame(t(table(parent_all_acc3vs4_VIP_sig['Feature.status'])))

parent_all_acc3vs5_VIP_table <- as.data.frame(t(table(parent_all_acc3vs5_VIP_sig['Feature.status'])))

parent_all_acc4vs5_VIP_table <- as.data.frame(t(table(parent_all_acc4vs5_VIP_sig['Feature.status'])))


parent_all_acc1vs2_VIP_table$Comparison <- "acc1vs2"
parent_all_acc1vs3_VIP_table$Comparison <- "acc1vs3"
parent_all_acc1vs4_VIP_table$Comparison <- "acc1vs4"
parent_all_acc1vs5_VIP_table$Comparison <- "acc1vs5"

parent_all_acc2vs3_VIP_table$Comparison <- "acc2vs3"
parent_all_acc2vs4_VIP_table$Comparison <- "acc2vs4"
parent_all_acc2vs5_VIP_table$Comparison <- "acc2vs5"

parent_all_acc3vs4_VIP_table$Comparison <- "acc3vs4"
#parent_all_acc3vs5_VIP_table$Comparison <- "acc3vs5" #Error in `$<-.data.frame`(`*tmp*`, Comparison, value = "acc3vs5") : replacement has 1 row, data has 0

parent_all_acc4vs5_VIP_table$Comparison <- "acc4vs5"


feat.stat.table <- rbind(parent_all_acc1vs2_VIP_table, 
                         parent_all_acc1vs3_VIP_table, 
                         parent_all_acc1vs4_VIP_table, 
                         parent_all_acc1vs5_VIP_table, 
                         parent_all_acc2vs3_VIP_table, 
                         parent_all_acc2vs4_VIP_table, 
                         parent_all_acc2vs5_VIP_table, 
                         parent_all_acc3vs4_VIP_table, 
                         parent_all_acc4vs5_VIP_table)


feat.stat.table.acc <- feat.stat.table %>% spread(key = Var1, value = Freq)

feat.stat.table.acc

write.csv(feat.stat.table.acc, "output/feat.stat.table.acc.csv")
```

``` {r Knownstats gen, echo=TRUE, warning=FALSE, message=FALSE}
path2 <- "output/"

filenames <- list.files(path = path2, pattern="csv$") #figure out how to loop this

parent_all_AZvsBY_VIP_table <- as.data.frame(t(table(parent_all_AZvsBY_VIP_sig['Feature.status'])))

parent_all_AZvsCX_VIP_table <- as.data.frame(t(table(parent_all_AZvsCX_VIP_sig['Feature.status'])))

parent_all_AZvsDW_VIP_table <- as.data.frame(t(table(parent_all_AZvsDW_VIP_sig['Feature.status'])))

parent_all_AZvsEV_VIP_table <- as.data.frame(t(table(parent_all_AZvsEV_VIP_sig['Feature.status'])))

parent_all_AZvsFU_VIP_table <- as.data.frame(t(table(parent_all_AZvsFU_VIP_sig['Feature.status'])))

parent_all_AZvsGT_VIP_table <- as.data.frame(t(table(parent_all_AZvsGT_VIP_sig['Feature.status'])))

parent_all_AZvsHS_VIP_table <- as.data.frame(t(table(parent_all_AZvsHS_VIP_sig['Feature.status'])))

parent_all_AZvsIR_VIP_table <- as.data.frame(t(table(parent_all_AZvsIR_VIP_sig['Feature.status'])))

parent_all_AZvsJQ_VIP_table <- as.data.frame(t(table(parent_all_AZvsJQ_VIP_sig['Feature.status'])))


parent_all_BYvsCX_VIP_table <- as.data.frame(t(table(parent_all_BYvsCX_VIP_sig['Feature.status'])))

parent_all_BYvsDW_VIP_table <- as.data.frame(t(table(parent_all_BYvsDW_VIP_sig['Feature.status'])))

parent_all_BYvsEV_VIP_table <- as.data.frame(t(table(parent_all_BYvsEV_VIP_sig['Feature.status'])))

parent_all_BYvsFU_VIP_table <- as.data.frame(t(table(parent_all_BYvsFU_VIP_sig['Feature.status'])))

parent_all_BYvsGT_VIP_table <- as.data.frame(t(table(parent_all_BYvsGT_VIP_sig['Feature.status'])))

parent_all_BYvsHS_VIP_table <- as.data.frame(t(table(parent_all_BYvsHS_VIP_sig['Feature.status'])))

parent_all_BYvsIR_VIP_table <- as.data.frame(t(table(parent_all_BYvsIR_VIP_sig['Feature.status'])))

parent_all_BYvsJQ_VIP_table <- as.data.frame(t(table(parent_all_BYvsJQ_VIP_sig['Feature.status'])))


parent_all_CXvsDW_VIP_table <- as.data.frame(t(table(parent_all_CXvsDW_VIP_sig['Feature.status'])))

parent_all_CXvsEV_VIP_table <- as.data.frame(t(table(parent_all_CXvsEV_VIP_sig['Feature.status'])))

parent_all_CXvsFU_VIP_table <- as.data.frame(t(table(parent_all_CXvsFU_VIP_sig['Feature.status'])))

parent_all_CXvsGT_VIP_table <- as.data.frame(t(table(parent_all_CXvsGT_VIP_sig['Feature.status'])))

parent_all_CXvsHS_VIP_table <- as.data.frame(t(table(parent_all_CXvsHS_VIP_sig['Feature.status'])))

parent_all_CXvsIR_VIP_table <- as.data.frame(t(table(parent_all_CXvsIR_VIP_sig['Feature.status'])))

parent_all_CXvsJQ_VIP_table <- as.data.frame(t(table(parent_all_CXvsJQ_VIP_sig['Feature.status'])))


parent_all_DWvsEV_VIP_table <- as.data.frame(t(table(parent_all_DWvsEV_VIP_sig['Feature.status'])))

parent_all_DWvsFU_VIP_table <- as.data.frame(t(table(parent_all_DWvsFU_VIP_sig['Feature.status'])))

parent_all_DWvsGT_VIP_table <- as.data.frame(t(table(parent_all_DWvsGT_VIP_sig['Feature.status'])))

parent_all_DWvsHS_VIP_table <- as.data.frame(t(table(parent_all_DWvsHS_VIP_sig['Feature.status'])))

parent_all_DWvsIR_VIP_table <- as.data.frame(t(table(parent_all_DWvsIR_VIP_sig['Feature.status'])))

parent_all_DWvsJQ_VIP_table <- as.data.frame(t(table(parent_all_DWvsJQ_VIP_sig['Feature.status'])))


parent_all_EVvsFU_VIP_table <- as.data.frame(t(table(parent_all_EVvsFU_VIP_sig['Feature.status'])))

parent_all_EVvsGT_VIP_table <- as.data.frame(t(table(parent_all_EVvsGT_VIP_sig['Feature.status'])))

parent_all_EVvsHS_VIP_table <- as.data.frame(t(table(parent_all_EVvsHS_VIP_sig['Feature.status'])))

parent_all_EVvsIR_VIP_table <- as.data.frame(t(table(parent_all_EVvsIR_VIP_sig['Feature.status'])))

parent_all_EVvsJQ_VIP_table <- as.data.frame(t(table(parent_all_EVvsJQ_VIP_sig['Feature.status'])))


parent_all_FUvsGT_VIP_table <- as.data.frame(t(table(parent_all_FUvsGT_VIP_sig['Feature.status'])))

parent_all_FUvsHS_VIP_table <- as.data.frame(t(table(parent_all_FUvsHS_VIP_sig['Feature.status'])))

parent_all_FUvsIR_VIP_table <- as.data.frame(t(table(parent_all_FUvsIR_VIP_sig['Feature.status'])))

parent_all_FUvsJQ_VIP_table <- as.data.frame(t(table(parent_all_FUvsJQ_VIP_sig['Feature.status'])))


parent_all_GTvsHS_VIP_table <- as.data.frame(t(table(parent_all_GTvsHS_VIP_sig['Feature.status'])))

parent_all_GTvsIR_VIP_table <- as.data.frame(t(table(parent_all_GTvsIR_VIP_sig['Feature.status'])))

parent_all_GTvsJQ_VIP_table <- as.data.frame(t(table(parent_all_GTvsJQ_VIP_sig['Feature.status'])))


parent_all_HSvsIR_VIP_table <- as.data.frame(t(table(parent_all_HSvsIR_VIP_sig['Feature.status'])))

parent_all_HSvsJQ_VIP_table <- as.data.frame(t(table(parent_all_HSvsJQ_VIP_sig['Feature.status'])))


parent_all_IRvsJQ_VIP_table <- as.data.frame(t(table(parent_all_IRvsJQ_VIP_sig['Feature.status'])))


parent_all_AZvsBY_VIP_table$Comparison <- "AZvsBY"
#parent_all_AZvsCX_VIP_table$Comparison <- "AZvsCX"
#parent_all_AZvsDW_VIP_table$Comparison <- "AZvsDW"
#parent_all_AZvsEV_VIP_table$Comparison <- "AZvsEV"
#parent_all_AZvsFU_VIP_table$Comparison <- "AZvsFU"
#parent_all_AZvsGT_VIP_table$Comparison <- "AZvsGT"
#parent_all_AZvsHS_VIP_table$Comparison <- "AZvsHS"
#parent_all_AZvsIR_VIP_table$Comparison <- "AZvsIR"
#parent_all_AZvsJQ_VIP_table$Comparison <- "AZvsJQ"

parent_all_BYvsCX_VIP_table$Comparison <- "BYvsCX"
parent_all_BYvsDW_VIP_table$Comparison <- "BYvsDW"
parent_all_BYvsEV_VIP_table$Comparison <- "BYvsEV"
parent_all_BYvsFU_VIP_table$Comparison <- "BYvsFU"
#parent_all_BYvsGT_VIP_table$Comparison <- "BYvsGT"
#parent_all_BYvsHS_VIP_table$Comparison <- "BYvsHS"
#parent_all_BYvsIR_VIP_table$Comparison <- "BYvsIR"
parent_all_BYvsJQ_VIP_table$Comparison <- "BYvsJQ"

#parent_all_CXvsDW_VIP_table$Comparison <- "CXvsDW"
#parent_all_CXvsEV_VIP_table$Comparison <- "CXvsEV"
#parent_all_CXvsFU_VIP_table$Comparison <- "CXvsFU"
#parent_all_CXvsGT_VIP_table$Comparison <- "CXvsGT"
#parent_all_CXvsHS_VIP_table$Comparison <- "CXvsHS"
#parent_all_CXvsIR_VIP_table$Comparison <- "CXvsIR"
#parent_all_CXvsJQ_VIP_table$Comparison <- "CXvsJQ"

#parent_all_DWvsEV_VIP_table$Comparison <- "DWvsEV"
#parent_all_DWvsFU_VIP_table$Comparison <- "DWvsFU"
#parent_all_DWvsGT_VIP_table$Comparison <- "DWvsGT"
#parent_all_DWvsHS_VIP_table$Comparison <- "DWvsHS"
#parent_all_DWvsIR_VIP_table$Comparison <- "DWvsIR"
#parent_all_DWvsJQ_VIP_table$Comparison <- "DWvsJQ"

parent_all_EVvsFU_VIP_table$Comparison <- "EVvsFU"
#parent_all_EVvsGT_VIP_table$Comparison <- "EVvsGT"
#parent_all_EVvsHS_VIP_table$Comparison <- "EVvsHS"
parent_all_EVvsIR_VIP_table$Comparison <- "EVvsIR"
parent_all_EVvsJQ_VIP_table$Comparison <- "EVvsJQ"

#parent_all_FUvsGT_VIP_table$Comparison <- "FUvsGT"
#parent_all_FUvsHS_VIP_table$Comparison <- "FUvsHS"
parent_all_FUvsIR_VIP_table$Comparison <- "FUvsIR"
#parent_all_FUvsJQ_VIP_table$Comparison <- "FUvsJQ"

#parent_all_GTvsHS_VIP_table$Comparison <- "GTvsHS"
#parent_all_GTvsIR_VIP_table$Comparison <- "GTvsIR"
#parent_all_GTvsJQ_VIP_table$Comparison <- "GTvsJQ"

#parent_all_HSvsIR_VIP_table$Comparison <- "HSvsIR"
#parent_all_HSvsJQ_VIP_table$Comparison <- "HSvsJQ"

#parent_all_IRvsJQ_VIP_table$Comparison <- "IRvsJQ"


feat.stat.table2 <- rbind(parent_all_AZvsBY_VIP_table, 
                         parent_all_BYvsCX_VIP_table, 
                         parent_all_BYvsDW_VIP_table, 
                         parent_all_BYvsEV_VIP_table, 
                         parent_all_BYvsFU_VIP_table, 
                         parent_all_BYvsJQ_VIP_table, 
                         parent_all_EVvsFU_VIP_table, 
                         parent_all_EVvsIR_VIP_table, 
                         parent_all_EVvsJQ_VIP_table, 
                         parent_all_FUvsIR_VIP_table)

feat.stat.table.gen <- feat.stat.table2 %>% spread(key = Var1, value = Freq)

feat.stat.table.gen

write.csv(feat.stat.table.gen, "output/feat.stat.table.gen.csv")
```


### VIP plotting after t-test validation
                         
``` {r prepare VIP plot acc, echo=TRUE, warning=FALSE, message=FALSE}
# Attaching VIPs to t-test dataframes
parent_all_acc1vs2_VIP_sig2 <- merge(parent_all_acc1vs2_VIP_sig, parent_all_acc1vs2_VIP_1, by = "DirectParent")

parent_all_acc1vs3_VIP_sig2 <- merge(parent_all_acc1vs3_VIP_sig, parent_all_acc1vs3_VIP_1, by = "DirectParent")

parent_all_acc1vs4_VIP_sig2 <- merge(parent_all_acc1vs4_VIP_sig, parent_all_acc1vs4_VIP_1, by = "DirectParent")

parent_all_acc1vs5_VIP_sig2 <- merge(parent_all_acc1vs5_VIP_sig, parent_all_acc1vs5_VIP_1, by = "DirectParent")


parent_all_acc2vs3_VIP_sig2 <- merge(parent_all_acc2vs3_VIP_sig, parent_all_acc2vs3_VIP_1, by = "DirectParent")

parent_all_acc2vs4_VIP_sig2 <- merge(parent_all_acc2vs4_VIP_sig, parent_all_acc2vs4_VIP_1, by = "DirectParent")

parent_all_acc2vs5_VIP_sig2 <- merge(parent_all_acc2vs5_VIP_sig, parent_all_acc2vs5_VIP_1, by = "DirectParent")


parent_all_acc3vs4_VIP_sig2 <- merge(parent_all_acc3vs4_VIP_sig, parent_all_acc3vs4_VIP_1, by = "DirectParent")

parent_all_acc4vs5_VIP_sig2 <- merge(parent_all_acc4vs5_VIP_sig, parent_all_acc4vs5_VIP_1, by = "DirectParent")

```

```{r}
library(forcats)

#plot one comparison
plot_1vs3 <- parent_all_acc1vs3_VIP_sig2 %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) +
  #scale_colour_manual(values=c("#8B0046", "#468B00")) +
  #scale_fill_manual(values=c("#8B0046", "#468B00")) +
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_1vs3
```

```{r}
#plot one comparison
plot_4vs5 <- parent_all_acc4vs5_VIP_sig2 %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) +
  #scale_colour_manual(values=c("#8B0046", "#468B00")) +
  #scale_fill_manual(values=c("#8B0046", "#468B00")) +
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_4vs5
```

```{r combine VIP plot files}
parent_all_COMBO_sig2 <- rbind(parent_all_acc1vs2_VIP_sig2, parent_all_acc1vs3_VIP_sig2, parent_all_acc1vs4_VIP_sig2, parent_all_acc1vs5_VIP_sig2, parent_all_acc2vs3_VIP_sig2, parent_all_acc2vs4_VIP_sig2, parent_all_acc2vs5_VIP_sig2, parent_all_acc3vs4_VIP_sig2, parent_all_acc4vs5_VIP_sig2)
```

```{r}
plot_COMBO <- parent_all_COMBO_sig2 %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) + 
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_COMBO
```

```{r}
#filter only repeated metabolites 
#parent_all_COMBO_sig3 <- parent_all_COMBO_sig2 %>% group_by(DirectParent) %>% filter(n()>1)

parent_all_COMBO_sig3 <- parent_all_COMBO_sig2 %>% group_by(DirectParent, Enrichment.dir) %>% summarise_at(vars("VIP"), mean)

parent_all_COMBO_sig3 <- parent_all_COMBO_sig3 %>% group_by(DirectParent) %>% 
  arrange(VIP) %>% 
  mutate(order = row_number())
```

```{r}
plot_COMBO2 <- parent_all_COMBO_sig3 %>% ungroup() %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP, .fun = mean)) %>%
  ggplot(aes(x = VIP, y = DirectParent)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) + 
  ylab("") +
  xlab("VIP Score") +
  scale_color_discrete(name = "Days in \nAcclimation \nCage", labels=c('126 Days', '112 Days', '38 Days', '24 Days', '0 Days')) +
  theme_bw()

plot_COMBO2
```




``` {r prepare VIP plot gen, echo=TRUE, warning=FALSE, message=FALSE}
# Attaching VIPs to t-test dataframes
parent_all_AZvsBY_VIP_sig2 <- merge(parent_all_AZvsBY_VIP_sig, parent_all_AZvsBY_VIP_1, by = "DirectParent")
parent_all_AZvsCX_VIP_sig2 <- merge(parent_all_AZvsCX_VIP_sig, parent_all_AZvsCX_VIP_1, by = "DirectParent")
parent_all_AZvsDW_VIP_sig2 <- merge(parent_all_AZvsDW_VIP_sig, parent_all_AZvsDW_VIP_1, by = "DirectParent")
parent_all_AZvsEV_VIP_sig2 <- merge(parent_all_AZvsEV_VIP_sig, parent_all_AZvsEV_VIP_1, by = "DirectParent")
parent_all_AZvsFU_VIP_sig2 <- merge(parent_all_AZvsFU_VIP_sig, parent_all_AZvsFU_VIP_1, by = "DirectParent")
parent_all_AZvsGT_VIP_sig2 <- merge(parent_all_AZvsGT_VIP_sig, parent_all_AZvsGT_VIP_1, by = "DirectParent")
parent_all_AZvsHS_VIP_sig2 <- merge(parent_all_AZvsHS_VIP_sig, parent_all_AZvsHS_VIP_1, by = "DirectParent")
parent_all_AZvsIR_VIP_sig2 <- merge(parent_all_AZvsIR_VIP_sig, parent_all_AZvsIR_VIP_1, by = "DirectParent")
parent_all_AZvsJQ_VIP_sig2 <- merge(parent_all_AZvsJQ_VIP_sig, parent_all_AZvsJQ_VIP_1, by = "DirectParent")

parent_all_BYvsCX_VIP_sig2 <- merge(parent_all_BYvsCX_VIP_sig, parent_all_BYvsCX_VIP_1, by = "DirectParent")
parent_all_BYvsDW_VIP_sig2 <- merge(parent_all_BYvsDW_VIP_sig, parent_all_BYvsDW_VIP_1, by = "DirectParent")
parent_all_BYvsEV_VIP_sig2 <- merge(parent_all_BYvsEV_VIP_sig, parent_all_BYvsEV_VIP_1, by = "DirectParent")
parent_all_BYvsFU_VIP_sig2 <- merge(parent_all_BYvsFU_VIP_sig, parent_all_BYvsFU_VIP_1, by = "DirectParent")
parent_all_BYvsGT_VIP_sig2 <- merge(parent_all_BYvsGT_VIP_sig, parent_all_BYvsGT_VIP_1, by = "DirectParent")
parent_all_BYvsHS_VIP_sig2 <- merge(parent_all_BYvsHS_VIP_sig, parent_all_BYvsHS_VIP_1, by = "DirectParent")
parent_all_BYvsIR_VIP_sig2 <- merge(parent_all_BYvsIR_VIP_sig, parent_all_BYvsIR_VIP_1, by = "DirectParent")
parent_all_BYvsJQ_VIP_sig2 <- merge(parent_all_BYvsJQ_VIP_sig, parent_all_BYvsJQ_VIP_1, by = "DirectParent")

parent_all_CXvsDW_VIP_sig2 <- merge(parent_all_CXvsDW_VIP_sig, parent_all_CXvsDW_VIP_1, by = "DirectParent")
parent_all_CXvsEV_VIP_sig2 <- merge(parent_all_CXvsEV_VIP_sig, parent_all_CXvsEV_VIP_1, by = "DirectParent")
parent_all_CXvsFU_VIP_sig2 <- merge(parent_all_CXvsFU_VIP_sig, parent_all_CXvsFU_VIP_1, by = "DirectParent")
parent_all_CXvsGT_VIP_sig2 <- merge(parent_all_CXvsGT_VIP_sig, parent_all_CXvsGT_VIP_1, by = "DirectParent")
parent_all_CXvsHS_VIP_sig2 <- merge(parent_all_CXvsHS_VIP_sig, parent_all_CXvsHS_VIP_1, by = "DirectParent")
parent_all_CXvsIR_VIP_sig2 <- merge(parent_all_CXvsIR_VIP_sig, parent_all_CXvsIR_VIP_1, by = "DirectParent")
parent_all_CXvsJQ_VIP_sig2 <- merge(parent_all_CXvsJQ_VIP_sig, parent_all_CXvsJQ_VIP_1, by = "DirectParent")

parent_all_DWvsEV_VIP_sig2 <- merge(parent_all_DWvsEV_VIP_sig, parent_all_DWvsEV_VIP_1, by = "DirectParent")
parent_all_DWvsFU_VIP_sig2 <- merge(parent_all_DWvsFU_VIP_sig, parent_all_DWvsFU_VIP_1, by = "DirectParent")
parent_all_DWvsGT_VIP_sig2 <- merge(parent_all_DWvsGT_VIP_sig, parent_all_DWvsGT_VIP_1, by = "DirectParent")
parent_all_DWvsHS_VIP_sig2 <- merge(parent_all_DWvsHS_VIP_sig, parent_all_DWvsHS_VIP_1, by = "DirectParent")
parent_all_DWvsIR_VIP_sig2 <- merge(parent_all_DWvsIR_VIP_sig, parent_all_DWvsIR_VIP_1, by = "DirectParent")
parent_all_DWvsJQ_VIP_sig2 <- merge(parent_all_DWvsJQ_VIP_sig, parent_all_DWvsJQ_VIP_1, by = "DirectParent")

parent_all_EVvsFU_VIP_sig2 <- merge(parent_all_EVvsFU_VIP_sig, parent_all_EVvsFU_VIP_1, by = "DirectParent")
parent_all_EVvsGT_VIP_sig2 <- merge(parent_all_EVvsGT_VIP_sig, parent_all_EVvsGT_VIP_1, by = "DirectParent")
parent_all_EVvsHS_VIP_sig2 <- merge(parent_all_EVvsHS_VIP_sig, parent_all_EVvsHS_VIP_1, by = "DirectParent")
parent_all_EVvsIR_VIP_sig2 <- merge(parent_all_EVvsIR_VIP_sig, parent_all_EVvsIR_VIP_1, by = "DirectParent")
parent_all_EVvsJQ_VIP_sig2 <- merge(parent_all_EVvsJQ_VIP_sig, parent_all_EVvsJQ_VIP_1, by = "DirectParent")

parent_all_FUvsGT_VIP_sig2 <- merge(parent_all_FUvsGT_VIP_sig, parent_all_FUvsGT_VIP_1, by = "DirectParent")
parent_all_FUvsHS_VIP_sig2 <- merge(parent_all_FUvsHS_VIP_sig, parent_all_FUvsHS_VIP_1, by = "DirectParent")
parent_all_FUvsIR_VIP_sig2 <- merge(parent_all_FUvsIR_VIP_sig, parent_all_FUvsIR_VIP_1, by = "DirectParent")
parent_all_FUvsJQ_VIP_sig2 <- merge(parent_all_FUvsJQ_VIP_sig, parent_all_FUvsJQ_VIP_1, by = "DirectParent")

parent_all_GTvsHS_VIP_sig2 <- merge(parent_all_GTvsHS_VIP_sig, parent_all_GTvsHS_VIP_1, by = "DirectParent")
parent_all_GTvsIR_VIP_sig2 <- merge(parent_all_GTvsIR_VIP_sig, parent_all_GTvsIR_VIP_1, by = "DirectParent")
parent_all_GTvsJQ_VIP_sig2 <- merge(parent_all_GTvsJQ_VIP_sig, parent_all_GTvsJQ_VIP_1, by = "DirectParent")

parent_all_HSvsIR_VIP_sig2 <- merge(parent_all_HSvsIR_VIP_sig, parent_all_HSvsIR_VIP_1, by = "DirectParent")
parent_all_HSvsJQ_VIP_sig2 <- merge(parent_all_HSvsJQ_VIP_sig, parent_all_HSvsJQ_VIP_1, by = "DirectParent")

parent_all_IRvsJQ_VIP_sig2 <- merge(parent_all_IRvsJQ_VIP_sig, parent_all_IRvsJQ_VIP_1, by = "DirectParent")
```

```{r}
#plot one comparison
plot_BYvsCX <- parent_all_BYvsCX_VIP_sig2 %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) +
  #scale_colour_manual(values=c("#8B0046", "#468B00")) +
  #scale_fill_manual(values=c("#8B0046", "#468B00")) +
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_BYvsCX
```

```{r combine VIP plot files gen}
parent_allgen_COMBO_sig2 <- rbind(parent_all_AZvsBY_VIP_sig2,parent_all_AZvsCX_VIP_sig2,parent_all_AZvsDW_VIP_sig2,parent_all_AZvsEV_VIP_sig2,parent_all_AZvsFU_VIP_sig2,parent_all_AZvsGT_VIP_sig2,parent_all_AZvsHS_VIP_sig2,parent_all_AZvsIR_VIP_sig2,parent_all_AZvsJQ_VIP_sig2,parent_all_BYvsCX_VIP_sig2,parent_all_BYvsDW_VIP_sig2,parent_all_BYvsEV_VIP_sig2,parent_all_BYvsFU_VIP_sig2,parent_all_BYvsGT_VIP_sig2,parent_all_BYvsHS_VIP_sig2,parent_all_BYvsIR_VIP_sig2,parent_all_BYvsJQ_VIP_sig2,parent_all_CXvsDW_VIP_sig2,parent_all_CXvsEV_VIP_sig2,parent_all_CXvsFU_VIP_sig2,parent_all_CXvsGT_VIP_sig2,parent_all_CXvsHS_VIP_sig2,parent_all_CXvsIR_VIP_sig2,parent_all_CXvsJQ_VIP_sig2,parent_all_DWvsEV_VIP_sig2,parent_all_DWvsFU_VIP_sig2,parent_all_DWvsGT_VIP_sig2,parent_all_DWvsHS_VIP_sig2,parent_all_DWvsIR_VIP_sig2,parent_all_DWvsJQ_VIP_sig2,parent_all_EVvsFU_VIP_sig2,parent_all_EVvsGT_VIP_sig2,parent_all_EVvsHS_VIP_sig2,parent_all_EVvsIR_VIP_sig2,parent_all_EVvsJQ_VIP_sig2,parent_all_FUvsGT_VIP_sig2,parent_all_FUvsHS_VIP_sig2,parent_all_FUvsIR_VIP_sig2,parent_all_FUvsJQ_VIP_sig2,parent_all_GTvsHS_VIP_sig2,parent_all_GTvsIR_VIP_sig2,parent_all_GTvsJQ_VIP_sig2,parent_all_HSvsIR_VIP_sig2,parent_all_HSvsJQ_VIP_sig2,parent_all_IRvsJQ_VIP_sig2)
```

```{r}
plot_COMBO_gen <- parent_allgen_COMBO_sig2 %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP)) %>%
  ggplot(aes(x = VIP, y = DirectParent, fill = Enrichment.dir)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) + 
  ylab("") +
  xlab("VIP Score") +
  theme_bw()

plot_COMBO_gen
```

```{r}
#filter only repeated metabolites 
#parent_all_COMBO_sig3 <- parent_all_COMBO_sig2 %>% group_by(DirectParent) %>% filter(n()>1)

parent_allgen_COMBO_sig3 <- parent_allgen_COMBO_sig2 %>% group_by(DirectParent, Enrichment.dir) %>% summarise_at(vars("VIP"), mean)

parent_allgen_COMBO_sig3 <- parent_allgen_COMBO_sig3 %>% group_by(DirectParent) %>% 
  arrange(VIP) %>% 
  mutate(order = row_number())
```

```{r}
plot_COMBO_gen2 <- parent_allgen_COMBO_sig3 %>% ungroup() %>%
  mutate(DirectParent = fct_reorder(DirectParent, VIP, .fun = mean)) %>%
  ggplot(aes(x = VIP, y = DirectParent)) +
  geom_hline(aes(yintercept = DirectParent), linetype = "dotted", color = "grey") +
  geom_point(size = 3, aes(color = Enrichment.dir)) + 
  ylab("") +
  xlab("VIP Score") +
  scale_color_discrete(name = "Source \nColony") +
  theme_bw()

plot_COMBO_gen2
```