---
title: "wgcna"
output: html_document
date: '2022-07-11'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#code modified from Kevin as always 

```{r dependencies, warning=FALSE, message=FALSE}
#load packages
library("ggplot2")
library('vegan')
#install.packages("factoextra")
#library(factoextra)
library('ggfortify')
library('naniar')
library('cowplot')
library("BiocManager")
#BiocManager::install('mixOmics')
library("mixOmics")
library(tidyr)
library("RVAideMemoire")
library("VennDiagram")
library("broom")
library(janitor)
library(mdatools)
library(tibble)
#install.packages("hrbrthemes")
library(hrbrthemes)
library(gridExtra)
library(ggpubr)
```

```{r load packages, warning=FALSE, message=FALSE}
#install.packages("RSQLite")
library(RSQLite)
#BiocManager::install('genefilter')
library("genefilter")
#BiocManager::install('locfit')
library("locfit")
#BiocManager::install('DESeq2')
library("DESeq2")
library("RColorBrewer")
#BiocManager::install("GO.db")
library("GO.db")
#BiocManager::install("impute")
library("impute")
#BiocManager::install("preprocessCore")
library("preprocessCore")
#BiocManager::install("WGCNA")
library("WGCNA")
library("flashClust")
library("gridExtra")
#BiocManager::install("ComplexHeatmap")
library("ComplexHeatmap")
#BiocManager::install("goseq")
library("goseq")
library("dplyr")
#BiocManager::install("clusterProfiler")
library("clusterProfiler")
library("pheatmap")
library("magrittr")
library("reshape2")
```

#code from Kevin and https://bioinformaticsworkbook.org/tutorials/wgcna.html#gsc.tab=0

```{r prep data}
#prepare data with samples in columns and metabolites in rows
agg_all3 <- t(agg_all2)

#make first row column names (metabolites are already row names)
agg_all3 <- agg_all3 %>% row_to_names(row_number = 1)
#View(agg_all3)
```

## Data filtering: PoverA and genefilter

Conduct data filtering, this includes:  

*pOverA*: Specifying the minimum count for a proportion of samples for each metabolite. Here, we are using a pOverA of 0.0146. This is because we have 206 samples with a minimum of n=3 samples per group Therefore, we will accept genes that are present in 3/206 = 0.0146 of the samples because we expect different metabolites by groups as demonstrated by PLSDA analysis. We are further setting the minimum value of metabolites to 7 (median normalized), such that 4% of the samples must have a non-zero normalized metabolite presence in order for the metabolite to remain in the data set.  

Filter in the package "genefilter". Pre-filtering our dataset to reduce the memory size dataframe, increase the speed of the transformation and testing functions, and improve quality of statistical analysis by removing low-coverage counts. Removed counts could represent outliers in the data and removing these improves sensitivity of statistical tests.   

``` {r data filering, echo=TRUE, warning=FALSE, message=FALSE}
filt <- filterfun(pOverA(0.0146,0.07))

#create filter for the counts data
gfilt <- genefilter(agg_all3, filt)

#identify genes to keep by count filter
keep <- agg_all3[gfilt,]

#identify gene lists
n.keep <- rownames(keep)

#gene count data filtered in PoverA, P percent of the samples have counts over A
agg_all_filt <- as.data.frame(agg_all3[which(rownames(agg_all3) %in% n.keep),])

#How many rows do we have before and after filtering?
nrow(agg_all3) #Before
nrow(agg_all_filt) #After
#Filtering removed 12 metabolites, 332 metabolites are used in analysis.  
```


#Outlier detection
``` {r outlier detection, echo=TRUE, warning=FALSE, message=FALSE}
#Checking that all row and column names match. Should return "TRUE"
all(rownames(meta$ATTRIBUTE_sampleID) %in% colnames(agg_all_filt))
all(rownames(meta$ATTRIBUTE_sampleID) == colnames(agg_all_filt))
```

```{r metabolite outliers}
sampleTree = hclust(dist(agg_all_filt), method = "average");
# Plot the sample tree: Open a graphic output window of size 12 by 9 inches
# The user should change the dimensions if the window is too large or too small.

#pdf("/output/WGCNA/outliers_metabolites.pdf")
#pdf(file=paste0(path, "outliers_metabolites.pdf"))

plot(sampleTree, main = "Sample clustering to detect outliers", sub="", xlab="", cex.lab = 1.5, cex.axis = 1.5, cex.main = 2)
dev.off()

#no metabolite outliers
```

```{r sample outliers}
#Transpose such that samples are in rows and metabolites are in columns.
tagg_all_filt <- t(agg_all_filt)

#Look for outliers by examining tree of samples  
sampleTree = hclust(dist(tagg_all_filt), method = "average");

# Plot the sample tree: Open a graphic output window of size 12 by 9 inches
# The user should change the dimensions if the window is too large or too small.
#pdf("output/WGCNA/outliers_samples.pdf")

plot(sampleTree, main = "Sample clustering to detect outliers", sub="", xlab="", cex.lab = 1.5, cex.axis = 1.5, cex.main = 2)
dev.off()

#View(tagg_all_filt)
```

# 2. Network construction and consensus modlue detection
## Choosing a soft-thresholding power: Analysis of a network topology β
``` {r soft threshold, echo=TRUE, warning=FALSE, message=FALSE}
# Choose a set of soft-thresholding powers
#powers <- c(seq(from = 1, to=200, by=2), c(21:30)) #Create a string of numbers from 1 through 10, and even numbers from 10 through 20

allowWGCNAThreads() 
powers <- c(c(1:20), seq(from = 12, to=20, by=2)) #Create a string of numbers from 1 through 10, and even numbers from 10 through 20

# Call the network topology analysis function
sft <-pickSoftThreshold(tagg_all_filt, powerVector = powers, verbose = 5)

#Plot the results.  
sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
# # # Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
      xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
     main = paste("Scale independence"));
 text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     labels=powers,cex=cex1,col="red");
# # # this line corresponds to using an R^2 cut-off
 abline(h=0.8,col="red")
# # # Mean connectivity as a function of the soft-thresholding power
 plot(sft$fitIndices[,1], sft$fitIndices[,5],
     xlab="Soft Threshold (power)",ylab="Mean Connectivity", type="n",
     main = paste("Mean connectivity"))
 text(sft$fitIndices[,1], sft$fitIndices[,5], labels=powers, cex=cex1,col="red")

# Soft Threshold power is 11
```

```{r numeric}
#change dataframe to matrix
tagg_all_filt <- as.data.frame(tagg_all_filt)
tagg_all_filt <- tagg_all_filt %>% mutate( across( where(is.character), ~ as.numeric(.x) ) )
#View(tagg_all_filt)
```

```{r pick power}
picked_power = 11
temp_cor <- cor       
cor <- WGCNA::cor         # Force it to use WGCNA cor function (fix a namespace conflict issue)
netwk <- blockwiseModules(tagg_all_filt,                # <= input here

                          # == Adjacency Function ==
                          power = picked_power,                # <= power here
                          networkType = "signed",

                          # == Tree and Block Options ==
                          deepSplit = 2,
                          pamRespectsDendro = F,
                          # detectCutHeight = 0.75,
                          minModuleSize = 5,
                          maxBlockSize = 4000,

                          # == Module Adjustments ==
                          reassignThreshold = 0,
                          mergeCutHeight = 0.25,

                          # == TOM == Archive the run results in TOM file (saves time)
                          saveTOMs = T,
                          saveTOMFileBase = "ER",

                          # == Output Options
                          numericLabels = T,
                          verbose = 3)

cor <- temp_cor  #return cor function to original namespace 
```

```{r dendrogram}
# Convert labels to colors for plotting
mergedColors = labels2colors(netwk$colors)
# Plot the dendrogram and the module colors underneath
plotDendroAndColors(
  netwk$dendrograms[[1]],
  mergedColors[netwk$blockGenes[[1]]],
  "Module colors",
  dendroLabels = FALSE,
  hang = 0.03,
  addGuide = TRUE,
  guideHang = 0.05 )
```

#Relate module (cluster) assignments to treatment groups

```{r relate clusters}
module_df <- data.frame(
  metabolite = names(netwk$colors),
  colors = labels2colors(netwk$colors)
)

module_df[1:5,]
#>            metabolite                colors
#> 1	00056bcaf3eb04f1d988da98936bc1d5	turquoise		
#> 2	01678bcea2b58f4934ca047a3d8d6b97	turquoise		
#> 3	01bd3fe94455ce451ccbe6fc57069261	turquoise		
#> 4	031bc75c4d162ff7bc8bf302eb73565d	green		
#> 5	034640392fd761ca55a00036940c73c1	blue

#write.csv(module_df, "output/WGCNA/metabolite_modules.csv")
```

```{r calculate eigan}
#calcuate an Eigangene (or Eiganmetabolite) (hypothetical central metabolite) for each module

# Get Module Eigengenes per cluster
MEs <- moduleEigengenes(tagg_all_filt, mergedColors)$eigengenes

# Reorder modules so similar modules are next to each other
MEs <- orderMEs(MEs)
module_order = names(MEs) %>% gsub("ME","", .)

# Add Sample names
MEs0 <- MEs
MEs0$Coral.ID = row.names(MEs)

# tidy & plot data
mME = MEs0 %>%
  pivot_longer(-Coral.ID) %>%
  mutate(
    name = gsub("ME", "", name),
    name = factor(name, levels = module_order)
  )

mME %>% ggplot(., aes(x=Coral.ID, y=name, fill=value)) +
  geom_tile() +
  theme_bw() +
  scale_fill_gradient2(
    low = "blue",
    high = "red",
    mid = "white",
    midpoint = 0,
    limit = c(-1,1)) +
  theme(axis.text.x = element_text(angle=90)) +
  labs(title = "Module-trait Relationships", y = "Modules", fill="corr")

```


## Relate Module (cluster) Assignments to Groupings: ACCLIMATION

Prepare trait data. Data has to be numeric, so I will substitute acclimation treatment/genotype for numeric values. The "trait" we are considering here is Grouping  

Make a dataframe that has a column for each attribute name and a row for samples. Populate a 1 for samples that match each Group and a 0 for samples not matching respective Groups 

This process changes Groups from a categorical variable into a binary variable. This will allow for correlations between mean eigengenes and Groups  

```{r prep grouping data ACC}
meta3 <- meta2[,c(2,3,4,11)]
#View(meta3)

meta3$num <- c("1")
allACC <- as.data.frame(tidyr::pivot_wider(meta3, names_from = ATTRIBUTE_acclimation, values_from = num, id_cols = ATTRIBUTE_sampleID))
allACC[is.na(allACC)] <- c("0")
rownames(allACC) <- allACC$ATTRIBUTE_sampleID
datACC <- allACC[c(1:207),c(2:6)] #remove blanks and "NA" acclimation
head(datACC)
```

```{r define numbers}
# Define numbers of genes and samples and print. 
nMetabolites = ncol(tagg_all_filt)
nSamples = nrow(tagg_all_filt)
nMetabolites #332
nSamples #206
```

```{r dendrogram ACC}
#get rid of OBY3 sample as it was filtered out during previous analysis 
datACC2 <- datACC[c(-3),]

# Correlations of traits with eigengenes
moduleAccCor = cor(MEs, datACC2, use = "p");
moduleAccPvalue = corPvalueStudent(moduleAccCor, nSamples);
Colors=sub("ME","", names(MEs))
moduleAccTree = hclust(dist(t(moduleAccCor)), method = "average")
#pdf(file="output/WGCNA/ModuleAccClusterTree.pdf", height=8, width=22)
plot(moduleAccTree)
dev.off()

# Correlations of metabolites with eigengenes. Calculate correlations between ME's and groups 
moduleGeneCor=cor(MEs,tagg_all_filt)
moduleGenePvalue = corPvalueStudent(moduleGeneCor, nSamples);
#head(moduleGenePvalue)
```

```{r kME values}
#Calculate kME values (module membership). 
#datKME = signedKME(tagg_all_filt, MEs0, outputColumnName = "kME")
#head(datKME)

#Save module colors and labels for use in subsequent analyses.  
#save(MEs, moduleLabels, moduleColors, geneTree, file = "output/WGCNA/NetworkConstructionWGCNA.RData") 
```

## Plot module-trait associations: ACCLIMATION

Represent module trait correlations as a heatmap 
```{r, echo=TRUE, warning=FALSE, message=FALSE}
textMatrix = paste(signif(moduleAccCor, 2), "\n(",signif(moduleAccPvalue, 1), ")", sep = "")
dim(textMatrix) = dim(moduleAccCor)
head(textMatrix)

labeledHeatmap(Matrix = moduleAccCor, xLabels = names(datACC2),  yLabels = names(MEs), ySymbols = names(MEs), cex.lab.y= 0.55, cex.lab.x= 0.55, colors = blueWhiteRed(50), textMatrix = textMatrix, setStdMargins = TRUE, cex.text = 0.25, textAdj = , zlim = c(-1,1), main = paste("Module-trait relationships"))

#pdf("Users/cassieraker/Documents/_URI/_Research/Data/2019_PR_ch3_chemicalecology/2021_UTAustin_data/output/WGCNA/Module_trait_relationships.pdf")

labeledHeatmap(Matrix = moduleAccCor, xLabels = names(datACC2),  yLabels = names(MEs), ySymbols = names(MEs), cex.lab.y= 0.55, cex.lab.x= 0.55, colors = blueWhiteRed(50), textMatrix = textMatrix, setStdMargins = TRUE, cex.text = 0.25, textAdj = , zlim = c(-1,1), main = paste("Module-trait relationships"))
dev.off()
```

# Generate a complex heatmap of module-trait relationships.  

```{r acc heatmap, echo=TRUE, warning=FALSE, message=FALSE}
#bold sig p-values
#dendrogram with WGCNA MEtree cut-off
#colored y-axis
#Create list of pvalues for eigengene correlation with specific life stages
heatmappval <- signif(moduleAccPvalue, 1)
#Make list of heatmap row colors
htmap.colors <- names(MEs)
htmap.colors <- gsub("ME", "", htmap.colors)
library(dendsort)
row_dend = dendsort(hclust(dist(moduleAccCor)))
col_dend = dendsort(hclust(dist(t(moduleAccCor))))

pdf(file="Module-trait-relationship-heatmap.pdf", height = 8, width = 8)

ht=Heatmap(moduleAccCor, name = "Eigengene", column_title = "Module-Group Eigengene Correlation", 
        col = blueWhiteRed(50), 
        row_names_side = "left", 
        row_dend_side = "left",
        width = unit(4, "in"), 
        height = unit(3.5, "in"), 
        column_dend_reorder = TRUE, 
        cluster_columns = col_dend,
        row_dend_reorder = FALSE,
        column_split = 6, 
        column_dend_height = unit(.5, "in"),
        column_names_rot = 45,
        column_labels = c("38 days", "24 Days", "0 Days", "112 Days", "126 Days"),
        cluster_rows = row_dend, 
        row_gap = unit(2.5, "mm"), 
        border = TRUE,
        cell_fun = function(j, i, x, y, w, h, col) {
        if(heatmappval[i, j] < 0.05) {
            grid.text(sprintf("%s", heatmappval[i, j]), x, y, gp = gpar(fontsize = 10, fontface = "bold"))
        }
        else {
            grid.text(sprintf("%s", heatmappval[i, j]), x, y, gp = gpar(fontsize = 10, fontface = "plain"))
        }},
        column_names_gp =  gpar(fontsize = 12, border=FALSE),
        row_names_gp = gpar(fontsize = 12, alpha = 0.75, border = FALSE))
ht
#dev.off()
```


# Plot mean eigengene values for each module

```{r, echo=TRUE, warning=FALSE, message=FALSE}
# Number of each metabolites in each module 
row_mod_num <- data.frame(table(module_df$colors))

# Bring in additional metadata
sample_metadata <- meta2 %>% select(ATTRIBUTE_sampleID, ATTRIBUTE_acclimation, ATTRIBUTE_genotype)
sample_metadata$Coral.ID <- as.factor(sample_metadata$ATTRIBUTE_sampleID)
sample_metadata$ATTRIBUTE_acclimation <- as.factor(sample_metadata$ATTRIBUTE_acclimation)
sample_metadata$ATTRIBUTE_genotype <- as.factor(sample_metadata$ATTRIBUTE_genotype)

mME_meta <- merge(mME, sample_metadata, by = "Coral.ID") %>%
  rename(Module = name)
mME_meta$Module <- factor(mME_meta$Module, levels = c("brown", "turquoise", "blue", "yellow", "red", "green", "grey"))
module_order <- c("brown", "turquoise", "blue", "yellow", "red", "green", "grey")
mME_meta2 <- mME_meta %>% arrange(match(Module, module_order))

expression_plots<-mME_meta%>%
#  group_by(Module) %>%
  ggplot(aes(x=ATTRIBUTE_acclimation, y=value, fill=ATTRIBUTE_acclimation)) +
  facet_grid(Module ~.)+
  ylab("Mean Module Eigenegene Value") +
  geom_hline(yintercept = 0, linetype="dashed", color = "grey")+
  geom_boxplot(width=.5, outlier.shape= NA, position = position_dodge(width = 0.5), alpha = 0.7) +
  stat_summary(fun=mean, geom="line", aes(group=ATTRIBUTE_acclimation, color = ATTRIBUTE_acclimation), position = position_dodge(width = 0.5))  + 
  geom_point(pch = 21, position = position_dodge(width = 0.5)) +
  #scale_fill_manual(values=c("#CC3300", "#46008B", "#468B00")) +
  #scale_color_manual(values=c("#CC3300", "#46008B", "#468B00")) + 
  #scale_x_discrete(labels=c("0" = "Day 0", "37" = "Day 37", "52" = "Day 52")) +
  xlab("Acclimation") + #Axis titles
  theme_bw() + theme(panel.border = element_rect(color="black", fill=NA, size=0.75), panel.grid.major = element_blank(), #Makes background theme white
                     panel.grid.minor = element_blank(), axis.line = element_blank()) +
  theme(legend.position = "none")
  theme(axis.text = element_text(size = 8, color = "black"),
        axis.title = element_text(size = 12, color = "black")); expression_plots

#ggsave(filename="output/WGCNA/expression_eigengene.jpeg", plot=expression_plots, dpi=300, width=7, height=10, units="in")
```

## Relate Module (cluster) Assignments to Groupings: GENOTYPE

```{r prep grouping data GEN}
meta3 <- meta2[,c(2,3,4,11)]

meta3$num <- c("1")
meta3 <- meta3[c(1:207),] #remove blank samples
allGEN <- as.data.frame(pivot_wider(meta3, names_from = ATTRIBUTE_genotype, values_from = num, id_cols = ATTRIBUTE_sampleID))
allGEN[is.na(allGEN)] <- c("0")
rownames(allGEN) <- allGEN$ATTRIBUTE_sampleID
datGEN <- allGEN[c(1:207),c(2:11)] #remove blanks and "NA" acclimation
head(datGEN)
```

```{r define numbers}
# Define numbers of genes and samples and print. 
nMetabolites = ncol(tagg_all_filt)
nSamples = nrow(tagg_all_filt)
nMetabolites #332
nSamples #206
```

```{r dendrogram GEN}
#get rid of OBY3 sample as it was filtered out during previous analysis 
datGEN2 <- datGEN[c(-3),]

# Correlations of traits with eigengenes
moduleGenCor = cor(MEs, datGEN2, use = "p");
moduleGenPvalue = corPvalueStudent(moduleGenCor, nSamples);
Colors=sub("ME","", names(MEs))
moduleGenTree = hclust(dist(t(moduleGenCor)), method = "average")
#pdf(file="output/WGCNA/ModuleAccClusterTreeGen.pdf", height=8, width=22)
plot(moduleGenTree)
dev.off()

# Correlations of metabolites with eigengenes. Calculate correlations between ME's and groups 
moduleGeneCor=cor(MEs,tagg_all_filt)
moduleGenePvalue = corPvalueStudent(moduleGeneCor, nSamples);
#head(moduleGenePvalue)
```

```{r kME values}
#Calculate kME values (module membership). 
#datKME = signedKME(tagg_all_filt, MEs0, outputColumnName = "kME")
#head(datKME)

#Save module colors and labels for use in subsequent analyses.  
#save(MEs, moduleLabels, moduleColors, geneTree, file = "output/WGCNA/NetworkConstructionWGCNA.RData") 
```

## Plot module-trait associations: GENOTYPE

Represent module trait correlations as a heatmap 
```{r heatmap GEN, echo=TRUE, warning=FALSE, message=FALSE}
textMatrix = paste(signif(moduleGenCor, 2), "\n(",signif(moduleGenPvalue, 1), ")", sep = "")
dim(textMatrix) = dim(moduleGenCor)
head(textMatrix)

labeledHeatmap(Matrix = moduleGenCor, xLabels = names(datGEN2),  yLabels = names(MEs), ySymbols = names(MEs), cex.lab.y= 0.55, cex.lab.x= 0.55, colors = blueWhiteRed(50), textMatrix = textMatrix, setStdMargins = TRUE, cex.text = 0.25, textAdj = , zlim = c(-1,1), main = paste("Module-trait relationships GEN"))

#pdf("output/WGCNA/Module_trait_relationships_gen.pdf")

labeledHeatmap(Matrix = moduleGenCor, xLabels = names(datGEN2),  yLabels = names(MEs), ySymbols = names(MEs), cex.lab.y= 0.55, cex.lab.x= 0.55, colors = blueWhiteRed(50), textMatrix = textMatrix, setStdMargins = TRUE, cex.text = 0.45, textAdj = , zlim = c(-1,1), main = paste("Module-trait relationships GEN"))
dev.off()
```

# Generate a complex heatmap of module-trait relationships.  

```{r gen heatmap, echo=TRUE, warning=FALSE, message=FALSE}
#bold sig p-values
#dendrogram with WGCNA MEtree cut-off
#colored y-axis
#Create list of pvalues for eigengene correlation with specific life stages
heatmappval_gen <- signif(moduleGenPvalue, 1)
#Make list of heatmap row colors
htmap.colors <- names(MEs)
htmap.colors <- gsub("ME", "", htmap.colors)
library(dendsort)
row_dend = dendsort(hclust(dist(moduleGenCor)))
col_dend = dendsort(hclust(dist(t(moduleGenCor))))

pdf(file="Raker_SciReports_figS5.pdf", height = 8, width = 8)

ht_gen=Heatmap(moduleGenCor, name = "Eigengene", column_title = "Module-Group Eigengene Correlation", 
        col = blueWhiteRed(50), 
        row_names_side = "left", 
        row_dend_side = "left",
        width = unit(4, "in"), 
        height = unit(3.5, "in"), 
        column_dend_reorder = TRUE, 
        cluster_columns = col_dend,
        row_dend_reorder = FALSE,
        column_split = 6, 
        column_dend_height = unit(.5, "in"),
        column_names_rot = 30,
        cluster_rows = row_dend, 
        row_gap = unit(2.5, "mm"), 
        border = TRUE,
        cell_fun = function(j, i, x, y, w, h, col) {
        if(heatmappval_gen[i, j] < 0.05) {
            grid.text(sprintf("%s", heatmappval_gen[i, j]), x, y, gp = gpar(fontsize = 10, fontface = "bold"))
        }
        else {
            grid.text(sprintf("%s", heatmappval_gen[i, j]), x, y, gp = gpar(fontsize = 10, fontface = "plain"))
        }},
        column_names_gp =  gpar(fontsize = 12, border=FALSE),
        row_names_gp = gpar(fontsize = 12, alpha = 0.75, border = FALSE))
ht_gen
#dev.off()
```

# Plot mean eigengene values for each module

```{r, echo=TRUE, warning=FALSE, message=FALSE}
# Number of each metabolites in each module 
row_mod_num <- data.frame(table(module_df$colors))

# Bring in additional metadata
sample_metadata <- meta2 %>% select(ATTRIBUTE_sampleID, ATTRIBUTE_acclimation, ATTRIBUTE_genotype)
sample_metadata$Coral.ID <- as.factor(sample_metadata$ATTRIBUTE_sampleID)
sample_metadata$ATTRIBUTE_acclimation <- as.factor(sample_metadata$ATTRIBUTE_acclimation)
sample_metadata$ATTRIBUTE_genotype <- as.factor(sample_metadata$ATTRIBUTE_genotype)

mME_meta <- merge(mME, sample_metadata, by = "Coral.ID") %>%
  rename(Module = name)
mME_meta$Module <- factor(mME_meta$Module, levels = c("brown", "turquoise", "blue", "yellow", "red", "green", "grey"))
module_order <- c("brown", "turquoise", "blue", "yellow", "red", "green", "grey")
mME_meta2 <- mME_meta %>% arrange(match(Module, module_order))

expression_plots<-mME_meta%>%
#  group_by(Module) %>%
  ggplot(aes(x=ATTRIBUTE_genotype, y=value, fill=ATTRIBUTE_genotype)) +
  facet_grid(Module ~.)+
  ylab("Mean Module Eigenegene Value") +
  geom_hline(yintercept = 0, linetype="dashed", color = "grey")+
  geom_boxplot(width=.5, outlier.shape= NA, position = position_dodge(width = 0.5), alpha = 0.7) +
  stat_summary(fun=mean, geom="line", aes(group=ATTRIBUTE_genotype, color = ATTRIBUTE_genotype), position = position_dodge(width = 0.5))  + 
  geom_point(pch = 21, position = position_dodge(width = 0.5)) +
  #scale_fill_manual(values=c("#CC3300", "#46008B", "#468B00")) +
  #scale_color_manual(values=c("#CC3300", "#46008B", "#468B00")) + 
  #scale_x_discrete(labels=c("0" = "Day 0", "37" = "Day 37", "52" = "Day 52")) +
  xlab("Genotype") + #Axis titles
  theme_bw() + theme(panel.border = element_rect(color="black", fill=NA, size=0.75), panel.grid.major = element_blank(), #Makes background theme white
                     panel.grid.minor = element_blank(), axis.line = element_blank()) +
  theme(legend.position = "none")
  theme(axis.text = element_text(size = 8, color = "black"),
        axis.title = element_text(size = 12, color = "black")); expression_plots

#ggsave(filename="output/WGCNA/expression_eigengene.jpeg", plot=expression_plots, dpi=300, width=7, height=10, units="in")
```
# Pathway Analysis for each module

```{r select metabolites, echo=TRUE, warning=FALSE, message=FALSE}
module_df <- read.csv("./output/WGCNA/metabolite_modules.csv")
module_df <- module_df %>% rename(Module = colors)

# Select metabolites for each module 
#brown (n=15), turquoise (n=221), blue (n=45), yellow (n=12), red (n=9), green (n=11), grey (n=19)
module_brown <- module_df %>% filter(Module == "brown")  %>% select(metabolite)
module_turquoise <- module_df %>% filter(Module == "turquoise")  %>% select(metabolite)
module_blue <- module_df %>% filter(Module == "blue")  %>% select(metabolite)
module_yellow <- module_df %>% filter(Module == "yellow")  %>% select(metabolite)
module_red <- module_df %>% filter(Module == "red")  %>% select(metabolite)
module_green <- module_df %>% filter(Module == "green")  %>% select(metabolite)
module_grey <- module_df %>% filter(Module == "grey")  %>% select(metabolite)
```

#select out modules
```{r select modules}
#use dplyr
modbrown <- siri.heat %>%
      filter(id %in% module_brown$metabolite)

modturquoise <- siri.heat %>%
      filter(id %in% module_turquoise$metabolite)

modblue <- siri.heat %>%
      filter(id %in% module_blue$metabolite)

modyellow <- siri.heat %>%
      filter(id %in% module_yellow$metabolite)

modred <- siri.heat %>%
      filter(id %in% module_red$metabolite)

modgreen <- siri.heat %>%
      filter(id %in% module_green$metabolite)

modgrey <- siri.heat %>%
      filter(id %in% module_grey$metabolite)
```

```{r write csv for MetaboAnalystR website}
write.csv(modbrown, "modbrown.csv")
write.csv(modturquoise, "modturquoise.csv")
write.csv(modblue, "modblue.csv")
write.csv(modyellow, "modyellow.csv")
write.csv(modred, "modred.csv")
write.csv(modgreen, "modgreen.csv")
write.csv(modgrey, "modgrey.csv")
```

## Linear regressions for modules

```{r add metada to eigenvalues}
#turn coral ID into row names
#meta2 <- data.frame(meta2, row.names = 2)

#add new column to metadata that treats acclimation time as a numeric variable (i.e. # of days)
meta2$acclimation2 <- case_when(meta2$ATTRIBUTE_acclimation == 1 ~ 126, 
                               meta2$ATTRIBUTE_acclimation == 2 ~ 112,
                               meta2$ATTRIBUTE_acclimation == 3 ~ 38,
                               meta2$ATTRIBUTE_acclimation == 4 ~ 24,
                               meta2$ATTRIBUTE_acclimation == 5 ~ 0,)
meta2$acclimation2 <- as.numeric(meta2$acclimation2)

#merge with eigenvalues
eigen <- merge(MEs, meta2, by=0)
#View(eigen)
```

## Plot
```{r individual modules}
brown <- ggplot(eigen, aes(x=acclimation2, y=MEbrown)) +
  #geom_point() +
  geom_smooth(method=lm, color="red", fill="#69b3a2", se=TRUE) +
  stat_cor(label.x = 15, label.y = -0.02) +
  theme_bw() +
  ylab("Brown Module") +
  xlab("Acclimation Time")
brown

turquoise <- ggplot(eigen, aes(x=acclimation2, y=MEturquoise)) +
  geom_point() +
  geom_smooth(method=lm, color="red", fill="#69b3a2", se=TRUE) +
  stat_cor(label.x = 50, label.y = 0.1) +
  theme_bw() +
  ylab("Turquoise Module") +
  xlab("Acclimation Time")
turquoise

blue <- ggplot(eigen, aes(x=acclimation2, y=MEblue)) +
  #geom_point() +
  geom_smooth(method=lm, color="red", fill="#69b3a2", se=TRUE) +
  stat_cor(label.x = 15, label.y = -0.02) +
  theme_bw() +
  ylab("Blue Module") +
  xlab("Acclimation Time")
blue

yellow <- ggplot(eigen, aes(x=acclimation2, y=MEyellow)) +
  geom_point() +
  geom_smooth(method=lm, color="red", fill="#69b3a2", se=TRUE) +
  stat_cor(label.x = 50, label.y = -0.05) +
  theme_bw() +
  ylab("Yellow Module") +
  xlab("Acclimation Time")
yellow

red <- ggplot(eigen, aes(x=acclimation2, y=MEred)) +
  #geom_point() +
  geom_smooth(method=lm, color="red", fill="#69b3a2", se=TRUE) +
  stat_cor(label.x = 15, label.y = -0.02) +
  theme_bw() +
  ylab("Red Module") +
  xlab("Acclimation Time")
red

green <- ggplot(eigen, aes(x=acclimation2, y=MEgreen)) +
  geom_point() +
  geom_smooth(method=lm, color="red", fill="#69b3a2", se=TRUE) +
  stat_cor(label.x = 50, label.y = -0.1) +
  theme_bw() +
  ylab("Green Module") +
  xlab("Acclimation Time")
green

grey <- ggplot(eigen, aes(x=acclimation2, y=MEgrey)) +
  geom_point() +
  geom_smooth(method=lm, color="red", fill="#69b3a2", se=TRUE) +
  stat_cor(label.x = 50, label.y = -0.12) +
  theme_bw() +
  ylab("Grey Module") +
  xlab("Acclimation Time")
grey
```

```{r combine plots}
lr_all <- grid.arrange(grey, green, turquoise, yellow, nrow = 2)
lr_all
```


## WGCNA with each variable as a column
## following Carlos's DAPC_tagseq_transplant code 

```{r data from ch1}
#load survivorship data
surv_all <- read.csv("survivorship_all.csv", header = TRUE, check.names = FALSE)

#load growth data 
growth <- read.csv("growth.csv", header = TRUE, check.names = FALSE)

#load predation data
pred <- read.csv("predation.csv", header = TRUE, check.names = FALSE)

#merge ch1 data
ch1 <- merge(surv_all, growth)
ch1 <- merge(ch1, pred)

#get rid of any row with NAs
ch1 <- na.omit(ch1)

#add new column to survivorship data that treats acclimation time as a numeric variable (i.e. # of days)
ch1$acclimation2 <- case_when(ch1$acclimation == 1 ~ 126, 
                               ch1$acclimation == 2 ~ 112,
                               ch1$acclimation == 3 ~ 38,
                               ch1$acclimation == 4 ~ 24,
                               ch1$acclimation == 5 ~ 0,)
ch1$acclimation2 <- as.numeric(ch1$acclimation2)
#View(ch1)

#merge with eigen_all
eigen_all <- merge(eigen, ch1, all = TRUE)
#View(eigen_all)
```

```{r prep data}
traits <- eigen_all[,c(1,22,23,25)] #select traits that you want
#View(traits)
ME2 <- eigen_all[,c(3:9)]
```

```{r correlations}
#correlations of traits with eigengenes
moduleTraitCor = cor(ME2, traits, use = "p");
moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples);
Colors=sub("ME2","",names(ME2))

#correlations of genes with eigengenes
moduleGeneCor=cor(ME2,traits, use = 'pairwise.complete.obs') #allows for NAs
moduleGenePvalue = corPvalueStudent(moduleGeneCor, nSamples)
```

```{r heatmap}
quartz()
#represent module trait correlations as a heatmap
sizeGrWindow(10,6)
# Will display correlations and their p-values
textMatrix = paste(signif(moduleTraitCor, 2), "\n(",
                        signif(moduleTraitPvalue, 1), ")", sep = "");
dim(textMatrix) = dim(moduleTraitCor)
par(mar = c(6, 8.5, 3, 3));
# Display the correlation values within a heatmap plot
heat1<- labeledHeatmap(Matrix = moduleTraitCor,
             xLabels = names(traits),
             yLabels = names(ME2),
             ySymbols = names(ME2),
             colorLabels = FALSE,
             colors = colorRampPalette(c("blue","lightblue","white","coral","red"))(50),
             textMatrix = textMatrix,
             setStdMargins = FALSE,
             cex.text = 0.5,
             zlim = c(-1,1),
             main = paste("Module-trait relationships"))
heat1
```

```{r acc and betaine heatmap, echo=TRUE, warning=FALSE, message=FALSE}
#bold sig p-values
#dendrogram with WGCNA MEtree cut-off
#colored y-axis
#Create list of pvalues for eigengene correlation with specific life stages
heatmappval <- signif(moduleTraitPvalue, 1)
#Make list of heatmap row colors
htmap.colors <- names(ME2)
htmap.colors <- gsub("ME", "", htmap.colors)
library(dendsort)
row_dend = dendsort(hclust(dist(moduleTraitCor)))
col_dend = dendsort(hclust(dist(t(moduleTraitCor))))

pdf(file="Raker_SciReports_fig4.pdf", height = 8, width = 8)

heat2=Heatmap(moduleTraitCor, name = "Eigengene", column_title = "Module-Group Eigengene Correlation", 
        col = blueWhiteRed(50), 
        row_names_side = "left", 
        row_dend_side = "right",
        width = unit(4, "in"), 
        height = unit(3.5, "in"), 
        column_dend_reorder = TRUE, 
        cluster_columns = col_dend,
        column_names_rot = 45,
        column_labels = c("Acclimation time", "Survivorship", "Growth", "Predation"),
        row_dend_reorder = FALSE,
        column_split = 6, 
        column_dend_height = unit(.5, "in"),
        cluster_rows = row_dend, 
        row_gap = unit(2.5, "mm"), 
        border = TRUE,
        cell_fun = function(j, i, x, y, w, h, col) {
        if(heatmappval[i, j] < 0.05) {
            grid.text(sprintf("%s", heatmappval[i, j]), x, y, gp = gpar(fontsize = 8, fontface = "bold"))
        }
        else {
            grid.text(sprintf("%s", heatmappval[i, j]), x, y, gp = gpar(fontsize = 8, fontface = "plain"))
        }},
        column_names_gp =  gpar(fontsize = 12, border=FALSE),
        row_names_gp = gpar(fontsize = 12, alpha = 0.75, border = FALSE))

heat2
#dev.off()
```